### 2019-04-30 article/article.tex
Create latex file

\documentclass[letter,12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[tc]{titlepic}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{lmodern}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{amsthm}
\usepackage{geometry,listings}
%\geometry{margin=2.5cm}
\usepackage{color,xcolor,moreverb}
\usepackage{tikz,graphicx}
\usepackage{fancyhdr}
\usepackage{url}
\usepackage{enumitem}
\usepackage[mathcal]{euscript}
\usepackage{tikz,tkz-tab,genyoungtabtikz}
\usepackage{bbm, bm}
\usepackage{mathrsfs}
\usepackage{xargs}
\usepackage{sagetex}
\usepackage{hyperref}

%Notes
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommand{\pauline}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
\newcommand{\nicolas}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green]{#1}}

% Maths
\newcommand{\RR}{\mathbb{R}}
\newcommand{\KK}{\mathbb{K}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\CC}{\mathbb{C}}

\DeclareMathOperator{\Sn}{\mathbb{S}_n}
\DeclareMathOperator{\GLr}{GL_r}

%Tableaux
\newcommand{\diagramme}{\YFrench \Yboxdim{10pt}\yng}
\newcommand{\tableau}{\YFrench \Yboxdim{10pt}\young}
%\newcommand{\diagramme}{\Yboxdim{10pt}\yng}  % notation anglaise
%\newcommand{\tableau}{\Yboxdim{10pt}\young}  % notation anglaise
\newcommand{\petitDiagramme}{\YFrench \Yboxdim{5pt}\yng}
\newcommand{\petitTableau}{\tiny \YFrench \Yboxdim{5pt}\young}
%\newcommand{\petitDiagramme}{\Yboxdim{5pt}\yng}  % notation anglaise
%\newcommand{\petitTableau}{\tiny \Yboxdim{5pt}\young}  % notation anglaise

%%- 1 ère page
\title{Computing the bicharacter of huge subspaces of polynomials}
\author{Pauline Hubert \and Nicolas Thiéry}

\begin{document}

	\maketitle

	\begin{abstract}
		... 
	\end{abstract}

	\section{Introduction}

\bibliographystyle{plain}
\nocite{*}
\bibliography{biblio}
\end{document}

### 2019-04-30 article/article.tex
Copy and paste content of jupyter worksheet 1

@@
 \usepackage[utf8]{inputenc}
-\usepackage{babel}
 \usepackage{lmodern}
@@
 \usepackage[mathcal]{euscript}
-\usepackage{tikz,tkz-tab,genyoungtabtikz}
+\usepackage{tikz,tkz-tab}
+\usepackage{genyoungtabtikz}
 \usepackage{bbm, bm}
@@
 \usepackage{xargs}
-\usepackage{sagetex}
+%\usepackage{sagetex}
 \usepackage{hyperref}
@@
 \DeclareMathOperator{\GLr}{GL_r}
+\DeclareMathOperator{\harmonics}{\mathcal{H}}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{conjecture}{Conjecture}
+\newtheorem{prop}{Proposition}
+\newtheorem{lemme}{Lemma}
+\newtheorem{coroll}{Corollary}
+\newtheorem{definition}{Definition}
 
@@
 
+	\tableofcontents
+
 	\section{Introduction}
+	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $H_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi $GL_k$-$S_n$  module.
+The main achievement is a calculation of this character for $n=6$ and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+
+	This is a potentially huge calculation ($H_{5,6}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
+So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
+As much as possible, the code was written to be modular and reusable.
+
+	\section{Contexte}
+	Note: throughout this notebook, we implicitly use the Frobenius map, and identify $S_n$ and $GL_k$ characters with their associated symmetric functions.
+
+	Consider the polynomial ring $P=\QQ[X]$ with $k$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
+	$$(X_{i,j})_{0\leq i<k, 0\leq j<n}$$
+
+	The polynomial ring $P$ is endowed with an action of the symmetric group $S_n$ by diagonal permutation of the columns, and $GL_k$ by diagonal action on the columns.
+The invariant ring $P^{S_n}$ is also known as the ring of multisymmetric functions.
+The coinvariant ring $P_{S_n}$ is the quotient of $R$ by the ideal $\langle {P^{S_n}}^+ \rangle$.
+It inherits from $P$ a structure of graded $GL_k$-$S_n$ bimodule.
+
+	The grading can be refined into a multigrading by rows.
+The multigrading is preserved by the action of $S_n$.
+The multigrading is not preserved by the action of $GL_k$, but instead carries exactly the information about the $GL_r$ character.
+It's thus equivalent to consider the $GL_r$-$S_n$ bicharacter or the $S_n$ multigraded character of $P_{S_n}$.
+
+	When $k=1$, the action of $GL_1$ is trivial; $P_{S_n}$ is of dimension $n!$ and carries the usual graded representation of $S_n$. Its character is given by a Hall-Littlewood polynomial.
+	When $k=2$, $P_{S_n}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture, the bigraded character is a Macdonald polynomial.
+
+	\section{Strategies}
+
+	\subsection{Computing in the space of harmonic polynomials}
+
+	We first need to compute in a quotient by an ideal.
+	A standard approach would be to compute a Gröbner basis of this ideal.
+	We haven't actually tried it, but given the number of variables and dimension of the quotient, we expect this calculation to be intractable.
+	Beside
+
+	So we took the classical route of realizing the coinvariant ring as the space $\def\harmonics{\mathcal{H}}\harmonics_{k,n}$ of *diagonal harmonic polynomials*.
+	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
+
+	Solving those differential equations would not be that tractable either.
+
+	\subsection{Polarization: diagonal harmonic polynomials from harmonic polynomials}
+
+	Define the polarization operators:
+
+	$$P_{i,i'}^d = \sum_j   x_{i',j} \partial_{i,j}^d\,.$$
+
+	For $d=1$, those operators implement the action of $sl_k$ induced by $gl_k$.
+
+	\begin{theorem}
+		Multisymmetric polynomials are obtained by polarization of symmetric polynomials in the first set of variables.
+	\end{theorem}
+
+	\begin{conjecture}
+		Diagonal harmonic polynomials are obtained by polarization of harmonic polynomials in the first set of variables.
+	\end{conjecture}
+
+	In the sequel, we assume that the above conjecture holds.
+The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the VanDerMonde determinant under differentiation.
+
+	In practice, we implemented a general purpose utility in Sage `Space(vectors, operators)` that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
+
+	TODO: put an example here
+
+	No rocket science here: maintain a matrix in row echelon form representing a basis of the space computed so far, and a ToDo list of $op(v)$ that remain to be computed and inserted in the matrix.
+
+	This utility should already have been in Sage, and will end up there.
+
+	Once a basis of $\harmonics_{k,n}$ is constructed, there still remains to recover its bicharacter.
+For $GL_k$ that's given by the multigrading.
+For $S_n$ some additional work has to be done (e.g.
+computing the traces of the action of permutations of all cycle types).
+
+	At this stage, we have an algorithm, but are still doing linear algebra in a huge space (cost $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space).
+
+	\subsection{Exploiting the multigrading}
+
+	The above utility can be adapted to exploit the multigrading.
+The input is now a collection of homogeneous vectors and operators together with their multidegrees, and a separate row echelon matrix is maintained for each multidegree.
+
+	Advantages:
+	- Writing $N=:\sum N_D$, The complexity becomes $(\sum N_D^2) M$ instead of $(\sum N_D)^2M_D$ (in fact better.
+	- The multidegrees, and therefore $GL_k$ character, can be directly read off the result.
+
+	\subsection{Exploiting representations of the symmetric group}
+
+	The polarization operators commute with the action of $S_n$. Therefore,
+	we can compute independently each $S_n$ isotypic component of $\harmonics_{k,n}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
+	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
+
+	In fact we can do better.
+
+	Fix a partition $\lambda$. Recall that a basis of the Specht module $V_\lambda$ is given by the family of Garnir/Specht polynomials $(G_{P})_P$ indexed by standard tableaux $P$ of shape $\lambda$.
+
+	To get a basis of the full isotypic component $\harmonics^\lambda$, we can, for example, use a generalization of this construction (voir \cite{Ariki1997}): a family of polynomials $(G_{P,Q})_{P,Q}$ indexed by a pairs of standard tableaux of shape $\lambda$:
+	- $Q$ specifies the copy of $V_\lambda$
+	- $P$ specifies the location within that copy of $V_\lambda$
+
+	Remark: For a fixed tableau $P$, denote by $\harmonics_k^P$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
+It's exactly the image of $\harmonics$ under the Young idempotent associated to $P$.
+For a given shape $\lambda$, the $\harmonics_k^P$ are all conjugate under $S_n$, and their direct sum is the isotypic component $\harmonics_k^\lambda$.
+
+	Conclusion: It is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$
+
+	\subsection{Exploiting column antisymmetries}
+
+	Specht polynomials tend to be big: in $6$ variables, the VanDerMonde determinant has $6!=720$ monomials.
+
+	But that's mostly because they are antisymmetric w.r.t.
+a large column stabilizer $S_P$.
+It's therefore sufficient to keep one representative monomial per $S_P$ orbit (and do some appropriate straightening whenever a new monomial is created).
+
+	This trick was already used by François for the polarizations of the VanDerMonde (the diagram space). Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
+
+	**Gain**: in theory up to $n!$. In practice between one and two orders of magnitude due to the overhead of straightening monomials.
+
+	\subsection{Exploiting row symmetries}
+
+	$H_k^P$ is symmetric w.r.t. permutation of rows, and such permutations
+	exchange multigraded components. For example, for $r=3$, the homogeneous components of respective multidegree $4,2,1$ and $2,1,4$ coincide
+	up to cycling of the rows. It is therefore sufficient, in principle, to compute homogeneous components with decreasing multidegree.
+	To achieve this, polarization operators can be tweaked: whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows.
+It can then easily be shown that those tweaked polarization operator properly generate the whole $\harmonics_k^P$ space from $\harmonics^P$.
+
+	**Gain**: an order of magnitude; below are the total dimension of each $\harmonics_5^\lambda$ and its restriction to homogeneous components of decreasing multidegree:
+
+	\subsection{Exploiting representations of $sl_k$}
+
+	Building on the previous strategy, it would be tempting to only compute the subspace of $sl_r$ highest weight vectors within each $\harmonics_k^P$.
+
+	The current code partially achieves this by avoiding the use of polarization operators of degree $0$ (which clearly would leave the space of highest weight vectors).
+The obtained space is still too big, and the actual highest weight vectors are obtained by computing the anihilator of the polarization operators $P_{i,i-1}^1$.
+
+	The first step requires an additional, not yet proven, trick.
+
+	We are currently exploring how to tweak the polarization operators to stabilize the space of highest weight vectors.
+
+	**Current gain:** another order of magnitude; down from 3 days to 45 minutes for $\harmonics_5^{1^6}$
+
+	**Potential gain:** another order of magnitude, both in time and memory:
+
+	\subsection{Exploiting the skew commutation of polarization operators}
+
+	The polarization operators skew commute.
+Therefore it would be in principle sufficient to apply them in some "decreasing order".
+This sounds promising given that, at this stage about 90\% of the polynomials that are produced are redundant and reduced to zero by the linear algebra.
+
+	However we have not yet been able put to use that optimization together with the other $sl_k$ optimizations, because the tweaked polarization operators don't skew commute consistently.
 

### 2019-04-30 article/article.tex
Add definitions in context section

@@
 %Notes
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\usepackage[colorinlistoftodos,prependcaption,textsize=small,textwidth=2.5cm]{todonotes}
 \newcommand{\pauline}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
@@
 	\section{Introduction}
-	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $H_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi $GL_k$-$S_n$  module.
+	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi $\GLr$-$\Sn$  module.
 The main achievement is a calculation of this character for $n=6$ and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
-	This is a potentially huge calculation ($H_{5,6}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
+	This is a potentially huge calculation ($\harmonics_{5,6}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
 So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
@@
 
-	\section{Contexte}
-	Note: throughout this notebook, we implicitly use the Frobenius map, and identify $S_n$ and $GL_k$ characters with their associated symmetric functions.
+	\section{Context}
 
-	Consider the polynomial ring $P=\QQ[X]$ with $k$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
-	$$(X_{i,j})_{0\leq i<k, 0\leq j<n}$$
+	Consider the polynomial ring $P=\QQ[X]$ with $k$ sets of $n$ variables.
+To fix conventions, we think of $X$ as a matrix of variables: \pauline{small $x$ for variables, capital $X$ for sets of variables?
+}
+	$$(X_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
+	and we denote by $X_i$ the i-th set of variable.
 
-	The polynomial ring $P$ is endowed with an action of the symmetric group $S_n$ by diagonal permutation of the columns, and $GL_k$ by diagonal action on the columns.
-The invariant ring $P^{S_n}$ is also known as the ring of multisymmetric functions.
-The coinvariant ring $P_{S_n}$ is the quotient of $R$ by the ideal $\langle {P^{S_n}}^+ \rangle$.
-It inherits from $P$ a structure of graded $GL_k$-$S_n$ bimodule.
+	The polynomial ring $P$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns, and $\GLr$ by diagonal action on the rows.
+The invariant ring $P^{\Sn}$ is also known as the ring of multisymmetric functions.
+The co-invariant ring $P_{\Sn}$ is the quotient of $R$ by the ideal $\langle {P^{\Sn}}^+ \rangle$ \pauline{+ = without constant terms ?}.
+It inherits from $P$ a structure of graded $\GLr$-$\Sn$ bi-module.
 
 	The grading can be refined into a multigrading by rows.
-The multigrading is preserved by the action of $S_n$.
-The multigrading is not preserved by the action of $GL_k$, but instead carries exactly the information about the $GL_r$ character.
-It's thus equivalent to consider the $GL_r$-$S_n$ bicharacter or the $S_n$ multigraded character of $P_{S_n}$.
+The multigrading is preserved by the action of $\Sn$.
+The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$ character.
+It's thus equivalent to consider the $\GLr$-$\Sn$ bicharacter or the $\Sn$ multigraded character of $P_{\Sn}$.
 
-	When $k=1$, the action of $GL_1$ is trivial; $P_{S_n}$ is of dimension $n!$ and carries the usual graded representation of $S_n$. Its character is given by a Hall-Littlewood polynomial.
-	When $k=2$, $P_{S_n}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture, the bigraded character is a Macdonald polynomial.
+	When $k=1$, the action of $GL_1$ is trivial; $P_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
+	When $k=2$, $P_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture, the bigraded character is a Macdonald polynomial.
+
+	Throughout this notebook, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ characters with their associated symmetric functions. \\
+
+	We denote the partial derivative the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for any variable $x$ in $X$.
+
+	When $X$ contains only on set of variable ($r=1$), we define the \emph{harmonic polynomials} as follow.
+
+	\begin{definition}
+		Let $f \in \QQ[X]$, $f$ is \emph{harmonic} if and only if
+		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0 $$
+		for all $k \geq 0$, $k \in \NN$.
+	\end{definition}
+
+	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$ is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
+It is also a realization of the coinvariants of the symmetric group: $\QQ[X]\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.
+
+	As an example, $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$.
+
+	Note that $\Delta:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\
+
+	Let now go back to $X$ containing an arbitrary number $r$ of sets of variables.
+	We define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
+	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{11}}^{\alpha_1}\partial_{x_{r1}}^{\alpha_r} + \dots + \partial_{x_{1n}}^{\alpha_1}\partial_{x_{rn}}^{\alpha_r}$$
+
+	For example, $r=3$ and we denote $x, y$ and $z$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
+
+	The space of the diagonal harmonic polynomials $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. And $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.
+
+	%define polarization operators
 
@@
 	We haven't actually tried it, but given the number of variables and dimension of the quotient, we expect this calculation to be intractable.
-	Beside
 
@@
 	Once a basis of $\harmonics_{k,n}$ is constructed, there still remains to recover its bicharacter.
-For $GL_k$ that's given by the multigrading.
-For $S_n$ some additional work has to be done (e.g.
+For $\GLr$ that's given by the multigrading.
+For $\Sn$ some additional work has to be done (e.g.
 computing the traces of the action of permutations of all cycle types).
@@
 	- Writing $N=:\sum N_D$, The complexity becomes $(\sum N_D^2) M$ instead of $(\sum N_D)^2M_D$ (in fact better.
-	- The multidegrees, and therefore $GL_k$ character, can be directly read off the result.
+	- The multidegrees, and therefore $\GLr$ character, can be directly read off the result.
 
@@
 
-	The polarization operators commute with the action of $S_n$. Therefore,
-	we can compute independently each $S_n$ isotypic component of $\harmonics_{k,n}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
+	The polarization operators commute with the action of $\Sn$. Therefore,
+	we can compute independently each $\Sn$ isotypic component of $\harmonics_{k,n}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
 	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
@@
 It's exactly the image of $\harmonics$ under the Young idempotent associated to $P$.
-For a given shape $\lambda$, the $\harmonics_k^P$ are all conjugate under $S_n$, and their direct sum is the isotypic component $\harmonics_k^\lambda$.
+For a given shape $\lambda$, the $\harmonics_k^P$ are all conjugate under $\Sn$, and their direct sum is the isotypic component $\harmonics_k^\lambda$.
 
@@
 
+	\section{Applications}
+
 \bibliographystyle{plain}

### 2019-04-30 article/article.tex
Add polarization and steenrod op.

@@
 
-	Note that $\Delta:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\
+	Note that $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\
 
@@
 
-	%define polarization operators
+	\begin{definition}
+		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
+		$$P_{x_a,x_b}^k = \sum_{i=1}^{n} x_{bi} \partial_{x_{ai}}^k$$
+		where $x_a$ and $x_b$ are two sets of variables of $X$. 
+	\end{definition}
+
+	It is well known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives.
+Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
+
+	\begin{definition} \pauline{how to introduce them ?}
+		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by
+		$$St_{x_a}^k = \sum_{i=1}^{n} x_{ai} \partial_{x_{ai}}^k$$
+		where $x_a$ is a set of variables of $X$. 
+	\end{definition}
+
+	Only the Steenrod operators for $k=2$ and $k=3$ are necessary since the other operators can be obtained from the two first ones.
+For example, $St_{x_a}^4 = St_{x_a}^3St_{x_a}^2 - St_{x_a}^2St_{x_a}^3$.
+
+	Note that $St_{x_a}^k = P_{x_a,x_a}^k$ but we distinguish the two families of operators because they play different roles.
 

### 2019-05-02 diagonal_polynomial_ring.py
Add optimisations on antisymmetries and row symmetries on jupyter notebook

@@ -412,7 +412,7 @@ class DiagonalPolynomialRing(UniqueRepresentation, Parent):
                 result = act_on_polynomial(result, ss)
         return result
         
-    def steenrod_op(self, p, i, k):
+    def steenrod_op(self, p, i, k, row_symmetry=None):
         """
         Apply the Steenrod operator of degree `k` for the `i`th set of variables
         to `p`. 
@@ -436,7 +436,15 @@ class DiagonalPolynomialRing(UniqueRepresentation, Parent):
         """
         n = self._n
         X = self.variables()
-        return sum(X[i,j]*p.derivative(X[i,j], k) for j in range(0, n))
+        result = sum(X[i,j]*p.derivative(X[i,j], k) for j in range(0, n))
+        if row_symmetry=="permutation" and result:
+            deg = self.multidegree(result) 
+            deg = tuple(deg) + tuple(0 for i in range(self._inert))
+            if list(deg) != sorted(deg, reverse=True):
+                s = reverse_sorting_permutation(deg)
+                ss = self.row_permutation(s)
+                result = act_on_polynomial(result, ss)
+        return result
         
     def diagonal_steenrod(self, p, i1, i2, d1, d2):
         """
@@ -908,7 +916,7 @@ class DiagonalAntisymmetricPolynomialRing(DiagonalPolynomialRing):
             result = antisymmetric_normal(result, self._n, self._r+self._inert, antisymmetries)
         return result
 
-    def multi_polarization(self, p, D, i2, antisymmetries=None): 
+    def multi_polarization(self, p, D, i2): 
         """
         Return the multi polarization `P_{D,i_2}. p` of `p`.
         The result is reduced with respect to the given antisymmetries.
@@ -928,4 +936,13 @@ class DiagonalAntisymmetricPolynomialRing(DiagonalPolynomialRing):
         if antisymmetries and result:
             result = reduce_antisymmetric_normal(result, self._n, self._r+self._inert, antisymmetries)
         return result
-
+        
+        
+    def steenrod_op(self, p, i, k, row_symmetry=None):
+        """
+        """
+        antisymmetries = self._antisymmetries
+        result = super(DiagonalAntisymmetricPolynomialRing,self).steenrod_op(p, i, k, row_symmetry=row_symmetry)
+        if antisymmetries and result:
+            result = antisymmetric_normal(result, self._n, self._r+self._inert, antisymmetries)
+        return result

### 2019-05-03 compute_character.py
Clean, add last functions and optimisation and add documentation

@@ -94,29 +94,14 @@ def steenrod_operators(P, degree=1):
     MATH..:: \sum_i x_i \partial_{x_i}^{k+1}
     
     INPUT: 
-    - ``P`` -- a polynomial ring and degree an interger. 
+    - ``P`` -- a polynomial ring
+    - ``degree`` -- an Interger. 
     """
     r = P._r
     D = P._grading_set
     op = {}
     for i in range(r):
         op[D((-degree if j==i else 0 for j in range(r)))] = [functools.partial(P.steenrod_op, i=i, k=degree+1)]
-    return op
-
-def diagonal_steenrod_operators(P, list_deg):
-    """
-    Return the diagonal Steenrod operators
-    
-    INPUT:
-    - ``P`` -- a polynimial ring in at least two sets of variables
-    - ``list_deg`` -- a list of the degree for the operators
-    """
-    r = P._r
-    D = P._grading_set
-    op = {}
-    for dx, dy in list_deg:
-        op[D((-dx if j==0 else -dy if j==1 else 0 for j in range(r)))] = [
-            functools.partial(P.diagonal_steenrod, i1=0, i2=1, d1=dx, d2=dy)]
     return op
 
 def polarization_operators(P, side=None, row_symmetry=None, max_deg=0):
@@ -176,6 +161,7 @@ def higher_polarization_operators(P, side=None, row_symmetry=None, max_deg=0):
             if (i1<i2 if side == 'down' else i1!=i2)
            }
 
+
 def symmetric_derivatives(P, list_deg, row_symmetry=None):
     """
     Return the list of all symmetric derivative of degree contained
@@ -191,6 +177,19 @@ def symmetric_derivatives(P, list_deg, row_symmetry=None):
   
 
 def merge(dict1, dict2):
+    """
+    Merge two dictionnaries whose values are lists into the first one. 
+    
+    INPUT:
+    - ``dict1``, ``dict2`` -- dictionnaries
+    
+    EXAMPLES::
+        sage: dict1 = {"colors":["red", "blue"], "numbers":[1,2,3]}
+        sage: dict2 = {"colors":["blue", "green"]}
+        sage: merge(dict1, dict2)
+        {'colors': ['red', 'blue', 'blue', 'green'], 'numbers': [1, 2, 3]}
+
+    """
     result = dict1
     for key, value in dict2.iteritems():
         if key in result:
@@ -198,13 +197,43 @@ def merge(dict1, dict2):
         else:
             result[key] = value
[…]

### 2019-05-03 compute_character.py
Complete documentation

@@ -463,6 +463,15 @@ def character_quotient(M, N, n, r, left_basis=s, right_basis=s):
 ##############################################################################      
 
 def factorise(f, n):
+    """
+    Return the factorization of the tensor product `f` w.r.t the right symmetric
+    functions. The right symmetric functions have their supports in the partitions
+    on `n`. 
+    
+    INPUT:
+    - ``f`` -- a sum of tensor products on symmetric functions
+    - ``n`` -- an Integer
+    """
     SymmetricFunctions(QQ).s()
     supp = sorted(f.support())
     result = {}
@@ -479,6 +488,15 @@ def factorise(f, n):
             show(b)
         
 def dimension(f, n):
+    """
+    Return the dimension of the tensor product `f` w.r.t the right symmetric
+    functions. The right symmetric functions have their supports in the partitions
+    on `n` and they reprensent characters of `S_n`. 
+    
+    INPUT:
+    - ``f`` -- a sum of tensor products on symmetric functions
+    - ``n`` -- an Integer
+    """
     supp = sorted(f.support())
     result = {}
     res = []

### 2019-05-06 compute_character.py
Correct typo

@@ -269,7 +269,7 @@ def add_degrees_isotypic(d1, d2):
 
     """
     D = cartesian_product([ZZ for i in range(len(d1[0]))])
-    return D(d1[0])s+D(d2), d1[1]
+    return D(d1[0])+D(d2), d1[1]
     
 def add_degrees_symmetric(d1,d2):
     """

### 2019-05-06 article/article.tex
Add content in context section

@@
 	\section{Introduction}
-	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi $\GLr$-$\Sn$  module.
-The main achievement is a calculation of this character for $n=6$ and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
+The main achievement is a calculation of this character for $n=6$ \pauline{+ some cases for $n=7$ ?} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
@@
 To fix conventions, we think of $X$ as a matrix of variables: \pauline{small $x$ for variables, capital $X$ for sets of variables?
-}
+} \pauline{introduce inert variables now or later?}
 	$$(X_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
-	and we denote by $X_i$ the i-th set of variable.
+	and we denote by $X_i$ the i-th set of variables.
 
-	The polynomial ring $P$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns, and $\GLr$ by diagonal action on the rows.
+	The polynomial ring $P$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of $\GLr$ by diagonal action on the rows.
 The invariant ring $P^{\Sn}$ is also known as the ring of multisymmetric functions.
-The co-invariant ring $P_{\Sn}$ is the quotient of $R$ by the ideal $\langle {P^{\Sn}}^+ \rangle$ \pauline{+ = without constant terms ?}.
-It inherits from $P$ a structure of graded $\GLr$-$\Sn$ bi-module.
+The co-invariant ring $P_{\Sn}$ is the quotient of $P$ by the ideal $\langle {P^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
+It inherits from $P$ a structure of graded $\GLr \times \Sn$ bi-module.
 
@@
 The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$ character.
-It's thus equivalent to consider the $\GLr$-$\Sn$ bicharacter or the $\Sn$ multigraded character of $P_{\Sn}$.
+It's thus equivalent to consider the $\GLr \times \Sn$ bicharacter or the $\Sn$ multigraded character of $P_{\Sn}$.
 
 	When $k=1$, the action of $GL_1$ is trivial; $P_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
-	When $k=2$, $P_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture, the bigraded character is a Macdonald polynomial.
+	When $k=2$, $P_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
 
-	Throughout this notebook, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ characters with their associated symmetric functions. \\
+	Throughout this notebook, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur symmetric functions. \\
 
@@
 
-	Note that $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic and that if $f$ is harmonic then $\partial_i f$ is also harmonic. \\
+	Note that the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic. It is also easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$. \\
 
-	Let now go back to $X$ containing an arbitrary number $r$ of sets of variables.
-	We define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
-	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{11}}^{\alpha_1}\partial_{x_{r1}}^{\alpha_r} + \dots + \partial_{x_{1n}}^{\alpha_1}\partial_{x_{rn}}^{\alpha_r}$$
+	Going back to an arbitrary number $r$ of sets of variables, we define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
+	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{11}}^{\alpha_1}\dots\partial_{x_{r1}}^{\alpha_r} + \dots + \partial_{x_{1n}}^{\alpha_1}\dots\partial_{x_{rn}}^{\alpha_r} = \sum_{j=1}^{n} \prod_{i=1}^{r} \partial_{x_{ij}}^{\alpha_i}$$
 
-	For example, $r=3$ and we denote $x, y$ and $z$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
+	For example, take $r=3$ and denote $x, y$ and $z$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
 
-	The space of the diagonal harmonic polynomials $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. And $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.
+	The space of the diagonal harmonic polynomials $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
+
+	The previous definition means that the diagonal harmonic polynomials are solutions of differential equations systems. They can also be obtained by construction using polarization operators.
 
@@
 Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
+\\
 
-	\begin{definition} \pauline{how to introduce them ?}
+	The diagonal harmonics $\harmonics_{n,r}$ have been studied a lot until now.
+The character in the case $r=2$ is due to Garsia and Haiman (see \cite{GarsiaHaiman1993}) and some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
+Therefore, the computation of those characters should lead to a better understanding of those spaces.
+
+	In their work, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
+\\
+
+	F.
+Bergeron recently introduced another generalization of the diagonal harmonics, with inert variables.
+We add a new row $\theta = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$.
+The symmetric group still acts diagonally on the rows of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
+Like before, we consider the smallest subspace containing a certain determinant and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
+The determinant used in this case is defined as follow.
+
+	Let $\lambda$ be a partition of $n$, we also denote $\lambda$ the Ferrer's diagram associated to the partition $\lambda$ and each cell of $\lambda$ is given by the coordinates of its bottom left corner.
+Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+	For example, the partition $21$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{21} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+\\
+
+	Since those subspaces are completely new, computing some characters on Sage helps understanding them better and allows to find some properties of thoses spaces. 
+	Plus, experimentation helped finding the right definition we needed for this generalization.
+
+	\begin{definition} \pauline{find the right place}
 		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by

### 2019-05-06 isomorphic_object.py
Experimental file about isomorphic objects

@@ -1,0 +1,41 @@
+from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
+
+# Stuff here everything currently missing in SageMath about isomorphic algebras
+class Algebras_IsomorphicObjects(IsomorphicObjectsCategory):
+    class ParentMethods:
+        def summation(self, x, y):
+            return self.retract(x.lift() + y.lift())
+        def gens(self):
+            return [self.retract(g) for g in self.ambient().gens()]
+
+Algebras.IsomorphicObjects = Algebras_IsomorphicObjects
+
+class IsomorphicObject(UniqueRepresentation, Parent):
+    def ambient(self):
+        return self._ambient
+    def lift(self, p):
+        return p.value
+    def retract(self, p):
+        return self.element_class(self,p)
+    def base_ring(self):
+        return self.ambient().base_ring()
+    def __init__(self, ambient, category):
+        self._ambient = ambient
+        Parent.__init__(self, category=category.IsomorphicObjects())
+        # Bricolage
+        self._remove_from_coerce_cache(ambient)
+        phi = sage.categories.morphism.SetMorphism(Hom(ambient, self, category), self.retract)
+        phi.register_as_coercion()
+
+    class Element(ElementWrapper):
+        pass
+
+"""
+
+sage: %runfile isomorphic_object.py
+sage: P = PolynomialRing(QQ, ['x','y'])
+sage: PP = IsomorphicObject(P, Algebras(QQ))
+sage: x,y = PP.gens()
+sage: (2*x + y)^2 + 1
+4*x^2 + 4*x*y + y^2 + 1
+"""

### 2019-05-13 diagonal_polynomial_ring.py
Improve antisymmetries gestion

@@ -85,13 +85,6 @@ class DiagonalPolynomialRing(UniqueRepresentation, Parent):
         """
         return self._P.base_ring()
         
-    def polynomial_ring(self):
-        """
-        sage: D = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
-        sage: D.polynomial_ring()
-        Multivariate Polynomial Ring in q0, q1, q2 over Rational Field
-        """
-        return self._Q
         
     def gens(self):
         """
@@ -99,7 +92,7 @@ class DiagonalPolynomialRing(UniqueRepresentation, Parent):
         sage: D.gens()
         (q0, q1, q2)
         """
-        return self.polynomial_ring().gens()
+        return self._Q.gens()
 
 
     def algebra_generators(self):

### 2019-05-13 isomorphic_object.py

@@ -1,4 +1,33 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import functools
+
+from sage.structure.parent import Parent
+from sage.structure.unique_representation import UniqueRepresentation
+from sage.structure.sage_object import load
+
+from sage.parallel.decorate import parallel
+from sage.misc.misc_c import prod
+
+from sage.rings.polynomial.polynomial_ring_constructor import PolynomialRing
+from sage.rings.integer_ring import ZZ
+from sage.rings.rational_field import QQ
 from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
+from sage.categories.algebras import Algebras
+from sage.categories.cartesian_product import cartesian_product
+from sage.functions.other import binomial
+from sage.combinat.words.word import Word
+
+from diagram import *
+from subspace import *
+from young_idempotent import *
+from polynomial_derivative import *
+
+from utilities import *
+from antisymmetric_utilities import *
+
+
 
 # Stuff here everything currently missing in SageMath about isomorphic algebras
 class Algebras_IsomorphicObjects(IsomorphicObjectsCategory):
@@ -29,13 +58,301 @@ class IsomorphicObject(UniqueRepresentation, Parent):
 
     class Element(ElementWrapper):
         pass
+        
+        
+class DiagonalPolynomialRing(IsomorphicObject):
+    """
+    The ring of diagonal polynomials in $n \times r$ variables and $n \times k$ inert variables.
+    In order to distinguish the inert variables among the others, they are named `theta_{i,j}`
 
+    EXAMPLES::
+
+        sage: P = DiagonalPolynomialRing(QQ, 4, 3)
+        sage: P
+        Diagonal polynomial ring with 3 rows of 4 variables over Rational Field
+
+        sage: P = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
+        sage: P
+        Diagonal polynomial ring with 3 rows of 4 variables and 1 row(s) of inert variables over Rational Field
+
+    """
+    def __init__(self, R, n, r, inert=0):
+        names = ["x%s%s"%(i,j) for i in range(r) for j in range(n)]+["theta%s%s"%(i,j) for i in range(inert) for j in range(n)]
+        P = PolynomialRing(R, n*(r+inert), names)
+        IsomorphicObject.__init__(self, P, Algebras())
+        vars = P.gens()
+        self._P = P
+        self._R = R
[…]

### 2019-05-13 article/article.tex
Add content in setion 3

@@
 \newcommand{\tableau}{\YFrench \Yboxdim{10pt}\young}
-%\newcommand{\diagramme}{\Yboxdim{10pt}\yng}  % notation anglaise
-%\newcommand{\tableau}{\Yboxdim{10pt}\young}  % notation anglaise
 \newcommand{\petitDiagramme}{\YFrench \Yboxdim{5pt}\yng}
 \newcommand{\petitTableau}{\tiny \YFrench \Yboxdim{5pt}\young}
-%\newcommand{\petitDiagramme}{\Yboxdim{5pt}\yng}  % notation anglaise
-%\newcommand{\petitTableau}{\tiny \Yboxdim{5pt}\young}  % notation anglaise
 
@@
 	\begin{abstract}
-		... 
+		To complete ... 
 	\end{abstract}
@@
 	$$(X_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
-	and we denote by $X_i$ the i-th set of variables.
+	and we denote by $X_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
 
@@
 
-	The previous definition means that the diagonal harmonic polynomials are solutions of differential equations systems. They can also be obtained by construction using polarization operators.
+	The previous definition means that the diagonal harmonic polynomials are solutions of differential equations systems. 
+	They can also be obtained by construction using polarization operators.
 
-	\begin{definition}
+	\begin{definition} \pauline{define polarization now or later ?}
 		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
@@
 
-	It is well known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives.
+	For $=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$.
+
+	It is known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives.
 Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
-\\
 
@@
 We add a new row $\theta = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$.
-The symmetric group still acts diagonally on the rows of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
+The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
 Like before, we consider the smallest subspace containing a certain determinant and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
@@
 
-	Let $\lambda$ be a partition of $n$, we also denote $\lambda$ the Ferrer's diagram associated to the partition $\lambda$ and each cell of $\lambda$ is given by the coordinates of its bottom left corner.
+	Let $\lambda$ be a partition of $n$, we also denote $\lambda$ the Ferrer's diagram associated to the partition $\lambda$ and each cell of $\lambda$ is given by the coordinates $(a,b)$ of its bottom left corner.
 Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
@@
 
-	\begin{definition} \pauline{find the right place}
+	\begin{definition} \pauline{find the right place for Steenrod op}
 		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by
@@
 
-	So we took the classical route of realizing the coinvariant ring as the space $\def\harmonics{\mathcal{H}}\harmonics_{k,n}$ of *diagonal harmonic polynomials*.
+	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_{n,r}$ of diagonal harmonic polynomials.
 	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
 
-	Solving those differential equations would not be that tractable either.
+	Solving those differential equations would not be that tractable either. So instead we used operators (partial derivatives and polarization operators).
 
-	\subsection{Polarization: diagonal harmonic polynomials from harmonic polynomials}
+	\subsection{Polarization: diagonal harmonics from harmonics}
 
-	Define the polarization operators:
-
-	$$P_{i,i'}^d = \sum_j   x_{i',j} \partial_{i,j}^d\,.$$
-
-	For $d=1$, those operators implement the action of $sl_k$ induced by $gl_k$.
+	\begin{definition}
+		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
+		$$P_{x_a,x_b}^k = \sum_{i=1}^{n} x_{bi} \partial_{x_{ai}}^k$$
+		where $x_a$ and $x_b$ are two sets of variables of $X$. 
+	\end{definition}
 
@@
 
-	\begin{conjecture}
+	\begin{theorem}
 		Diagonal harmonic polynomials are obtained by polarization of harmonic polynomials in the first set of variables.
-	\end{conjecture}
+	\end{theorem}
 
-	In the sequel, we assume that the above conjecture holds.
-The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the VanDerMonde determinant under differentiation.
+	The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the Vandermonde determinant under differentiation.
 
-	In practice, we implemented a general purpose utility in Sage `Space(vectors, operators)` that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
+	In practice, we implemented a general purpose utility in Sage \texttt{Space(vectors, operators)} that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
+	\nicolas{put an example here}
 
-	TODO: put an example here
+	No rocket science here: maintain a matrix in row echelon form representing a basis of the space computed so far, and a ToDo list of $op(v)$, that remain to be computed and inserted in the matrix, where $op$ is an operator and $v$ an element of the subspace in construction.
 
-	No rocket science here: maintain a matrix in row echelon form representing a basis of the space computed so far, and a ToDo list of $op(v)$ that remain to be computed and inserted in the matrix.
+	This utility should already have been in Sage, and will end up there. \\
 
-	This utility should already have been in Sage, and will end up there.
-
-	Once a basis of $\harmonics_{k,n}$ is constructed, there still remains to recover its bicharacter.
+	Once a basis of $\harmonics_{n,r}$ is constructed, there still remains to recover its bicharacter.
 For $\GLr$ that's given by the multigrading.
@@
 
-	Advantages:
-	- Writing $N=:\sum N_D$, The complexity becomes $(\sum N_D^2) M$ instead of $(\sum N_D)^2M_D$ (in fact better.
-	- The multidegrees, and therefore $\GLr$ character, can be directly read off the result.
+	There are two advantages of doing that. 
+	First, writing $N=:\sum N_D$, the complexity becomes $(\sum N_D^2) M$ instead of $(\sum N_D)^2M_D$ (in fact better).
+	Second, the multidegrees, and therefore $\GLr$ character, can be directly read off the result.
 
@@
 
-	The polarization operators commute with the action of $\Sn$. Therefore,
-	we can compute independently each $\Sn$ isotypic component of $\harmonics_{k,n}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
+	The polarization operators, ie the action of $\GLr$, commute with the action of $\Sn$.
+Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n,r}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
 	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
@@
 
-	Specht polynomials tend to be big: in $6$ variables, the VanDerMonde determinant has $6!=720$ monomials.
+	Specht polynomials tend to be big: in $6$ variables, the Vandermonde determinant has $6!=720$ monomials.
 
@@
 
-	This trick was already used by François for the polarizations of the VanDerMonde (the diagram space). Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
+	This trick was already used by François for the polarizations of the Vandermonde (the diagram space). Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
 
@@
 	The polarization operators skew commute.
-Therefore it would be in principle sufficient to apply them in some "decreasing order".
+\pauline{add commutator computation} Therefore it would be in principle sufficient to apply them in some "decreasing order".
 This sounds promising given that, at this stage about 90\% of the polynomials that are produced are redundant and reduced to zero by the linear algebra.

### 2019-05-13 article/article.tex
Complete section on repr. of Sn

@@
 \DeclareMathOperator{\harmonics}{\mathcal{H}}
+\DeclareMathOperator{\sgn}{sgn}
 
@@
 
+	\subsection{Harmonic and diagonal harmonic polynomials}
+
 	Consider the polynomial ring $P=\QQ[X]$ with $k$ sets of $n$ variables.
 To fix conventions, we think of $X$ as a matrix of variables: \pauline{small $x$ for variables, capital $X$ for sets of variables?
-} \pauline{introduce inert variables now or later?}
+}
 	$$(X_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
@@
 	It is known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives. 
-Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
+	%Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
 
@@
 
-	In their work, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
+	\subsection{Generalizations}
+
+	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
 \\
@@
 
-	We first need to compute in a quotient by an ideal.
+	We first need to compute in a quotient by an ideal, $P / I_n$ where $I_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. 
 	A standard approach would be to compute a Gröbner basis of this ideal.
@@
 	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_{n,r}$ of diagonal harmonic polynomials.
-	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
+	This is the space of those polynomials that satisfy the equations given by the multisymmetric \pauline{multi symmetric vs diagonal symmetric ?} functions seen as differential operators.
 
@@
 
-	\begin{theorem}
+	\begin{theorem} \label{DiagHarm}
 		Diagonal harmonic polynomials are obtained by polarization of harmonic polynomials in the first set of variables.
@@
 
-	The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the Vandermonde determinant under differentiation.
+	Therorem \ref{DiagHarm} has been proven for two sets of variables.
+It is not proven yet for more than two sets of variables but it has been verified by calculation for a large number of sets of variables so we assume it to be true since we will never reach that number of sets in our case.
 
-	In practice, we implemented a general purpose utility in Sage \texttt{Space(vectors, operators)} that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
+	The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the Vandermonde determinant under differentiation. \\
+
+	In practice, we implemented a general purpose utility in Sage, \texttt{Subspace(vectors, operators)} that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
 	\nicolas{put an example here}
@@
 
+	In practice, first we compute $\harmonics_{n}$ and decompose it into isotypic components using the Young symmetrizer.
+Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ from those of $\harmonics_{n}$.
+\\
+
+	To define the Young symmetrizer, we first need to define two elements of the symmetric group algebra $\CC \Sn$.
+Let $P_{\lambda}$ be the subgroup of $\Sn$ of all row preserving permutations and $Q_{\lambda}$ the subgroup of the columns preserving permutations.
+Then we have $a_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sigma$ and  $b_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sgn(\sigma) \sigma$.
+Finally, the Young symmetrizer is the element $$c_{\lambda} = a_{\lambda} b_{\lambda}.$$
+
+	\begin{theorem} \cite{FultonHarris1991}
+		The Young symmetrizer $c_{\lambda}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $V_{\lambda}$ of $\Sn$.
+		Thus any irreducible representation can be obtain this way for a unique partition. 
+	\end{theorem}
+
+	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\harmonics_{n}$ gives representatives of the isotypic components of $\Sn$.
+\pauline{Do we need to prove explicitly commutation with symmetric operators?}
+
+	As mentioned above, since the action of $\GLr$ and $\Sn$ commutes, at this stage we only have to apply the polarization operators on each isotypic component independently to be able to compute the bicharacter.
+\\
+
 	In fact we can do better.
@@
 
-	To get a basis of the full isotypic component $\harmonics^\lambda$, we can, for example, use a generalization of this construction (voir \cite{Ariki1997}): a family of polynomials $(G_{P,Q})_{P,Q}$ indexed by a pairs of standard tableaux of shape $\lambda$:
-	- $Q$ specifies the copy of $V_\lambda$
-	- $P$ specifies the location within that copy of $V_\lambda$
+	To get a basis of the full isotypic component $\harmonics^\lambda$, we can, for example, use a generalization of this construction (see \cite{Ariki1997}): a family of polynomials $(G_{P,Q})_{P,Q}$ indexed by a pairs $(P,Q)$ of standard tableaux of shape $\lambda$ where $Q$ specifies the copy of $V_\lambda$ and $P$ specifies the location within that copy of $V_\lambda$.
 
 	Remark: For a fixed tableau $P$, denote by $\harmonics_k^P$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
-It's exactly the image of $\harmonics$ under the Young idempotent associated to $P$.
+It's exactly the image of $\harmonics_n$ under the Young idempotent associated to $P$.
 For a given shape $\lambda$, the $\harmonics_k^P$ are all conjugate under $\Sn$, and their direct sum is the isotypic component $\harmonics_k^\lambda$.
 
-	Conclusion: It is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$
+	To conclude, it is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$
 
@@
 	The polarization operators skew commute.
-\pauline{add commutator computation} Therefore it would be in principle sufficient to apply them in some "decreasing order".
+Therefore it would be in principle sufficient to apply them in some "decreasing order".
 This sounds promising given that, at this stage about 90\% of the polynomials that are produced are redundant and reduced to zero by the linear algebra.
@@
 	\section{Applications}
+	Ask Francois ...
 

### 2019-05-14 article/article.tex
Add content in context

@@
 
-	Consider the polynomial ring $P=\QQ[X]$ with $k$ sets of $n$ variables.
+	Consider the polynomial ring $R=\QQ[X]$ with $k$ sets of $n$ variables.
 To fix conventions, we think of $X$ as a matrix of variables: \pauline{small $x$ for variables, capital $X$ for sets of variables?
 }
-	$$(X_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
+	$$(x_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
 	and we denote by $X_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
 
-	The polynomial ring $P$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of $\GLr$ by diagonal action on the rows.
-The invariant ring $P^{\Sn}$ is also known as the ring of multisymmetric functions.
-The co-invariant ring $P_{\Sn}$ is the quotient of $P$ by the ideal $\langle {P^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
-It inherits from $P$ a structure of graded $\GLr \times \Sn$ bi-module.
+	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of $\GLr$ by diagonal action on the rows.
+The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions.
+The co-invariant ring $R_{\Sn}$ is the quotient of $P$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
+It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.
 
@@
 
-	When $k=1$, the action of $GL_1$ is trivial; $P_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
-	When $k=2$, $P_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
+	When $k=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
+	When $k=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
 
@@
 
-	We denote the partial derivative the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for any variable $x$ in $X$.
-
-	When $X$ contains only on set of variable ($r=1$), we define the \emph{harmonic polynomials} as follow.
+	We denote the partial derivative the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for any variable $x \in X$.
+	When $X$ contains only on set of variable ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
 
@@
 	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$ is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
-It is also a realization of the coinvariants of the symmetric group: $\QQ[X]\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.
+It is also a realization of the coinvariants of the symmetric group: $\QQ[X]\, /\, \langle Sym(X)^+ \rangle$ \pauline{$= \QQ[X] / \mathcal{I}_n$} and a graded regular representation of $\Sn$.
 
@@
 
-	Note that the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic. It is also easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$. \\
+	Note that the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic.
+It is also easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$.
+From that we have another way to define $\harmonics_{n}$, see (\cite{Haiman2002} and \cite{Bergeron2009}) for more details.
+
+	\begin{theorem}
+		The space of harmonic polynomials $\harmonics_{n}$ is the smallest subspace containing the Vandermonde determinant $V_n$ and closed by partial derivatives.
+	\end{theorem}
 
@@
 
-	The space of the diagonal harmonic polynomials $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
+	The space of \emph{diagonal harmonic polynomials} $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
 
 	The previous definition means that the diagonal harmonic polynomials are solutions of differential equations systems. 
-	They can also be obtained by construction using polarization operators.
+	As for the harmonics, we have an alternative way to obtain $\harmonics_{n,r}$.
 
-	\begin{definition} \pauline{define polarization now or later ?}
+	\begin{definition}
 		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
@@
 
-	For $=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$.
+	For $k=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$. Moreover, we have the following useful theorems.
 
-	It is known (\cite{Haiman2002} and \cite{Bergeron2009}) that the harmonics $\harmonics_{n,1}$ are generated by the Vandermonde determinant $V_n$ and closed by partial derivatives. 
-	%Moreover, the diagonal harmonics $\harmonics_{n,r}$ are generated by $\harmonics_{n,1}$ and closed by the polarization operators.
+	\begin{theorem}
+		Multisymmetric polynomials are obtained by polarization of symmetric polynomials in the first set of variables.
+	\end{theorem}
+
+	\begin{theorem} \label{DiagHarm}
+		Diagonal harmonic polynomials $\harmonics_{n,r}$ are obtained by polarization of harmonic polynomials $\harmonics_{n,1}$ in the first set of variables.
+	\end{theorem}
+
+	Therorem \ref{DiagHarm} has been proven for two sets of variables.
+It is not proven yet for more than two sets of variables but it has been verified by calculation for a large number of sets of variables so we assume it to be true since we will never reach that number of sets in our case.
+\\
 
@@
 	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
-\\
+
+	Let $X=(x_1, x_2, \dots, x_n)$ and $Y=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\mu$ be a partition of $n$.
+We also denote $\mu$ the Ferrer's diagram (in French notation) associated to the partition $\mu$ and each cell of $\mu$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
+Then, let define
+	$$V_{\mu} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \mu}$$
+	and the Gasia-Haiman module associated to $\mu$ is the smallest subspace containing $V_{\mu}$ and closed under differentiation for both sets of variables. \\
 
@@
 The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
-Like before, we consider the smallest subspace containing a certain determinant and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
-The determinant used in this case is defined as follow.
 
-	Let $\lambda$ be a partition of $n$, we also denote $\lambda$ the Ferrer's diagram associated to the partition $\lambda$ and each cell of $\lambda$ is given by the coordinates $(a,b)$ of its bottom left corner.
+	Let $\lambda$ be a partition of $n$, note $(a,b)$ the Cartesian coordinates its cells.
 Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
 	For example, the partition $21$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{21} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+
+	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
+We denote this space by $\mathcal{E}_{\lambda}$.
 \\
@@
 
-	\begin{definition} \pauline{find the right place for Steenrod op}
-		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by
-		$$St_{x_a}^k = \sum_{i=1}^{n} x_{ai} \partial_{x_{ai}}^k$$
-		where $x_a$ is a set of variables of $X$. 
-	\end{definition}
-
-	Only the Steenrod operators for $k=2$ and $k=3$ are necessary since the other operators can be obtained from the two first ones.
-For example, $St_{x_a}^4 = St_{x_a}^3St_{x_a}^2 - St_{x_a}^2St_{x_a}^3$.
-
-	Note that $St_{x_a}^k = P_{x_a,x_a}^k$ but we distinguish the two families of operators because they play different roles.
-
 	\section{Strategies}
 
-	\subsection{Computing in the space of harmonic polynomials}
+	\subsection{Computing in the space of harmonic polynomials using polarization}
 
-	We first need to compute in a quotient by an ideal, $P / I_n$ where $I_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. 
+	We first need to compute in a quotient by an ideal, $R / \mathcal{I}_n$ where $\mathcal{I}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. 
 	A standard approach would be to compute a Gröbner basis of this ideal.
@@
 
-	Solving those differential equations would not be that tractable either. So instead we used operators (partial derivatives and polarization operators).
-
-	\subsection{Polarization: diagonal harmonics from harmonics}
-
-	\begin{definition}
-		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
-		$$P_{x_a,x_b}^k = \sum_{i=1}^{n} x_{bi} \partial_{x_{ai}}^k$$
-		where $x_a$ and $x_b$ are two sets of variables of $X$. 
-	\end{definition}
-
-	\begin{theorem}
-		Multisymmetric polynomials are obtained by polarization of symmetric polynomials in the first set of variables.
-	\end{theorem}
-
-	\begin{theorem} \label{DiagHarm}
-		Diagonal harmonic polynomials are obtained by polarization of harmonic polynomials in the first set of variables.
-	\end{theorem}
-
-	Therorem \ref{DiagHarm} has been proven for two sets of variables.
-It is not proven yet for more than two sets of variables but it has been verified by calculation for a large number of sets of variables so we assume it to be true since we will never reach that number of sets in our case.
-
-	The space of harmonic polynomials $\harmonics_n$ itself can be constructed, for example, as the subspace spanned by the Vandermonde determinant under differentiation. \\
+	Solving those differential equations would not be that tractable either. So instead we used operators, partial derivatives and polarization operators defined in the previous section. \\
 
@@
 
+	\begin{definition} \pauline{find the right place for Steenrod op}
+		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by
+		$$St_{x_a}^k = \sum_{i=1}^{n} x_{ai} \partial_{x_{ai}}^k$$
+		where $x_a$ is a set of variables of $X$. 
+	\end{definition}
+
+	Only the Steenrod operators for $k=2$ and $k=3$ are necessary since the other operators can be obtained from the two first ones.
+For example, $St_{x_a}^4 = St_{x_a}^3St_{x_a}^2 - St_{x_a}^2St_{x_a}^3$.
+
+	Note that $St_{x_a}^k = P_{x_a,x_a}^k$ but we distinguish the two families of operators because they play different roles.
+
 \bibliographystyle{plain}

### 2019-05-14 diagonal_polynomial_ring.py
Copy all methods in isomorphic_object. Doctest fails.

@@ -3,6 +3,7 @@
 
 import functools
 
+from sage.misc.cachefunc import cached_method, cached_function
 from sage.structure.parent import Parent
 from sage.structure.unique_representation import UniqueRepresentation
 from sage.structure.sage_object import load
@@ -18,9 +19,6 @@ from sage.categories.cartesian_product import cartesian_product
 from sage.functions.other import binomial
 from sage.combinat.words.word import Word
 
-from diagram import *
-from subspace import *
-from young_idempotent import *
 from polynomial_derivative import *
 
 from utilities import *

### 2019-05-14 isomorphic_object.py

@@ -3,6 +3,7 @@
 
 import functools
 
+from sage.misc.cachefunc import cached_method, cached_function
 from sage.structure.parent import Parent
 from sage.structure.unique_representation import UniqueRepresentation
 from sage.structure.sage_object import load
@@ -19,9 +20,6 @@ from sage.categories.cartesian_product import cartesian_product
 from sage.functions.other import binomial
 from sage.combinat.words.word import Word
 
-from diagram import *
-from subspace import *
-from young_idempotent import *
 from polynomial_derivative import *
 
 from utilities import *
@@ -69,105 +67,36 @@ class DiagonalPolynomialRing(IsomorphicObject):
 
         sage: P = DiagonalPolynomialRing(QQ, 4, 3)
         sage: P
-        Diagonal polynomial ring with 3 rows of 4 variables over Rational Field
+        The image by some isomorphism of Multivariate Polynomial Ring in x00, x01, x02, x03, x10, x11, x12, x13, x20, x21, x22, x23 over Rational Field
+
 
         sage: P = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
         sage: P
-        Diagonal polynomial ring with 3 rows of 4 variables and 1 row(s) of inert variables over Rational Field
+        The image by some isomorphism of Multivariate Polynomial Ring in x00, x01, x02, x03, x10, x11, x12, x13, x20, x21, x22, x23, theta00, theta01, theta02, theta03 over Rational Field
 
     """
     def __init__(self, R, n, r, inert=0):
         names = ["x%s%s"%(i,j) for i in range(r) for j in range(n)]+["theta%s%s"%(i,j) for i in range(inert) for j in range(n)]
         P = PolynomialRing(R, n*(r+inert), names)
-        IsomorphicObject.__init__(self, P, Algebras())
-        vars = P.gens()
+        IsomorphicObject.__init__(self, P, Algebras(R))
+        self._n = n
+        self._r = r
+        self._inert = inert
         self._P = P
         self._R = R
         self._Q = PolynomialRing(QQ,'q',r)
         self._grading_set = cartesian_product([ZZ for i in range(r)])
         self._hilbert_parent = PolynomialRing(ZZ, r, 'q')
-        #dans fonctions direct
-        self._vars = matrix([[vars[i*n+j] for j in range(n)] for i in range(r+inert)])
-        self._X = matrix([[vars[i*n+j] for j in range(n)] for i in range(r)])
[…]

### 2019-05-15 isomorphic_object.py
Correct some fail doctests

@@ -88,7 +88,6 @@ class DiagonalPolynomialRing(IsomorphicObject):
         self._grading_set = cartesian_product([ZZ for i in range(r)])
         self._hilbert_parent = PolynomialRing(ZZ, r, 'q')
         
-    
     def Q_gens(self):
         """
         sage: D = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
@@ -233,11 +232,10 @@ class DiagonalPolynomialRing(IsomorphicObject):
             ....:     assert P.random_monomial(D).multidegree() == D
         """
         X = self.algebra_generators()
-        X_by_rows = [Set(list(row)) for row in X]
+        X_by_rows = [Set(list(X[i,j] for j in range(X.ncols()))) for i in range(X.nrows())]
         return prod( X_by_rows[i].random_element()
                      for i in range(len(D))
                      for j in range(D[i]) )
-                     
                      
     def random_element(self, D, l=10):
         """
@@ -315,10 +313,9 @@ class DiagonalPolynomialRing(IsomorphicObject):
             return self.parent()._grading_set([sum(v[n*i+j] for j in range(n))
                                       for i in range(r)])
                                       
-                                      
-        def derivative(self, x, k):
+        def derivative(self, *args):
             p = self.parent()._P(self)
-            return self.parent()(p.derivative(x, k))
+            return self.parent()(p.derivative(*args))
             
         def apply_permutation(self):
             d = self.multidegree()
@@ -480,7 +477,6 @@ class DiagonalPolynomialRing(IsomorphicObject):
                 result = result.apply_permutation()
             return result
             
-            
         def multi_polarization(self, D, i2):
             """
             Return the multi polarization `P_{D,i_2}. p` of `p`.
@@ -614,6 +610,7 @@ class DiagonalPolynomialRing(IsomorphicObject):
             # Goal: produce pjs such that:
             # - p = \sum_j e^j pjs[j]
             # - HW_{≤ i1, i2}(q) for q in pjs
+            polarization = self.parent().Element.polarization
[…]

### 2019-05-16 diagonal_polynomial_ring_old.py
Old version of this file, without isomorphisms

@@ -1,0 +1,941 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import functools
+
+from sage.misc.cachefunc import cached_method, cached_function
+from sage.structure.parent import Parent
+from sage.structure.unique_representation import UniqueRepresentation
+from sage.structure.sage_object import load
+
+from sage.parallel.decorate import parallel
+from sage.misc.misc_c import prod
+
+from sage.rings.polynomial.polynomial_ring_constructor import PolynomialRing
+from sage.rings.integer_ring import ZZ
+from sage.rings.rational_field import QQ
+from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
+from sage.categories.algebras import Algebras
+from sage.categories.cartesian_product import cartesian_product
+from sage.functions.other import binomial
+from sage.combinat.words.word import Word
+
+from isomorphic_object import *
+from polynomial_derivative import *
+
+from utilities import *
+from antisymmetric_utilities import *
+
+##############################################################################
+# Polynomial ring with diagonal action
+##############################################################################
+
+class DiagonalPolynomialRing(UniqueRepresentation, Parent):
+    """
+    The ring of diagonal polynomials in $n \times r$ variables and $n \times k$ inert variables.
+    In order to distinguish the inert variables among the others, they are named `theta_{i,j}`
+
+    EXAMPLES::
+
+        sage: P = DiagonalPolynomialRing(QQ, 4, 3)
+        sage: P
+        Diagonal polynomial ring with 3 rows of 4 variables over Rational Field
+
+        sage: P = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
+        sage: P
+        Diagonal polynomial ring with 3 rows of 4 variables and 1 row(s) of inert variables over Rational Field
+
+    """
+    def __init__(self, R, n, r, inert=0):
+        names = ["x%s%s"%(i,j) for i in range(r) for j in range(n)]+["theta%s%s"%(i,j) for i in range(inert) for j in range(n)]
+        P = PolynomialRing(R, n*(r+inert), names)
+        self._n = n
+        self._r = r
+        self._inert = inert
+        vars = P.gens()
+        self._P = P
+        self._R = R
+        self._Q = PolynomialRing(QQ,'q',r)
[…]

### 2019-05-16 diagonal_polynomial_ring.py
Now inherits from isomorphic_object

@@ -4,8 +4,6 @@
 import functools
 
 from sage.misc.cachefunc import cached_method, cached_function
-from sage.structure.parent import Parent
-from sage.structure.unique_representation import UniqueRepresentation
 from sage.structure.sage_object import load
 
 from sage.parallel.decorate import parallel
@@ -19,6 +17,7 @@ from sage.categories.cartesian_product import cartesian_product
 from sage.functions.other import binomial
 from sage.combinat.words.word import Word
 
+from isomorphic_object import *
 from polynomial_derivative import *
 
 from utilities import *
@@ -28,7 +27,7 @@ from antisymmetric_utilities import *
 # Polynomial ring with diagonal action
 ##############################################################################
 
-class DiagonalPolynomialRing(UniqueRepresentation, Parent):
+class DiagonalPolynomialRing(IsomorphicObject):
     """
     The ring of diagonal polynomials in $n \times r$ variables and $n \times k$ inert variables.
     In order to distinguish the inert variables among the others, they are named `theta_{i,j}`
@@ -37,62 +36,56 @@ class DiagonalPolynomialRing(UniqueRepresentation, Parent):
 
         sage: P = DiagonalPolynomialRing(QQ, 4, 3)
         sage: P
-        Diagonal polynomial ring with 3 rows of 4 variables over Rational Field
+        The image by some isomorphism of Multivariate Polynomial Ring in x00, x01, x02, x03, x10, x11, x12, x13, x20, x21, x22, x23 over Rational Field
+
 
         sage: P = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
         sage: P
-        Diagonal polynomial ring with 3 rows of 4 variables and 1 row(s) of inert variables over Rational Field
+        The image by some isomorphism of Multivariate Polynomial Ring in x00, x01, x02, x03, x10, x11, x12, x13, x20, x21, x22, x23, theta00, theta01, theta02, theta03 over Rational Field
 
     """
     def __init__(self, R, n, r, inert=0):
         names = ["x%s%s"%(i,j) for i in range(r) for j in range(n)]+["theta%s%s"%(i,j) for i in range(inert) for j in range(n)]
         P = PolynomialRing(R, n*(r+inert), names)
+        IsomorphicObject.__init__(self, P, Algebras(R))
         self._n = n
         self._r = r
         self._inert = inert
-        vars = P.gens()
         self._P = P
         self._R = R
[…]

### 2019-05-16 isomorphic_object.py
Correct some doctests

@@ -1,29 +1,32 @@
 #!/usr/bin/env python
 # -*- coding: utf-8 -*-
 
-import functools
+from sage.structure.unique_representation import UniqueRepresentation
+from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
+from sage.structure.element_wrapper import ElementWrapper
 
+
+# To delete after remove DiagonalPolynomialRing
+import functools
 from sage.misc.cachefunc import cached_method, cached_function
 from sage.structure.parent import Parent
-from sage.structure.unique_representation import UniqueRepresentation
-from sage.structure.sage_object import load
 
+from sage.structure.sage_object import load
 from sage.parallel.decorate import parallel
 from sage.misc.misc_c import prod
 
 from sage.rings.polynomial.polynomial_ring_constructor import PolynomialRing
 from sage.rings.integer_ring import ZZ
 from sage.rings.rational_field import QQ
-from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
 from sage.categories.algebras import Algebras
 from sage.categories.cartesian_product import cartesian_product
 from sage.functions.other import binomial
 from sage.combinat.words.word import Word
 
 from polynomial_derivative import *
-
 from utilities import *
 from antisymmetric_utilities import *
+
 
 
 

### 2019-05-16 diagonal_polynomial_ring.py
Correct all bugs due to IsomorphicObject

@@ -14,7 +14,6 @@ from sage.rings.integer_ring import ZZ
 from sage.rings.rational_field import QQ
 from sage.categories.algebras import Algebras
 from sage.categories.cartesian_product import cartesian_product
-from sage.functions.other import binomial
 from sage.combinat.words.word import Word
 
 from isomorphic_object import *
@@ -83,8 +82,8 @@ class DiagonalPolynomialRing(IsomorphicObject):
         """
         return self._inert
         
-    def inject_variables(self):
-        self._P.inject_variables()
+    def variable_names(self):
+        return self._P.variable_names()
         
     def algebra_generators(self):
         """
@@ -345,7 +344,7 @@ class DiagonalPolynomialRing(IsomorphicObject):
             EXAMPLES::
                 sage: P = DiagonalPolynomialRing(QQ, 3, 4)
                 sage: X = P.algebra_generators()
-                sage: p = X[0,0]*X[1,1]^2 + (-1)*X[0,1]^2*X[1,0] # PB -
+                sage: p = X[0,0]*X[1,1]^2 - X[0,1]^2*X[1,0] # PB -
                 sage: p
                 -x01^2*x10 + x00*x11^2
                 sage: p.higher_polarization(0, 1, 1, 1)
@@ -382,7 +381,7 @@ class DiagonalPolynomialRing(IsomorphicObject):
             EXAMPLES::
                 sage: P = DiagonalPolynomialRing(QQ, 3, 1)
                 sage: x = P.algebra_generators()
-                sage: v = (-1)*x[0,0]^3*x[0,1] + x[0,0]*x[0,1]^3 + x[0,0]^3*x[0,2] + (-1)*x[0,1]^3*x[0,2] + (-1)*x[0,0]*x[0,2]^3 + x[0,1]*x[0,2]^3; v
+                sage: v = -x[0,0]^3*x[0,1] + x[0,0]*x[0,1]^3 + x[0,0]^3*x[0,2] - x[0,1]^3*x[0,2] - x[0,0]*x[0,2]^3 + x[0,1]*x[0,2]^3; v
                 -x00^3*x01 + x00*x01^3 + x00^3*x02 - x01^3*x02 - x00*x02^3 + x01*x02^3
[…]

### 2019-05-16 isomorphic_object.py

@@ -4,30 +4,10 @@
 from sage.structure.unique_representation import UniqueRepresentation
 from sage.categories.isomorphic_objects import IsomorphicObjectsCategory
 from sage.structure.element_wrapper import ElementWrapper
-
-
-# To delete after remove DiagonalPolynomialRing
-import functools
-from sage.misc.cachefunc import cached_method, cached_function
-from sage.structure.parent import Parent
-
-from sage.structure.sage_object import load
-from sage.parallel.decorate import parallel
-from sage.misc.misc_c import prod
-
-from sage.rings.polynomial.polynomial_ring_constructor import PolynomialRing
-from sage.rings.integer_ring import ZZ
-from sage.rings.rational_field import QQ
+from sage.categories.homset import Hom
+from sage.categories.morphism import SetMorphism
 from sage.categories.algebras import Algebras
-from sage.categories.cartesian_product import cartesian_product
-from sage.functions.other import binomial
-from sage.combinat.words.word import Word
-
-from polynomial_derivative import *
-from utilities import *
-from antisymmetric_utilities import *
-
-
+from sage.structure.parent import Parent
 
 
 # Stuff here everything currently missing in SageMath about isomorphic algebras
@@ -37,6 +17,20 @@ class Algebras_IsomorphicObjects(IsomorphicObjectsCategory):
             return self.retract(x.lift() + y.lift())
         def gens(self):
             return [self.retract(g) for g in self.ambient().gens()]
+        def is_field(self):
+            return self._ambient.is_field()
+        def is_integral_domain(self):
+            return self._ambient.is_integral_domain()
+        def is_commutative(self):
+            return self._ambient.is_commutative()
+            
+    class ElementMethods:
+        def _sub_(x, y):
+            return x.parent().retract(x.lift() - y.lift())
+        def _neg_(self):
+            return self.parent().retract(-self.lift())
+        def _div_(x, y):
+            return x.parent().retract(x.lift()/y.lift())
 
 Algebras.IsomorphicObjects = Algebras_IsomorphicObjects
 
@@ -54,886 +48,12 @@ class IsomorphicObject(UniqueRepresentation, Parent):
         Parent.__init__(self, category=category.IsomorphicObjects())
         # Bricolage
         self._remove_from_coerce_cache(ambient)
[…]

### 2019-05-16 polynomial_derivative.py

@@ -3,10 +3,10 @@
 
 from sage.misc.misc_c import prod
 from sage.functions.other import factorial
+from sage.functions.other import binomial
 
 from sage.structure.element import have_same_parent
 from matrix_of_vectors import items_of_vector
-from diagonal_polynomial_ring import *
 
 ##############################################################################
 # Polynomials as differential operators

### 2019-05-31 compute_character.py
Reactive persist

@@ -708,8 +708,8 @@ def dimension(f, n):
 # Main function
 ############################################################################## 
 
-#@persist(hash=lambda k: 'character_%s_%s' % (k[0][1].size(),''.join(str(i) for i in k[0][1])),
-#        funcname='character')
+@persist(hash=lambda k: 'character_%s_%s' % (k[0][1].size(),''.join(str(i) for i in k[0][1])),
+        funcname='character')
 def compute_character(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
     """
     Given a diagram `mu`, compute the character associated to this diagram.

### 2019-06-03 article/article.tex

@@
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 	Therorem \ref{DiagHarm} has been proven for two sets of variables.
-It is not proven yet for more than two sets of variables but it has been verified by calculation for a large number of sets of variables so we assume it to be true since we will never reach that number of sets in our case.
+It is not proven yet for more than two sets of variables but it has been verified by calculation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
 \\
@@
 
-	The polarization operators, ie the action of $\GLr$, commute with the action of $\Sn$.
-Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n,r}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
-	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
+	First of all, we need an efficient way to compute the representations of $\Sn$.
+To do that, we will use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ and their multiplicities.
+	The isotypic projector we use is called the Young symmetrizer and is define as follow.
 
-	In practice, first we compute $\harmonics_{n}$ and decompose it into isotypic components using the Young symmetrizer.
-Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ from those of $\harmonics_{n}$.
-\\
-
-	To define the Young symmetrizer, we first need to define two elements of the symmetric group algebra $\CC \Sn$.
-Let $P_{\lambda}$ be the subgroup of $\Sn$ of all row preserving permutations and $Q_{\lambda}$ the subgroup of the columns preserving permutations.
+	We first need to define two elements of the symmetric group algebra $\CC \Sn$.
+Let $P_{\lambda}$ be the subgroup of $\Sn$ of all row preserving permutations of $\lambda$ and $Q_{\lambda}$ the subgroup of the columns preserving permutations of $\lambda$.
 Then we have $a_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sigma$ and  $b_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sgn(\sigma) \sigma$.
@@
 	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\harmonics_{n}$ gives representatives of the isotypic components of $\Sn$.
-\pauline{Do we need to prove explicitly commutation with symmetric operators?}
+\pauline{Do we need to prove explicitly commutation with symmetric operators?}  \\
 
-	As mentioned above, since the action of $\GLr$ and $\Sn$ commutes, at this stage we only have to apply the polarization operators on each isotypic component independently to be able to compute the bicharacter.
+	The action of $\GLr$ commutes with the action of $\Sn$.
+Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n,r}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
+	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
+
+	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ and decompose it into isotypic components using the Young symmetrizer.
+Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ from those of $\harmonics_{n}$.
 \\
@@
 
-	To conclude, it is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$
+	To conclude, it is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$.
 
@@
 
-	But that's mostly because they are antisymmetric w.r.t.
+	But that's mostly because they are anti-symmetric w.r.t.
 a large column stabilizer $S_P$.
@@
 
+	Inside isotypic component, polynomials are anti-symmetric with respect to the type $\lambda$ of the component.
+This is due to the fact that applying the young symmetrizer $y_{\lambda}$ firt symmetrize the polynomial with respect to the row preserving permutations of $\lambda$ and then anti-symmetrize the result with respect to the column preserving permutations of $\lambda$.
+
+	Thus it is sufficient to keep only a reduced form of the polynomials.
+
+	\begin{example}
+		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $111$.
+		Reduce form : $x_1\theta_2$. \\
+		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $21$. 
+		Reduce form : $-\theta_1$ 
+	\end{example}
+
 	This trick was already used by François for the polarizations of the Vandermonde (the diagram space). Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
 
-	**Gain**: in theory up to $n!$. In practice between one and two orders of magnitude due to the overhead of straightening monomials.
+	\textbf{Gain:} in theory up to $n!$. In practice between one and two orders of magnitude due to the overhead of straightening monomials.
 
@@
 
-	**Gain**: an order of magnitude; below are the total dimension of each $\harmonics_5^\lambda$ and its restriction to homogeneous components of decreasing multidegree:
+	\begin{example}
+		$x_1^2 - 2x_1x_2 + 2x_2x_3 - x_3^2 \in \mathcal{H}_{3}$ so $y_1^2 - 2y_1y_2 + 2y_2y_3 - y_3^2 \in \mathcal{H}_{3}$
+
+		$-2x_{1} y_{1} y_{2} + x_{1} y_{2}^{2} \in \mathcal{H}_{3}$ so $-2y_{1} x_{1} x_{2} + y_{1} x_{2}^{2} \in \mathcal{H}_{3}$
+	\end{example}
+
+	\textbf{Gain:} an order of magnitude; below are the total dimension of each $\harmonics_5^\lambda$ and its restriction to homogeneous components of decreasing multidegree.
 
@@
 
-	**Current gain:** another order of magnitude; down from 3 days to 45 minutes for $\harmonics_5^{1^6}$
+	\textbf{Current gain:} another order of magnitude; down from 3 days to 45 minutes for $\harmonics_5^{1^6}$
 
-	**Potential gain:** another order of magnitude, both in time and memory:
+	\textbf{Potential gain:} another order of magnitude, both in time and memory.
 

### 2019-06-03 setup.py
Updated setup.py and Dockerfile
- Add dependency on pypersist
- Install as Python package

@@ -50,7 +50,7 @@ setup(
                ],
     cmdclass = {'test': SageTest}, # adding a special setup command for tests
     setup_requires   = ['sage-package'],
-    install_requires = ['sage-package', 'sphinx'],
+    install_requires = ['sage-package', 'sphinx', 'tqdm', 'RISE', 'pypersist'],
 
     ext_modules=cythonize([
         Extension('utilities',

### 2019-06-03 compute_character.py
Workaround #25491

@@ -10,7 +10,9 @@ from add_degree import*
 from diagram import*
 
 SymmetricFunctions(QQ).inject_shorthands(verbose=False)
-
+# Workaround #25491 which prevents early unpickling of tensor products
+# of symmetric functions
+HopfAlgebrasWithBasis.TensorProducts
 
 ##############################################################################
 # Vandermonde like determinant
@@ -709,7 +711,7 @@ def dimension(f, n):
 ############################################################################## 
 
 @persist(hash=lambda k: 'character_%s_%s' % (k[0][1].size(),''.join(str(i) for i in k[0][1])),
-        funcname='character')
+        funcname='truc')
 def compute_character(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
     """
     Given a diagram `mu`, compute the character associated to this diagram.
@@ -733,6 +735,8 @@ def compute_character(mu, use_antisymmetry=True, row_symmetry="permutation", par
         s[] # s[1, 1, 1]
 
     """
+    print(mu)
+    return tensor([s[mu], s[mu]])
     n = Integer(mu.size())
     # Determinant computation
     v = vandermonde(mu)

### 2019-06-06 article/article.tex
Correct typos

@@
 	We first need to define two elements of the symmetric group algebra $\CC \Sn$.
-Let $P_{\lambda}$ be the subgroup of $\Sn$ of all row preserving permutations of $\lambda$ and $Q_{\lambda}$ the subgroup of the columns preserving permutations of $\lambda$.
-Then we have $a_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sigma$ and  $b_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sgn(\sigma) \sigma$.
-Finally, the Young symmetrizer is the element $$c_{\lambda} = a_{\lambda} b_{\lambda}.$$
+Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$.
+Then we have $a_{\mu} = \sum_{\sigma \in P_{\mu}} \sigma$ and  $b_{\mu} = \sum_{\sigma \in P_{\mu}} \sgn(\sigma) \sigma$.
+Finally, the Young symmetrizer is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$
 
@@
 
-	Specht polynomials tend to be big: in $6$ variables, the Vandermonde determinant has $6!=720$ monomials.
+	One thing that can slow down the computation is that the polynomials we are working with tend to be big.
+For example, in $6$ variables, the Vandermonde determinant has $6!=720$ monomials.
+This means that we need a lot of space to store them and it takes time when we want to apply operators on them.
 
-	But that's mostly because they are anti-symmetric w.r.t.
-a large column stabilizer $S_P$.
-It's therefore sufficient to keep one representative monomial per $S_P$ orbit (and do some appropriate straightening whenever a new monomial is created).
+	However, for all $p \in \mathcal{E}_\lambda$, p is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $p$.
+Indeed, when projecting $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes $p$ symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes $p.a_\mu$ anti-symmetric with respect to the column preserving permutations of $\mu$.
+	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{how do we guarantee one monomial is enough?} (and do some appropriate straightening whenever a new monomial is created).
+We chose to keep the smallest representative monomial in lexicographic order.
+\\
 
-	Inside isotypic component, polynomials are anti-symmetric with respect to the type $\lambda$ of the component.
-This is due to the fact that applying the young symmetrizer $y_{\lambda}$ firt symmetrize the polynomial with respect to the row preserving permutations of $\lambda$ and then anti-symmetrize the result with respect to the column preserving permutations of $\lambda$.
-
-	Thus it is sufficient to keep only a reduced form of the polynomials.
+	Thus keeping reduced form of the polynomials reduce space complexity and time complexity when applying operators.
+Note that each time an operator is applied to an element, the reduced form of this element is computed again.
 

### 2019-06-07 compute_character.py
Change persist + add latex output for character

@@ -636,7 +636,7 @@ def character_quotient(M, N, n, r, left_basis=s, right_basis=s):
 # Tools on character
 ##############################################################################      
 
-def factorise(f, n):
+def factorize(f, n=0):
     """
     Return the factorization of the tensor product `f` w.r.t the right symmetric
     functions. The right symmetric functions have their supports in the partitions
@@ -647,20 +647,18 @@ def factorise(f, n):
     - ``n`` -- an Integer
     
     EXAMPLES::
-    sage: factorise(compute_character(Partition([3,1])), 4)
-    [3, 1]
-    <html><script type="math/tex">\newcommand{\Bold}[1]{\mathbf{#1}}s_{}</script></html>
-    [1, 1, 1, 1]
-    <html><script type="math/tex">\newcommand{\Bold}[1]{\mathbf{#1}}s_{1,1} + s_{3}</script></html>
-    [2, 2]
-    <html><script type="math/tex">\newcommand{\Bold}[1]{\mathbf{#1}}s_{1}</script></html>
-    [2, 1, 1]
-    <html><script type="math/tex">\newcommand{\Bold}[1]{\mathbf{#1}}s_{1} + s_{2}</script></html>
+    sage: factorize(compute_character(Partition([3,1])), 4)
+    [([3, 1], s[]),
+     ([1, 1, 1, 1], s[1, 1] + s[3]),
+     ([2, 2], s[1]),
+     ([2, 1, 1], s[1] + s[2]),
+     ([4], 0)]
 
-
+    TODO : Delete n and correct code and worksheets 
     """
     SymmetricFunctions(QQ).s()
     supp = sorted(f.support())
+    n = f.support().pop()[1].size()
     result = {}
     res = []
     for mu in Partitions(n):
@@ -669,10 +667,42 @@ def factorise(f, n):
             if b == mu :
                 result[mu] += [(a,c)]
     result2 = [(mu,sum(c*s(nu) for (nu,c) in result[mu])) for mu in result.keys()]
-    for a, b in result2:
-        if b!=0:
-            print a
-            show(b)
+    #for a, b in result2:
+        #if b!=0:
+            #print a
+            #show(b)
+    return result2
+    
+def latex_output_character(f):
+    """
+    Return the latex code of the character `f`. 
+    
+    INPUT:
+    - ``f`` -- a sum of tensor products
+    
+    EXAMPLES:: 
+        sage: for mu in Partitions(3):
+        ....:     print(latex_output_character(compute_character(mu)))
[…]

### 2019-06-07 diagram.py
Change print function name

@@ -87,12 +87,12 @@ class Diagram():
         
         return max([c[1] for c in self.cells()])
         
-    def print_diagram(self):
+    def draw(self):
         """
         Print the diagram. 
         
         EXAMPLES ::
-            sage: Diagram([(0,0),(1,1),(2,2)]).print_diagram()
+            sage: Diagram([(0,0),(1,1),(2,2)]).print()
                  _
                _|_|
              _|_| 

### 2019-06-07 compute_character.py
Correct small bugs

@@ -666,7 +666,7 @@ def factorize(f, n=0):
         for (a, b), c in zip(supp, f.coefficients()):
             if b == mu :
                 result[mu] += [(a,c)]
-    result2 = [(mu,sum(c*s(nu) for (nu,c) in result[mu])) for mu in result.keys()]
+    result2 = [(tuple(mu),sum(c*s(nu) for (nu,c) in result[mu])) for mu in result.keys()]
     #for a, b in result2:
         #if b!=0:
             #print a

### 2019-06-10 compute_character.py
Allow polarisation of non projected subspaces

@@ -373,7 +373,6 @@ def add_degrees_symmetric(gen_deg,op_deg):
     d = D(gen_deg[0])+D(op_deg)
     return D(sorted(d, reverse=True)), gen_deg[1]
     
-    
 ##############################################################################
 # Polarization Space
 ##############################################################################
@@ -459,7 +458,11 @@ def PolarizedSpace(S, operators, add_degrees=add_degrees_isotypic):
         else :
             P2 = DiagonalPolynomialRing(P1._R, P1.ncols(), r , P1.ninert())
             for key, value in basis.iteritems():
-                d = (D((key[0][0] if i==0 else 0 for i in range(0,r))), key[1])
+                if isinstance(key[0], Integer):
+                    d = (D((key[0] if i==0 else 0 for i in range(0,r))))
+                    add_degrees = add_degree
+                else:
+                    d = (D((key[0][0] if i==0 else 0 for i in range(0,r))), key[1])
                 generators[d] = tuple(P2(b) for b in value)
         return Subspace(generators, operators, add_degrees=add_degrees)
     

### 2019-06-10 article/article.tex
Add examples using sagetex and young tableaux.

@@
 \usepackage{xargs}
-%\usepackage{sagetex}
+\usepackage{sagetex}
 \usepackage{hyperref}
@@
 \newcommand{\CC}{\mathbb{C}}
+\newcommand{\Sym}[1]{\mathbb{S}_{#1}}
 
@@
 
+%SageTex
+\renewcommand{\sagecommandlinetextoutput}{True} % False = output in Latex 
+\lstdefinestyle{SageInput}{
+	style=DefaultSageInput,
+	basicstyle=\small\normalfont\ttfamily,
+	numbers=none,
+ 	breaklines=true, }
+\lstdefinestyle{SageOutput}{style=DefaultSageOutput}
+
 %%- 1 ère page
@@
 	\section{Introduction}
-	This package was developped at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
+	This package was developed at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
 The main achievement is a calculation of this character for $n=6$ \pauline{+ some cases for $n=7$ ?} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
@@
 	$$(x_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
-	and we denote by $X_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
+	and we denote by $\bm{x}_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
+We use the convention that bold letters stand for sets of variables and light letters stand for the variables themselves.
 
 	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of $\GLr$ by diagonal action on the rows.
-The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions.
-The co-invariant ring $R_{\Sn}$ is the quotient of $P$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
+The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$.
+The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
 It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.
@@
 The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$ character.
-It's thus equivalent to consider the $\GLr \times \Sn$ bicharacter or the $\Sn$ multigraded character of $P_{\Sn}$.
+It's thus equivalent to consider the $\GLr \times \Sn$ bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
 
 	When $k=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
-	When $k=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($=16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
+	When $k=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
 
-	Throughout this notebook, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur symmetric functions. \\
+	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur symmetric functions. \\
 
@@
 	\begin{definition}
-		Let $f \in \QQ[X]$, $f$ is \emph{harmonic} if and only if
+		Let $f \in R$, $f$ is \emph{harmonic} if and only if
 		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0 $$
@@
 
+	For example the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic.
+
 	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$ is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
-It is also a realization of the coinvariants of the symmetric group: $\QQ[X]\, /\, \langle Sym(X)^+ \rangle$ \pauline{$= \QQ[X] / \mathcal{I}_n$} and a graded regular representation of $\Sn$.
+It is also a realization of the coinvariants of the symmetric group: $R\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.
 
-	As an example, $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$.
+	For example, $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$.
 
-	Note that the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic.
-It is also easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$.
-From that we have another way to define $\harmonics_{n}$, see (\cite{Haiman2002} and \cite{Bergeron2009}) for more details.
+	It is easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$.
+Using that, one can define $\harmonics_{n}$ directly with  partial derivatives instead of seeing them as solutions of a system of partial differential equations as stated in the following theorem.
+See \cite{Haiman2002} and \cite{Bergeron2009} for more details.
 
@@
 
-	For example, take $r=3$ and denote $x, y$ and $z$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
+	For example, take $r=3$ and denote $\bm{x}, \bm{y}$ and $\bm{z}$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
 
-	The space of \emph{diagonal harmonic polynomials} $\harmonics_{n,r}$ is the joint kernel of the $(D_\alpha)_\alpha$. Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
+	The space of \emph{diagonal harmonic polynomials} $\harmonics_{n,r}$ is the joint kernel of the differential operators $(D_\alpha)_\alpha$.
+Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
 
-	The previous definition means that the diagonal harmonic polynomials are solutions of differential equations systems. 
-	As for the harmonics, we have an alternative way to obtain $\harmonics_{n,r}$.
+	As for the harmonics, we have an alternative way to obtain $\harmonics_{n,r}$ directly using operators.
 
 	\begin{definition}
-		The \emph{polarisation operator} $P_{x_a,x_b}^k$ is given by
-		$$P_{x_a,x_b}^k = \sum_{i=1}^{n} x_{bi} \partial_{x_{ai}}^k$$
-		where $x_a$ and $x_b$ are two sets of variables of $X$. 
+		The \emph{polarisation operator} $P_{x,y}^k$ is given by
+		$$P_{x,y}^k = \sum_{i=1}^{n} y \partial_{x}^k$$
+		where $\bm{x}$ and $\bm{y}$ are two sets of variables of $X$. 
 	\end{definition}
 
-	For $k=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$. Moreover, we have the following useful theorems.
+	For $k=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$.
 
@@
 	Therorem \ref{DiagHarm} has been proven for two sets of variables.
-It is not proven yet for more than two sets of variables but it has been verified by calculation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
+It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
 \\
@@
 
-	Let $X=(x_1, x_2, \dots, x_n)$ and $Y=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\mu$ be a partition of $n$.
+	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\mu$ be a partition of $n$.
 We also denote $\mu$ the Ferrer's diagram (in French notation) associated to the partition $\mu$ and each cell of $\mu$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
@@
 Bergeron recently introduced another generalization of the diagonal harmonics, with inert variables.
-We add a new row $\theta = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$.
+We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$.
 The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
 
-	Let $\lambda$ be a partition of $n$, note $(a,b)$ the Cartesian coordinates its cells.
+	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates its cells.
 Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
@@
 We denote this space by $\mathcal{E}_{\lambda}$.
+The diagonal harmonics $\harmonics_{n,r}$ are thus a special case of $\mathcal{E}_{\lambda}$ for $\lambda = n$.
 \\
@@
 
-	We first need to compute in a quotient by an ideal, $R / \mathcal{I}_n$ where $\mathcal{I}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. 
+	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. 
 	A standard approach would be to compute a Gröbner basis of this ideal.
@@
 	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_{n,r}$ of diagonal harmonic polynomials.
-	This is the space of those polynomials that satisfy the equations given by the multisymmetric \pauline{multi symmetric vs diagonal symmetric ?} functions seen as differential operators.
+	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
 
@@
 	In practice, we implemented a general purpose utility in Sage, \texttt{Subspace(vectors, operators)} that computes the smallest subspace of a vector space which contains the given vectors and is stable under the action of the given linear operators.
-	\nicolas{put an example here}
+
+	\begin{example} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$.
+		\begin{sagesilent}
+			load("../subspace.py")
+		\end{sagesilent}
+		\begin{sagecommandline}
+			sage: R = QQ['x1,x2,x3']
+			sage: M = matrix.vandermonde(R.gens(), R)
+			sage: M
+			sage: derivatives = [attrcall('derivative', x) for x in R.gens()]
+			sage: H_3 = Subspace([M.determinant()], derivatives)
+			sage: H_3.basis()
+			sage: H_3.dimension()
+		\end{sagecommandline}	
+	\end{example}
 
@@
 
-	Once a basis of $\harmonics_{n,r}$ is constructed, there still remains to recover its bicharacter.
+	The exact same strategy works to build the subspace generated by the Vandermonde $V_{\lambda}$ and its partial derivatives.
+
+	Once a basis of $\harmonics_{n,r}$ or $\mathcal{E}_\lambda$ is constructed, there still remains to recover its bicharacter.
 For $\GLr$ that's given by the multigrading.
@@
 
-	There are two advantages of doing that. 
+	\begin{example} Compute $\mathcal{E}_{2,1}$ with two rows of variables using the multidegree. 
+		\begin{sagesilent}
+			load("../compute_character.py")
+		\end{sagesilent}
+		First, we compute $\mathcal{E}_{2,1}$ for one row of variables. 
+		\begin{sagecommandline}
+			sage: v = vandermonde(Partition([2,1]))
+			sage: v
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: derivatives
+			sage: E_21 = Subspace({v.multidegree(): [v]}, derivatives)
+			sage: E_21.basis()
+			sage: E_21.dimension()
+		\end{sagecommandline}
+		Then, we use polarization operators to introduce a second set of variables, still with multidegree. 
+		\begin{sagecommandline}
+			sage: polarizators = polarization_operators(2)
+			sage: polarizators
+			sage: E_21 = PolarizedSpace(E_21, polarizators)
+			sage: E_21.basis()
+			sage: E_21.dimension()
+			sage: E_21.dimensions()
+		\end{sagecommandline}	
+	\end{example}
+
+	Note that \texttt{PolarizedSpace} takes in argument a \texttt{Subspace} from which it extracts the basis and returns a \texttt{Subspace} given by this basis and the operators.
+The difference is that this time, the computation is adapted to take care of the change of polynomial ring between one and two (or more) sets of variables.
+\\
+
+	There are two advantages of considering the multidegree. 
 	First, writing $N=:\sum N_D$, the complexity becomes $(\sum N_D^2) M$ instead of $(\sum N_D)^2M_D$ (in fact better).
@@
 	First of all, we need an efficient way to compute the representations of $\Sn$.
-To do that, we will use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ and their multiplicities.
-	The isotypic projector we use is called the Young symmetrizer and is define as follow.
+Computing the traces of the action of permutations of all cycle types would not be an option because of the dimension and the high number of terms of the polynomials.
+	Instead, we use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ and their multiplicities. \\
 
-	We first need to define two elements of the symmetric group algebra $\CC \Sn$.
+	We first need to define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
 	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$.
-Then we have $a_{\mu} = \sum_{\sigma \in P_{\mu}} \sigma$ and  $b_{\mu} = \sum_{\sigma \in P_{\mu}} \sgn(\sigma) \sigma$.
-Finally, the Young symmetrizer is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$
+To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say to tableau filled in by integer from $1$ to $n$ in order, from left to right ans from bottom to top.
+	\begin{example} Consider $\Sym{3}$ and let $\mu = 21$.
+		The canonical tableau associated is \tableau(12,3).\\
+		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$.
+	\end{example}
+
+	With those subgroups, we define $a_{\mu} = \sum_{\sigma \in P_{\mu}} \sigma$ and  $b_{\mu} = \sum_{\sigma \in P_{\mu}} \sgn(\sigma) \sigma$.
+And finally, the Young symmetrizer is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$
+
+	\addtocounter{example}{-1}
+	\begin{example} (suite) 
+		For $\mu=21$, we have
+		$a_{21} = 1 + (12)$ and
+		$b_{21} = 1 - (13)$.
+
+		Therefore, $c_{21} = (1 + (12)) . (1 - (13)) = 1 + (12) - (13) - (132)$.
+
+		For the other partitions of size $3$, one can verify that 
+		$y_{111} = \sum_{\sigma \in \Sym{3}} \sigma$ and 
+		$y_{3} = \sum_{\sigma \in \Sym{3}} \sgn(\sigma)\sigma$
+	\end{example}
 
 	\begin{theorem} \cite{FultonHarris1991}
-		The Young symmetrizer $c_{\lambda}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $V_{\lambda}$ of $\Sn$.
+		The Young symmetrizer $c_{\lambda}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $A_{\lambda}$ of $\Sn$.
 		Thus any irreducible representation can be obtain this way for a unique partition. 
@@
 
-	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ and decompose it into isotypic components using the Young symmetrizer.
-Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ from those of $\harmonics_{n}$.
-\\
+	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ or $\mathcal{E}_\lambda$ for one set of variables and decompose it into isotypic components using the Young symmetrizer.
+Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ (resp.
+$\mathcal{E}_\lambda$ in $r>1$ sets of variables) from those of $\harmonics_{n}$ (resp.
+$\mathcal{E}_\lambda$ in 1 set of variables) .
+
+	\begin{example}
+		Compute $\harmonics_{3,2} = \mathcal{E}_3$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
+		\begin{sagecommandline}
+			sage: v = vandermonde(Partition([3]))
+			sage: v
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+		\end{sagecommandline}
+		At this stage, we project onto the isotypic components of $\Sym{3}$.
+		\begin{sagecommandline}
+			sage: E_3 = IsotypicComponent(E_3, 3)
+			sage: E_3
+		\end{sagecommandline}
+		The result is now a dictionnary of subspaces.
+		\begin{sagecommandline}
+			sage: E_3[Partition([3])].basis()
+			sage: E_3[Partition([2,1])].basis()
+			sage: E_3[Partition([1,1,1])].basis()
+		\end{sagecommandline}
+		Now we polarize each isotypic component. Note that, \texttt{PolarizedSpace} can receive a dictionary of subspaces, it then consider each subspace separately. 
+		\begin{sagecommandline}
+			sage: polarizators = polarization_operators(2)
+			sage: E_3 = PolarizedSpace(E_3, polarizators)
+			sage: E_3[Partition([2,1])].basis()
+		\end{sagecommandline}
+	We chose to print only the polarized isotypic component of type $21$ to avoid unreadable outputs in the example. 	
+	\end{example}
 

### 2019-06-11 article/article.tex
Complete section row symmetries

@@
 	This package was developed at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
-The main achievement is a calculation of this character for $n=6$ \pauline{+ some cases for $n=7$ ?} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+The main achievement is a calculation of this character for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
@@
 
-	Consider the polynomial ring $R=\QQ[X]$ with $k$ sets of $n$ variables.
-To fix conventions, we think of $X$ as a matrix of variables: \pauline{small $x$ for variables, capital $X$ for sets of variables?
-}
+	Consider the polynomial ring $R=\QQ[X]$ with $k$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
 	$$(x_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
@@
 	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
-We denote this space by $\mathcal{E}_{\lambda}$.
-The diagonal harmonics $\harmonics_{n,r}$ are thus a special case of $\mathcal{E}_{\lambda}$ for $\lambda = n$.
+We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
+The diagonal harmonics $\harmonics_{n,r}$ are thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
+\\
+
+	The character of $\mathcal{E}_{\lambda}^{(r)}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
+Therefore, when the precision is not necessary, we will drop the $(r)$ and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
 \\
@@
 
-	\begin{example} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$.
+	\begin{example} \label{H_3} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$. \pauline{Je n'ai trouvé comment avoir les output en latex avec sauts de ligne automatiques.}
 		\begin{sagesilent}
@@
 
-	Once a basis of $\harmonics_{n,r}$ or $\mathcal{E}_\lambda$ is constructed, there still remains to recover its bicharacter.
+	Once a basis of $\harmonics_{n,r}$ or $\mathcal{E}_\lambda^{(r)}$ is constructed, there still remains to recover its bicharacter.
 For $\GLr$ that's given by the multigrading.
@@
 
-	\begin{example} Compute $\mathcal{E}_{2,1}$ with two rows of variables using the multidegree. 
+	\begin{example} Compute $\mathcal{E}_{2,1}^{(2)}$ using the multidegree. 
 		\begin{sagesilent}
@@
 		\end{sagesilent}
-		First, we compute $\mathcal{E}_{2,1}$ for one row of variables. 
+		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		Then, we use polarization operators to introduce a second set of variables, still with multidegree. 
+		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
+		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the key corresponding.
+Moreover, we have access to dimension by multidegree.
 	\end{example}
@@
 Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n,r}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
-	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics^\lambda\,.$$
+	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics_n^\lambda\,.$$
 
-	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ or $\mathcal{E}_\lambda$ for one set of variables and decompose it into isotypic components using the Young symmetrizer.
+	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ or $\mathcal{E}_\lambda^{(1)}$ and decompose it into isotypic components using the Young symmetrizer.
 Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ (resp.
-$\mathcal{E}_\lambda$ in $r>1$ sets of variables) from those of $\harmonics_{n}$ (resp.
-$\mathcal{E}_\lambda$ in 1 set of variables) .
+$\mathcal{E}_\lambda^{(r)}$, $r>1$) from those of $\harmonics_{n}$ (resp.
+$\mathcal{E}_\lambda^{(1)}$) .
 
-	\begin{example}
-		Compute $\harmonics_{3,2} = \mathcal{E}_3$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
+	\begin{example} \label{multigrading}
+		Compute $\harmonics_{3,2} = \mathcal{E}_3^{(2)}$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
 		\begin{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: polarizators = polarization_operators(2)
-			sage: E_3 = PolarizedSpace(E_3, polarizators)
+			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2))
 			sage: E_3[Partition([2,1])].basis()
@@
 	One thing that can slow down the computation is that the polynomials we are working with tend to be big.
-For example, in $6$ variables, the Vandermonde determinant has $6!=720$ monomials.
+For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, has $6!=720$ monomials.
 This means that we need a lot of space to store them and it takes time when we want to apply operators on them.
@@
 Indeed, when projecting $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes $p$ symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes $p.a_\mu$ anti-symmetric with respect to the column preserving permutations of $\mu$.
-	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{how do we guarantee one monomial is enough?} (and do some appropriate straightening whenever a new monomial is created).
+	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
 We chose to keep the smallest representative monomial in lexicographic order.
@@
 
+	\begin{example} ~
+
+		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $111$.
+		Reduced form : $x_1\theta_2$.
+
+		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $21$. 
+		Reduced form : $-\theta_1$ 
+	\end{example}
+
+	In practice, the antisymmetries are exploited first when projecting $\mathcal{E}_\lambda^{(1)}$ onto isotypic components.
+When applying the Young idempotent, the reduced form of each element is computed.
+From this step, the polynomials lie in a diagonal polynomial ring with antisymmetries, thus each polynomial carries the information of its antisymmetries.
+	Then, we maintain the elements of the bases in their reduced form during the polarization.
+
 	\begin{example}
-		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $111$.
-		Reduce form : $x_1\theta_2$. \\
-		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $21$. 
-		Reduce form : $-\theta_1$ 
+			Compute $\harmonics_{3,2} = \mathcal{E}_3^{(2)}$ but this time exploiting antisymmetries. 
+		\begin{sagecommandline}
+			sage: v = vandermonde(Partition([3]))
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+		\end{sagecommandline}
+		At this stage, we project onto the isotypic components of $\Sym{3}$ exploiting antisymmetries. One can check the difference between this computation and the one in example \ref{multigrading}. 
+		\begin{sagecommandline}
+			sage: E_3 = IsotypicComponent(E_3, 3, use_antisymmetry=True)
+			%sage: E_3[Partition([3])].basis()
+			sage: E_3[Partition([2,1])].basis()
+			sage: E_3[Partition([1,1,1])].basis()
+		\end{sagecommandline}
+		We can check that the parent of the polynomials carries the information about the antisymmetries. 
+		\begin{sagecommandline}
+			sage: p = E_3[Partition([2,1])].basis().values()[0][0]
+			sage: p
+			sage: p.parent()
+		\end{sagecommandline}
+		Now we polarize each isotypic component still exploiting antisymmetries.  
+		\begin{sagecommandline}
+			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2))
+			sage: E_3[Partition([2,1])].basis()
+		\end{sagecommandline}
 	\end{example}
@@
 
-	$H_k^P$ is symmetric w.r.t. permutation of rows, and such permutations
-	exchange multigraded components. For example, for $r=3$, the homogeneous components of respective multidegree $4,2,1$ and $2,1,4$ coincide
-	up to cycling of the rows. It is therefore sufficient, in principle, to compute homogeneous components with decreasing multidegree.
+	The space $\mathcal{E}_\lambda$ is symmetric with respect to permutation of rows of $X$, and such permutations exchange multigraded components.
+For example, for $r=3$, the homogeneous components of respective multidegree $(4,2,1)$ and $(2,1,4)$ coincide up to cycling of the rows.
+This means that there are polynomials that are the same up to a permutation of the sets of variables and that we have redundant information.
+
+	It is therefore sufficient, in principle, to compute homogeneous components with decreasing multidegree.
+Thus, we reduce memory complexity since not every homogeneous components are kept and time complexity by decreasing the number of polynomials on which apply operators.
+
 	To achieve this, polarization operators can be tweaked: whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows.
-It can then easily be shown that those tweaked polarization operator properly generate the whole $\harmonics_k^P$ space from $\harmonics^P$.
+It can then easily be shown that those tweaked polarization operator properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$.
 
-	\begin{example}
-		$x_1^2 - 2x_1x_2 + 2x_2x_3 - x_3^2 \in \mathcal{H}_{3}$ so $y_1^2 - 2y_1y_2 + 2y_2y_3 - y_3^2 \in \mathcal{H}_{3}$
+	\begin{example} ~
 
-		$-2x_{1} y_{1} y_{2} + x_{1} y_{2}^{2} \in \mathcal{H}_{3}$ so $-2y_{1} x_{1} x_{2} + y_{1} x_{2}^{2} \in \mathcal{H}_{3}$
+		The polynomial $x_1^2 - 2x_1x_2 + 2x_2x_3 - x_3^2 \in \mathcal{H}_{3}$ has multidegree $(1,0)$ so the same polynomial with multidegree $(0,1)$ that is $y_1^2 - 2y_1y_2 + 2y_2y_3 - y_3^2$ also appears in $\mathcal{H}_{3}$ but it is not necessary to compute it explicitly.
+		%$-2x_{1} y_{1} y_{2} + x_{1} y_{2}^{2} \in \mathcal{H}_{3}$ so $-2y_{1} x_{1} x_{2} + y_{1} x_{2}^{2} \in \mathcal{H}_{3}$
 	\end{example}
 
-	\textbf{Gain:} an order of magnitude; below are the total dimension of each $\harmonics_5^\lambda$ and its restriction to homogeneous components of decreasing multidegree.
+	In practice, we exploit the row symmetries when we set up the polarization operators.
+As said above, when specifying the row symmetries, only components of decreasing multidegree appear in the final result.
+
+	\begin{example} Exploiting both antisymmetries of columns and row symmetries, the homogeneous components for $\mathcal{E}_3^{(2)}$ become the following.
+		\begin{sagesilent}
+			v = vandermonde(Partition([3]))
+			derivatives = partial_derivatives(v.parent())
+			E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+		\end{sagesilent}
+		\begin{sagecommandline}
+			sage: E_3 = IsotypicComponent(E_3, 3, use_antisymmetry=True)
+			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2, row_symmetry="permutation"))
+			sage: E_3[Partition([1,1,1])].basis()
+			sage: E_3[Partition([2,1])].basis()
+			sage: E_3[Partition([3])].basis()
+		\end{sagecommandline}	
+	We observe that only decreasing multidegree components still appears, we don't have components of multidegree $(1,2)$, $(0,3)$, $(0,2)$ and $(0,1)$.
+	\end{example}
+
+	By exploiting this symmetries, we gain an order of magnitude.\\
+
+	As said before, the character of $\GLr$ is given by the multidegree of the homogeneous components.
+In other words, for a given isotypic component of type $\mu$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}} q^{d(\mathcal{E})}$ where the sum is over all homogeneous $\mathcal{E}$ component of type $\mu$, $d(\mathcal{E})$ is the multidegree of the component $\mathcal{E}$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
+
+	When exploiting the row symmetries, since we don't compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation.
+However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions instead of summations to recover the character of $\GLr$ in each isotypic component.
+	\pauline{Add time computation comparison (with and without optimisations) ?} \\
+
+	For now we don't avoid to compute unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree.
+It would be even better if we could avoid computing those polynomials.
+It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.
 
@@
 	\section{Applications}
-	Ask Francois ...
+	Ask Francois.\\
+	Talk about non partition diagram, with or without hole (compositions).
 
-	\begin{definition} \pauline{find the right place for Steenrod op}
+	\begin{definition} \pauline{Steenrod operators? }
 		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by

### 2019-06-12 article/article.tex
Some corrections

@@
 	\section{Introduction}
-	This package was developed at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_{k,n}$ of diagonal harmonic polynomials on $k$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
-The main achievement is a calculation of this character for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
+It was then extended to compute other character on polynomials spaces.
+The main achievement is a calculation of this character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
-	This is a potentially huge calculation ($\harmonics_{5,6}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
-So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
+	This is a potentially huge calculation ($\harmonics_6^{(5)}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
+So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude\pauline{orders of magnitude?}.
 As much as possible, the code was written to be modular and reusable.
@@
 
-	Consider the polynomial ring $R=\QQ[X]$ with $k$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
-	$$(x_{i,j})_{0\leq i<k \atop 0\leq j<n}$$
+	Consider the polynomial ring $R=\QQ[X]$ with $r$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
+	$$(x_{i,j})_{0\leq i<r \atop 0\leq j<n}$$
 	and we denote by $\bm{x}_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
@@
 
-	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of $\GLr$ by diagonal action on the rows.
+	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of the general linear group $\GLr$ by diagonal action on the rows.
 The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$.
@@
 
-	We denote the partial derivative the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for any variable $x \in X$.
-	When $X$ contains only on set of variable ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
+	We denote the partial derivatives the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
+	When $X$ contains only one set of variables ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
 
 	\begin{definition}
-		Let $f \in R$, $f$ is \emph{harmonic} if and only if
-		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0 $$
-		for all $k \geq 0$, $k \in \NN$.
+		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$, $k \in \NN$,
+		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0.$$
 	\end{definition}
 
-	For example the Vandermonde determinant $V_n:=$ $\prod_{i<j}(x_i-x_j)$ is harmonic.
+	For example the Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.
 
@@
 
-	The space of \emph{diagonal harmonic polynomials} $\harmonics_{n,r}$ is the joint kernel of the differential operators $(D_\alpha)_\alpha$.
-Note that $\harmonics_{n,r}$ contains $\harmonics_{n,1} = \harmonics_{n}$.\\
+	The space of \emph{diagonal harmonic polynomials} $\harmonics_n^{(r)}$ is the joint kernel of the differential operators $(D_\alpha)_\alpha$.
+Note that $\harmonics_n^{(r)}$ contains $\harmonics_{n}^{(1)} = \harmonics_{n}$.\\
 
-	As for the harmonics, we have an alternative way to obtain $\harmonics_{n,r}$ directly using operators.
+	As for the harmonics, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.
 
@@
 
-	\begin{theorem}
+	\begin{theorem} \pauline{Ref for this theorem.}
 		Multisymmetric polynomials are obtained by polarization of symmetric polynomials in the first set of variables.
@@
 	\begin{theorem} \label{DiagHarm}
-		Diagonal harmonic polynomials $\harmonics_{n,r}$ are obtained by polarization of harmonic polynomials $\harmonics_{n,1}$ in the first set of variables.
+		Diagonal harmonic polynomials $\harmonics_n^{(r)}$ are obtained by polarization of harmonic polynomials $\harmonics_n^{(1)}$ in the first set of variables.
 	\end{theorem}
 
-	Therorem \ref{DiagHarm} has been proven for two sets of variables.
+	Therorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
 It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
@@
 
-	The diagonal harmonics $\harmonics_{n,r}$ have been studied a lot until now.
+	The diagonal harmonics $\harmonics_n^{(r)}$ have been studied a lot until now.
 The character in the case $r=2$ is due to Garsia and Haiman (see \cite{GarsiaHaiman1993}) and some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
@@
 Then, let define
-	$$V_{\mu} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \mu}$$
-	and the Gasia-Haiman module associated to $\mu$ is the smallest subspace containing $V_{\mu}$ and closed under differentiation for both sets of variables. \\
+	$$M_{\mu} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \mu}$$
+	and the Gasia-Haiman module associated to $\mu$ is the smallest subspace containing $M_{\mu}$ and closed under differentiation for both sets of variables. \\
 
-	F.
-Bergeron recently introduced another generalization of the diagonal harmonics, with inert variables.
-We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$.
+	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}.
+We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
 The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
 
-	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates its cells.
+	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
 Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
-	For example, the partition $21$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{21} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
 
-	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in the operators.
+	\begin{example}
+		The partition $2,1$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+	\end{example}
+
+	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in these operators.
 We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
-The diagonal harmonics $\harmonics_{n,r}$ are thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
+The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
 \\
@@
 	The character of $\mathcal{E}_{\lambda}^{(r)}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
-Therefore, when the precision is not necessary, we will drop the $(r)$ and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
+Therefore, when the precision is not necessary, we will drop the exponent and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
 \\
 
-	Since those subspaces are completely new, computing some characters on Sage helps understanding them better and allows to find some properties of thoses spaces. 
-	Plus, experimentation helped finding the right definition we needed for this generalization.
+	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute.
+In the next section, we expose strategies used to go further in the computation of those characters.
+
+	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{E}_\lambda^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{E}_\lambda^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.
 
@@
 	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables.
+\pauline{$\langle Sym(X)^+ \rangle$ ?}
 	A standard approach would be to compute a Gröbner basis of this ideal.
@@
 
-	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_{n,r}$ of diagonal harmonic polynomials.
+	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials.
 	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
@@
 
-	\begin{example} \label{H_3} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$. \pauline{Je n'ai trouvé comment avoir les output en latex avec sauts de ligne automatiques.}
+	\begin{example} \label{H_3} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$. \pauline{I haven't find yet a way to have latex output with automatic breaklines.}
 		\begin{sagesilent}
@@
 
-	No rocket science here: maintain a matrix in row echelon form representing a basis of the space computed so far, and a ToDo list of $op(v)$, that remain to be computed and inserted in the matrix, where $op$ is an operator and $v$ an element of the subspace in construction.
+	We simply do linear algebra here.
+We maintain a matrix in row echelon form representing a basis of the space computed so far, and a ToDo list of $op(v)$, that remain to be computed and inserted in the matrix, where $op$ is an operator and $v$ an element of the subspace in construction.
 
@@
 
-	Once a basis of $\harmonics_{n,r}$ or $\mathcal{E}_\lambda^{(r)}$ is constructed, there still remains to recover its bicharacter.
+	Once a basis of $\harmonics_n^{(r)}$ or $\mathcal{E}_\lambda^{(r)}$ is constructed, there still remains to recover its bicharacter.
 For $\GLr$ that's given by the multigrading.
@@
 
-	The above utility can be adapted to exploit the multigrading.
+	The \texttt{Subspace} utility can be adapted to exploit the multigrading.
 The input is now a collection of homogeneous vectors and operators together with their multidegrees, and a separate row echelon matrix is maintained for each multidegree.
@@
 		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the key corresponding.
+Operators are also separated by multidegree.
 Moreover, we have access to dimension by multidegree.
@@
 
-	Note that \texttt{PolarizedSpace} takes in argument a \texttt{Subspace} from which it extracts the basis and returns a \texttt{Subspace} given by this basis and the operators.
-The difference is that this time, the computation is adapted to take care of the change of polynomial ring between one and two (or more) sets of variables.
+	Note that \texttt{PolarizedSpace} takes in argument a \texttt{Subspace} from which it extracts the basis and returns a \texttt{Subspace} build from this basis and the given operators.
+The difference is that, this time, the computation is adapted to take care of the change of polynomial ring between one and two (or more) sets of variables.
 \\
@@
 
-	First of all, we need an efficient way to compute the representations of $\Sn$.
+	The $\GLr$ character can easily be recover from the multigrading, but it remains to find an efficient way to compute the representations of $\Sn$.
 Computing the traces of the action of permutations of all cycle types would not be an option because of the dimension and the high number of terms of the polynomials.
@@
 
-	We first need to define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
+	We first define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
 	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$.
-To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say to tableau filled in by integer from $1$ to $n$ in order, from left to right ans from bottom to top.
-	\begin{example} Consider $\Sym{3}$ and let $\mu = 21$.
+To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say to tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top.
+	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
 		The canonical tableau associated is \tableau(12,3).\\
-		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$.
+		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$. \\
 	\end{example}
@@
 	With those subgroups, we define $a_{\mu} = \sum_{\sigma \in P_{\mu}} \sigma$ and  $b_{\mu} = \sum_{\sigma \in P_{\mu}} \sgn(\sigma) \sigma$.
-And finally, the Young symmetrizer is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$
+And finally, the \emph{Young symmetrizer} is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$
+
+	The Young symmetrizer is also called \emph{Young idempotent}. See \cite{FultonHarris1991} for more on this.
 
 	\addtocounter{example}{-1}
-	\begin{example} (suite) 
-		For $\mu=21$, we have
-		$a_{21} = 1 + (12)$ and
-		$b_{21} = 1 - (13)$.
+	\begin{example} (end) 
+		For $\mu=2,1$, we have
+		$a_{2,1} = 1 + (12)$ and
+		$b_{2,1} = 1 - (13)$.
 
-		Therefore, $c_{21} = (1 + (12)) . (1 - (13)) = 1 + (12) - (13) - (132)$.
+		Therefore, $c_{2,1} = (1 + (12)) . (1 - (13)) = 1 + (12) - (13) - (132)$.
 
@@
 
-	\begin{theorem} \cite{FultonHarris1991}
+	\begin{theorem}
 		The Young symmetrizer $c_{\lambda}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $A_{\lambda}$ of $\Sn$.
@@
 
-	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\harmonics_{n}$ gives representatives of the isotypic components of $\Sn$.
-\pauline{Do we need to prove explicitly commutation with symmetric operators?}  \\
+	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
+	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$.
+\pauline{Need more details here!}  \\
 
-	The action of $\GLr$ commutes with the action of $\Sn$.
-Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n,r}$ by starting from a basis of harmonic polynomials that itself is adapted to its decomposition into isotypic components:
-	$$\harmonics_{n}=:\bigoplus_\lambda \harmonics_n^\lambda\,.$$
+	The action of $\GLr$ commutes with the action of $\Sn$, then the polarization operators commute with the Young symmetrizer.
+Therefore, we can compute independently each $\Sn$ isotypic component of $\mathcal{E}_\lambda^{(r)}$ by starting from a basis of $\mathcal{E}_\lambda^{(1)}$ that itself is adapted to its decomposition into isotypic components:
+	$$\mathcal{E}_\lambda^{(1)}=:\bigoplus_\mu \mathcal{E}_{\lambda,\mu}^{(1)}.$$
 
-	In practice, since the polarization operators commute with the Young symmetrizer, we first compute $\harmonics_{n}$ or $\mathcal{E}_\lambda^{(1)}$ and decompose it into isotypic components using the Young symmetrizer.
-Then we use the polarization operators to obtain the isotypic components of $\harmonics_{n,r}$ (resp.
-$\mathcal{E}_\lambda^{(r)}$, $r>1$) from those of $\harmonics_{n}$ (resp.
-$\mathcal{E}_\lambda^{(1)}$) .
+	Then we use the polarization operators to obtain all the isotypic components of $\mathcal{E}_\lambda^{(r)}$ ($r>1$) from those of $\mathcal{E}_\lambda^{(1)}$ .
 
 	\begin{example} \label{multigrading}
-		Compute $\harmonics_{3,2} = \mathcal{E}_3^{(2)}$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
+		Compute $\harmonics_3^{(2)} = \mathcal{E}_3^{(2)}$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		The result is now a dictionnary of subspaces.
+		The result is now a dictionnary of subspaces, one for each isotypic component.
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		Now we polarize each isotypic component. Note that, \texttt{PolarizedSpace} can receive a dictionary of subspaces, it then consider each subspace separately. 
+		We polarize each isotypic component. Note that, \texttt{PolarizedSpace} can receive a dictionary of subspaces, each subspace is then considered separately. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-	We chose to print only the polarized isotypic component of type $21$ to avoid unreadable outputs in the example. 	
+	We print only the polarized isotypic component of type $2,1$ to avoid unreadable outputs in this example. 	
 	\end{example}
 
-	In fact we can do better.
+	In fact we can do better. \pauline{Does it work only for $\harmonics_n^{(r)}$ or also for $\mathcal{E}_\lambda$?}
+	Fix a partition $\mu$. Recall that a basis of the Specht module $S_\mu$  is given by the family of Garnir/Specht polynomials $(G_{P})_P$ indexed by standard tableaux $P$ of shape $\mu$.
 
-	Fix a partition $\lambda$. Recall that a basis of the Specht module $V_\lambda$ is given by the family of Garnir/Specht polynomials $(G_{P})_P$ indexed by standard tableaux $P$ of shape $\lambda$.
+	To get a basis of the full isotypic component $\harmonics_{\mu}$ of $\harmonics_n$, we can, for example, use a generalization of this construction (see \cite{Ariki1997}): a family of polynomials $(G_{P,Q})_{P,Q}$ indexed by a pairs $(P,Q)$ of standard tableaux of shape $\mu$ where $Q$ specifies the copy of $S_\mu$ and $P$ specifies the location within that copy of $S_\mu$.
 
-	To get a basis of the full isotypic component $\harmonics^\lambda$, we can, for example, use a generalization of this construction (see \cite{Ariki1997}): a family of polynomials $(G_{P,Q})_{P,Q}$ indexed by a pairs $(P,Q)$ of standard tableaux of shape $\lambda$ where $Q$ specifies the copy of $V_\lambda$ and $P$ specifies the location within that copy of $V_\lambda$.
+	Remark: For a fixed tableau $P$, denote by $\harmonics_P^{(r)}$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
+It's exactly the image of $\harmonics_n$ under the Young idempotent associated to $P$.
+For a given shape $\mu$, the $\harmonics_P^{(r)}$ are all conjugate under $\Sn$, and their direct sum is the isotypic component $\harmonics_{\mu}^{(r)}$.
 
-	Remark: For a fixed tableau $P$, denote by $\harmonics_k^P$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
-It's exactly the image of $\harmonics_n$ under the Young idempotent associated to $P$.
-For a given shape $\lambda$, the $\harmonics_k^P$ are all conjugate under $\Sn$, and their direct sum is the isotypic component $\harmonics_k^\lambda$.
-
-	To conclude, it is sufficient to compute $\harmonics_k^P$ for one tableau of each shape $\lambda$. This reduces the complexity by the square of the number of standard tableaux of shape $\lambda$.
+	To conclude, it is sufficient to compute $\harmonics_P^{(r)}$ for one tableau of each shape $\mu$. This reduces the complexity by the square of the number of standard tableaux of shape $\mu$.
 
@@
 For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, has $6!=720$ monomials.
-This means that we need a lot of space to store them and it takes time when we want to apply operators on them.
+This means that we need a lot of space to store them and it takes time when we want to apply operators.
 
-	However, for all $p \in \mathcal{E}_\lambda$, p is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $p$.
-Indeed, when projecting $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes $p$ symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes $p.a_\mu$ anti-symmetric with respect to the column preserving permutations of $\mu$.
+	However, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
+Indeed, when projecting $v$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes any element symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes the result anti-symmetric with respect to the column preserving permutations of $\mu$.
 	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
-We chose to keep the smallest representative monomial in lexicographic order.
+We chose to keep the smallest representative monomial in lexicographic order and call the result the normal reduced form of $v$.
 \\
 
-	Thus keeping reduced form of the polynomials reduce space complexity and time complexity when applying operators.
-Note that each time an operator is applied to an element, the reduced form of this element is computed again.
+	Thus keeping reduced form of the polynomials decreases space complexity, and also time complexity when applying operators.
+Note that each time a polarization operator is applied to an element, the normal reduced form of the new element obtained is computed again.
 
@@
 
-		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $111$.
+		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$.
 		Reduced form : $x_1\theta_2$.
 
-		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $21$. 
+		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$. 
 		Reduced form : $-\theta_1$ 
@@
 From this step, the polynomials lie in a diagonal polynomial ring with antisymmetries, thus each polynomial carries the information of its antisymmetries.
-	Then, we maintain the elements of the bases in their reduced form during the polarization.
+	Then, we maintain the elements of the bases of the isotypic components in their reduced form during polarization.
 
 	\begin{example}
-			Compute $\harmonics_{3,2} = \mathcal{E}_3^{(2)}$ but this time exploiting antisymmetries. 
+			Compute $\harmonics_3^{(2)} = \mathcal{E}_3^{(2)}$ exploiting antisymmetries. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		We can check that the parent of the polynomials carries the information about the antisymmetries. 
+		We see that the parent of the polynomials carries the information about the antisymmetries to keep polynomials in normal reduced form.
 		\begin{sagecommandline}
@@
 
-	This trick was already used by François for the polarizations of the Vandermonde (the diagram space). Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
+	This trick was already used by François Bergeron for the polarizations of the Vandermonde (the diagram space).
+Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
 
-	\textbf{Gain:} in theory up to $n!$. In practice between one and two orders of magnitude due to the overhead of straightening monomials.
+	We gain in theory up to $n!$. In practice, between one and two orders of magnitude due to the overhead of straightening monomials.
 
@@
 For example, for $r=3$, the homogeneous components of respective multidegree $(4,2,1)$ and $(2,1,4)$ coincide up to cycling of the rows.
-This means that there are polynomials that are the same up to a permutation of the sets of variables and that we have redundant information.
+This means that there are polynomials in different homogeneous component that are the same up to a permutation of the sets of variables and that we have redundant information.
 
 	It is therefore sufficient, in principle, to compute homogeneous components with decreasing multidegree.
-Thus, we reduce memory complexity since not every homogeneous components are kept and time complexity by decreasing the number of polynomials on which apply operators.
+Thus, we reduce memory complexity since not every homogeneous components are kept in memory and time complexity by decreasing the number of polynomials on which apply operators.
 
@@
 		\end{sagecommandline}	
-	We observe that only decreasing multidegree components still appears, we don't have components of multidegree $(1,2)$, $(0,3)$, $(0,2)$ and $(0,1)$.
+	We observe that only decreasing multidegree components still appear, we don't have components of multidegree $(1,2)$, $(0,3)$, $(0,2)$ and $(0,1)$.
 	\end{example}
@@
 In other words, for a given isotypic component of type $\mu$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}} q^{d(\mathcal{E})}$ where the sum is over all homogeneous $\mathcal{E}$ component of type $\mu$, $d(\mathcal{E})$ is the multidegree of the component $\mathcal{E}$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
+\pauline{Find better notation.}
 
@@
 	For now we don't avoid to compute unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree.
-It would be even better if we could avoid computing those polynomials.
+It would be even better if we could avoid completely computation of those polynomials.
 It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.
@@
 
-	\textbf{Current gain:} another order of magnitude; down from 3 days to 45 minutes for $\harmonics_5^{1^6}$
+	\textbf{Current gain:} another order of magnitude; down from 3 days to 45 minutes for $\harmonics_{6;1^6}^{(5)}$
 

### 2019-06-21 article/article.tex
Rereading

@@
 	\section{Introduction}
+	In this article, we present a new SageMath package to compute bicharacter of some multivariate polynomials spaces. 
 	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
-It was then extended to compute other character on polynomials spaces.
-The main achievement is a calculation of this character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+It was then extended to compute other characters of polynomial spaces.
+
+	The main achievement is a calculation of the character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
@@
 	$$(x_{i,j})_{0\leq i<r \atop 0\leq j<n}$$
-	and we denote by $\bm{x}_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
+	and we denote by $\bm{x}_i = (x_{i,1}, x_{i,2}, \dots, x_{i,n})$ the i-th set of variables.
 We use the convention that bold letters stand for sets of variables and light letters stand for the variables themselves.
 
-	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of the general linear group $\GLr$ by diagonal action on the rows.
+	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns of $X$ and of the general linear group $\GLr$ by diagonal action on the rows of $X$.
 The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$.
@@
 The multigrading is preserved by the action of $\Sn$.
-The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$ character.
-It's thus equivalent to consider the $\GLr \times \Sn$ bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
+The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$-character.
+It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
 
@@
 
-	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur symmetric functions. \\
+	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur functions. \\
 
-	We denote the partial derivatives the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
+	We denote the partial derivatives by $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
 	When $X$ contains only one set of variables ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
@@
 	\begin{definition}
-		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$, $k \in \NN$,
+		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$,
 		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0.$$
@@
 
-	For example the Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.
-
-	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$ is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
+	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$, is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
 It is also a realization of the coinvariants of the symmetric group: $R\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.
 
-	For example, $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$.
+	\begin{example}
+		The Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.
+
+		The space of harmonic polynomials in two variables is $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$. 
+	\end{example}
 
@@
 	Going back to an arbitrary number $r$ of sets of variables, we define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
-	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{11}}^{\alpha_1}\dots\partial_{x_{r1}}^{\alpha_r} + \dots + \partial_{x_{1n}}^{\alpha_1}\dots\partial_{x_{rn}}^{\alpha_r} = \sum_{j=1}^{n} \prod_{i=1}^{r} \partial_{x_{ij}}^{\alpha_i}$$
+	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{1,1}}^{\alpha_1}\dots\partial_{x_{r,1}}^{\alpha_r} + \dots + \partial_{x_{1,n}}^{\alpha_1}\dots\partial_{x_{r,n}}^{\alpha_r}$$
 
-	For example, take $r=3$ and denote $\bm{x}, \bm{y}$ and $\bm{z}$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.
+	\begin{example}
+		Take $r=3$ and denote $\bm{x}, \bm{y}$ and $\bm{z}$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$. 
+	\end{example}
 
@@
 
-	As for the harmonics, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.
+	As for harmonic polynomials, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.
 
@@
 
-	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\mu$ be a partition of $n$.
-We also denote $\mu$ the Ferrer's diagram (in French notation) associated to the partition $\mu$ and each cell of $\mu$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
+	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$.
+We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
 Then, let define
-	$$M_{\mu} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \mu}$$
-	and the Gasia-Haiman module associated to $\mu$ is the smallest subspace containing $M_{\mu}$ and closed under differentiation for both sets of variables. \\
+	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
+	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\
 
@@
 We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
-The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.
+The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
 
@@
 
-	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables.
-\pauline{$\langle Sym(X)^+ \rangle$ ?}
+	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n = \langle Sym(X)^+ \rangle$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables.
 	A standard approach would be to compute a Gröbner basis of this ideal.
@@
 
-	At this stage, we have an algorithm, but are still doing linear algebra in a huge space (cost $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space).
+	At this stage, we have an algorithm, but are still doing linear algebra in a huge space. The cost is $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space.
 
@@
 		\end{sagecommandline}
-		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the key corresponding.
+		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the corresponding key.
 Operators are also separated by multidegree.
@@
 
-	The $\GLr$ character can easily be recover from the multigrading, but it remains to find an efficient way to compute the representations of $\Sn$.
+	The $\GLr$-character can easily be recover from the multigrading, but it remains to find an efficient way to compute the representations of $\Sn$.
 Computing the traces of the action of permutations of all cycle types would not be an option because of the dimension and the high number of terms of the polynomials.
-	Instead, we use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ and their multiplicities. \\
+	Instead, we use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ with their multiplicities. \\
 
 	We first define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
-	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$.
-To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say to tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top.
-	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
-		The canonical tableau associated is \tableau(12,3).\\
-		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$. \\
-	\end{example}
+	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the column preserving permutations of $\mu$.
+To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say the tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top.
 
@@
 
-	\addtocounter{example}{-1}
-	\begin{example} (end) 
+	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
+		The canonical tableau associated is \tableau(12,3).\\
+		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$.
+
 		For $\mu=2,1$, we have
@@
 		For the other partitions of size $3$, one can verify that 
-		$y_{111} = \sum_{\sigma \in \Sym{3}} \sigma$ and 
-		$y_{3} = \sum_{\sigma \in \Sym{3}} \sgn(\sigma)\sigma$
+		$c_{1,1,1} = \sum_{\sigma \in \Sym{3}} \sigma$ and 
+		$c_{3} = \sum_{\sigma \in \Sym{3}} \sgn(\sigma)\sigma$.
 	\end{example}
@@
 	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
-	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$.
-\pauline{Need more details here!}  \\
+	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on an adapted basis of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$.
+\pauline{Need more details here.}  \\
 
@@
 
-	However, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
-Indeed, when projecting $v$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes any element symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes the result anti-symmetric with respect to the column preserving permutations of $\mu$.
+	However, since we use the Young symmetrizer to construct $\mathcal{E}_\lambda$, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
+Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$.
 	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
-We chose to keep the smallest representative monomial in lexicographic order and call the result the normal reduced form of $v$.
+We chose to keep the smallest representative monomial in lexicographic order and call the result the \emph{normal reduced form} of $v$.
 \\
@@
 
-		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$.
-		Reduced form : $x_1\theta_2$.
+		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$ and has reduced form $x_1\theta_2$.
 
-		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$. 
-		Reduced form : $-\theta_1$ 
+		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$ and has reduced form $-\theta_1$.
 	\end{example}
@@
 
-	To achieve this, polarization operators can be tweaked: whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows.
-It can then easily be shown that those tweaked polarization operator properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$.
+	To achieve this, polarization operators can be tweaked.
+Whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows.
+It can then easily be shown that those tweaked polarization operators properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$.
+\pauline{Tweaked polarizators don't generate the whole space only the decreasing multidegree components.}
 
@@
 
-	In practice, we exploit the row symmetries when we set up the polarization operators.
+	In practice, when we polarize $\mathcal{E}_\lambda^{(1)}$, tweaked polarization operators are given in argument to \texttt{PolarizedSpace} instead of the classical ones.
 As said above, when specifying the row symmetries, only components of decreasing multidegree appear in the final result.
@@
 
-	As said before, the character of $\GLr$ is given by the multidegree of the homogeneous components.
-In other words, for a given isotypic component of type $\mu$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}} q^{d(\mathcal{E})}$ where the sum is over all homogeneous $\mathcal{E}$ component of type $\mu$, $d(\mathcal{E})$ is the multidegree of the component $\mathcal{E}$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
-\pauline{Find better notation.}
+	As said before, the $\GLr$-character of $\mathcal{E}_\lambda$ is given by the multidegree of the homogeneous components.
+In other words, for a given isotypic component $\mathcal{E}_{\lambda,\mu}$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}} q^{d}$ where the sum is over all homogeneous component $\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}$ of type $\mu$ and multidegree $d$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
 
 	When exploiting the row symmetries, since we don't compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation.
-However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions instead of summations to recover the character of $\GLr$ in each isotypic component.
+However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions $m_d$ instead of summations to recover the character of $\GLr$ in each isotypic component.
 	\pauline{Add time computation comparison (with and without optimisations) ?} \\
 
-	For now we don't avoid to compute unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree.
-It would be even better if we could avoid completely computation of those polynomials.
+	For now we don't avoid compute some unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree.
+It would be even better if we could avoid completely the computation of those polynomials.
 It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.
@@
 
+	\pauline{I changed nothing in the two following subsections.}
 	Building on the previous strategy, it would be tempting to only compute the subspace of $sl_r$ highest weight vectors within each $\harmonics_k^P$.

### 2019-07-05 article/article.tex
TODO notes

@@
 
+\nicolas{Ajouter des exemples au fur et à mesure}
+\nicolas{figure de la matrice avec les actions de $\Sn$ et $\GLr$}
+
 	Consider the polynomial ring $R=\QQ[X]$ with $r$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
@@
 
-	The grading can be refined into a multigrading by rows.
+	The natural grading of $R$ can be refined into a multigrading by rows.
 The multigrading is preserved by the action of $\Sn$.
@@
 
-	Therorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
+	Theorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
 It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
 \\
+        \nicolas{state conjecture explicitly + comment that we assume
+          that it holds}
 
+	\nicolas{fuse this paragraph with the earlier context about coinvariants}
 	The diagonal harmonics $\harmonics_n^{(r)}$ have been studied a lot until now.
@@
 	\subsection{Generalizations}
-
+	\nicolas{move to a later section, with 2-3 paragraphs of
+          announcement in the introduction}
 	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.

### 2019-07-05 article/article.tex
Add comments

--- 2019-06-21 article/article.tex
@@
 
-	When $k=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
-	When $k=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
+	When $r=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
+	When $r=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
 

### 2019-07-22 compute_character.py
Complete parallelization. Works fine!

@@ -5,7 +5,6 @@ from pypersist import persist
 from sage.misc.misc import attrcall
 from sage.categories.tensor import tensor
 
-
 from diagonal_polynomial_ring import*
 from subspace import*
 from young_idempotent import*
@@ -757,7 +756,7 @@ def dimension(f, n):
 
 @persist(hash=lambda k: 'character_%s_%s' % (k[0][1].size(),''.join(str(i) for i in k[0][1])),
         funcname='character')
-def compute_character(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
+def E_mu(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
     """
     Given a diagram `mu`, compute the character associated to this diagram.
     Compute the subspace span by the Vandermonde determinant associated to `mu`
@@ -798,12 +797,9 @@ def compute_character(mu, use_antisymmetry=True, row_symmetry="permutation", par
     op_pol = polarization_operators(r, deg, row_symmetry=row_symmetry)
     if parallel:
         charac = 0
-        for (((_,_),_), V_pol) in ParallelCharacter([(subspace, op_pol) for subspace in V_iso.values()]):
-            print "test parall"
-            print V_pol
-            print
-            # character
-            #charac += character(V_pol, row_symmetry=row_symmetry)
+        for (((_,_),_), V_pol) in parallel_character([(subspace, op_pol) for subspace in V_iso.values()]):
+            for key, coeff in V_pol.iteritems():
+                charac += coeff*tensor([s(key[0]), s(key[1])])
         return charac
     else:
         V_pol = PolarizedSpace(V_iso, op_pol)

### 2019-07-22 article/article.tex
Rewrite first section (context).

--- 2019-07-05 article/article.tex
@@
 \usepackage{tikz,graphicx}
-\usepackage{fancyhdr}
+\usepackage{float}
 \usepackage{url}
@@
 \usepackage[colorinlistoftodos,prependcaption,textsize=small,textwidth=2.5cm]{todonotes}
-\newcommand{\pauline}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
+\newcommand{\pauline}[1]{\todo[linecolor=blue,backgroundcolor=cyan!25,bordercolor=blue]{#1}}
 \newcommand{\nicolas}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green]{#1}}
@@
 	This is a potentially huge calculation ($\harmonics_6^{(5)}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
-So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude\pauline{orders of magnitude?}.
+So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
 As much as possible, the code was written to be modular and reusable.
 
-	\section{Context}
+	\section{Context : harmonic and diagonal harmonic polynomials}
 
-	\subsection{Harmonic and diagonal harmonic polynomials}
+\nicolas{Ajouter des exemples au fur et à mesure}
 
 	Consider the polynomial ring $R=\QQ[X]$ with $r$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
-	$$(x_{i,j})_{0\leq i<r \atop 0\leq j<n}$$
+	$$X := \begin{pmatrix}
+	x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
+	x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
+	\vdots & \vdots & \ddots & \vdots \\
+	x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\
+	\end{pmatrix}$$
 	and we denote by $\bm{x}_i = (x_{i,1}, x_{i,2}, \dots, x_{i,n})$ the i-th set of variables.
@@
 	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns of $X$ and of the general linear group $\GLr$ by diagonal action on the rows of $X$.
-The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$.
+	\begin{figure}[H]
+		\centering
+		\begin{tikzpicture}
+		\draw node{$\begin{pmatrix}
+			x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
+			x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
+			\vdots & \vdots & \ddots & \vdots \\
+			x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\
+			\end{pmatrix}$ } (0,0);
+		\draw (-2.4,.2)+(60:.25)
+		[xscale=.5,yscale=3.2,->,rotate=80] arc(-40:290:.25);
+		\node at (-3,0) {{\small$\GLr$}};
+		\draw (-.5,-1.5)+(60:.25)
+		[xscale=5.5,yscale=.6,->,rotate=-210] arc(-40:290:.25);
+		\node at (0,-2) {{\small$\Sn$}};
+		\end{tikzpicture}
+		\caption{Simultaneous actions of $\GLr$ and $\Sn$ on $X$.}
+	\end{figure}
+
+	The invariant ring $R^{\Sn}$ is known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$.
 The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
 It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.
+\pauline{Add details about grading.}
 
-	The grading can be refined into a multigrading by rows.
+	The natural grading of $R$ can be refined into a multigrading by rows.
 The multigrading is preserved by the action of $\Sn$.
@@
 It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
-
-	When $r=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
-	When $r=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
-
-	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur functions. \\
+\\
 
 	We denote the partial derivatives by $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
-	When $X$ contains only one set of variables ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
+	When $X$ contains only one set of variables, $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
 
@@
 
+	\begin{definition}
 		The space of \emph{diagonal harmonic polynomials} $\harmonics_n^{(r)}$ is the joint kernel of the differential operators $(D_\alpha)_\alpha$.
-Note that $\harmonics_n^{(r)}$ contains $\harmonics_{n}^{(1)} = \harmonics_{n}$.\\
+Note that $\harmonics_n^{(r)}$ contains $\harmonics_{n}^{(1)} = \harmonics_{n}$.
+	\end{definition}
 
@@
 		The \emph{polarisation operator} $P_{x,y}^k$ is given by
-		$$P_{x,y}^k = \sum_{i=1}^{n} y \partial_{x}^k$$
+		$$P_{x,y}^k = \sum_{i=1}^{n} y_i \partial_{x_i}^k$$
 		where $\bm{x}$ and $\bm{y}$ are two sets of variables of $X$. 
@@
 
-	\begin{theorem} \pauline{Ref for this theorem.}
+	\begin{theorem} \pauline{Nicolas as-tu la réf pour ce thm?}
 		Multisymmetric polynomials are obtained by polarization of symmetric polynomials in the first set of variables.
@@
 
-	\begin{theorem} \label{DiagHarm}
+	\begin{conjecture} \label{DiagHarm}
 		Diagonal harmonic polynomials $\harmonics_n^{(r)}$ are obtained by polarization of harmonic polynomials $\harmonics_n^{(1)}$ in the first set of variables.
-	\end{theorem}
+	\end{conjecture}
 
-	Therorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
-It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).
+	Conjecture \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
+It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true.
+\pauline{talk to Mike for more informations} \\
+
+    Since diagonal harmonics polynomials spaces are of huge dimension, they are not easy to study.
+Indeed, when $r=1$, $R_{\Sn}$ is of dimension $n!$, and when $r=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$).
+
+    In order to study those spaces, we will use representation theory and characters.
+Intuitively, through representation theory, the purpose is to cut modules into irreducible submodules according to the group action.
+Those submodules are then represented by irreducible characters that encodes the group action on each submodule.
+For $\GLr$ and $\Sn$, irreducible characters can be indexed by partitions and encoded by Schur functions.
+Knowing the irreducible characters gives informations of the studied module such as the dimension.
+
+    We will not enter into details on representation theory here but for more on this topic see \cite{FultonHarris1991}.
+Also, \cite{Sagan} is a classical reference for representation theory of the symmetric group and see \cite{Green2007} for more on the polynomial representations of the general linear group.
 \\
 
-	The diagonal harmonics $\harmonics_n^{(r)}$ have been studied a lot until now.
-The character in the case $r=2$ is due to Garsia and Haiman (see \cite{GarsiaHaiman1993}) and some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
-Therefore, the computation of those characters should lead to a better understanding of those spaces.
+   	The characters of the harmonic and diagonal harmonic polynomials spaces have been studied a lot until now.
+For example, it is known that, when r=1, the action of $GL_1$ is trivial and $R_{\Sn}$ carries the usual graded representation of $\Sn$.
+Its character is given by a Hall-Littlewood polynomial.
 
-	\subsection{Generalizations}
+    The case r=2 has been studied by Garsia and Haiman (see \cite{GarsiaHaiman1993}) and the bigraded character, as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), is a Macdonald polynomial.
 
-	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
-
-	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$.
-We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
-Then, let define
-	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
-	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\
-
-	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}.
-We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
-The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
-
-	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
-Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
-
-	\begin{example}
-		The partition $2,1$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
-	\end{example}
-
-	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in these operators.
-We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
-The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
+	Finally, some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
+Therefore, the computation of the characters of $\harmonics_{n}^{(r)}$ should lead to a better understanding of those spaces.
 \\
 
-	The character of $\mathcal{E}_{\lambda}^{(r)}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
-Therefore, when the precision is not necessary, we will drop the exponent and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
-\\
+	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.
 
-	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute.
 	In the next section, we expose strategies used to go further in the computation of those characters.
-
-	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{E}_\lambda^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{E}_\lambda^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.
+In the last section, we present some applications/generalizations we are able to make using the same computation strategies.
+\pauline{annonce du contenu à réécrire}
 
@@
 	\section{Applications}
+
+	\subsection{Inert variables}
+	\nicolas{2-3 paragraphs of announcement in the introduction}
+	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
+
+	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$.
+We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
+Then, let define
+	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
+	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\
+
+	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}.
+We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
+The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
+
+	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
+Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+
+	\begin{example}
+		The partition $2,1$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+	\end{example}
+
+	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in these operators.
+We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
+The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
+\\
+
+	The character of $\mathcal{E}_{\lambda}^{(r)}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
+Therefore, when the precision is not necessary, we will drop the exponent and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
+\\
+
+	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute. \\
+
+	\subsection{Further work}
+
+	\pauline{Change title}
+
 	Ask Francois.\\

### 2019-07-23 compute_character.py
Change function name compute_character for E_mu. Better name.

@@ -48,6 +48,8 @@ def vandermonde(gamma, r=0):
         Diagonal Polynomial Ring with 2 rows of 3 variables and inert variables over Rational Field
 
     """
+    if isinstance(gamma, Integer):
+        gamma = Partition([gamma])
     n = gamma.size()
     if r == 0:
         r = 1
@@ -661,12 +663,12 @@ def factorize(f, n=0):
     - ``n`` -- an Integer
     
     EXAMPLES::
-    sage: factorize(compute_character(Partition([3,1])), 4)
-    [([3, 1], s[]),
-     ([1, 1, 1, 1], s[1, 1] + s[3]),
-     ([2, 2], s[1]),
-     ([2, 1, 1], s[1] + s[2]),
-     ([4], 0)]
+    sage: factorize(E_mu(Partition([3,1])), 4)
+    [((3, 1), s[]),
+     ((1, 1, 1, 1), s[1, 1] + s[3]),
+     ((2, 2), s[1]),
+     ((2, 1, 1), s[1] + s[2]),
+     ((4,), 0)]
 
     TODO : Delete n and correct code and worksheets 
     """
@@ -696,7 +698,7 @@ def latex_output_character(f):
     
     EXAMPLES:: 
         sage: for mu in Partitions(3):
-        ....:     print(latex_output_character(compute_character(mu)))
+        ....:     print(latex_output_character(E_mu(mu)))
         1 \otimes s_{3} +(s_{1} + s_{2}) \otimes s_{2,1} +(s_{1,1} + s_{3}) \otimes s_{1,1,1} 
         1 \otimes s_{2,1} + s_{1} \otimes s_{1,1,1} 
         1 \otimes s_{1,1,1} 
@@ -730,10 +732,10 @@ def dimension(f, n):
     
     
     EXAMPLES::
-        sage: f = compute_character(Partition([3,1]))
+        sage: f = E_mu(Partition([3,1]))
         sage: dimension(f, 4)
         [((3, 1), 1), ((1, 1, 1, 1), 1), ((2, 2), 1), ((2, 1, 1), 2)]
-        sage: dimension(compute_character(Partition([3])),3)
+        sage: dimension(E_mu(Partition([3])),3)
         [((1, 1, 1), 1), ((3,), 1), ((2, 1), 2)]
 
     """
@@ -770,10 +772,10 @@ def E_mu(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
[…]

### 2019-07-23 article/article.tex
Review section on strategies to fit with context section. Move inert variables computations at the end and complete the subsection.

@@
 			\end{pmatrix}$ } (0,0);
-		\draw (-2.4,.2)+(60:.25)
-		[xscale=.5,yscale=3.2,->,rotate=80] arc(-40:290:.25);
+		\draw (-2.4,.3)+(60:.25)
+		[xscale=.5,yscale=3.4,->,rotate=80] arc(-40:290:.25);
 		\node at (-3,0) {{\small$\GLr$}};
-		\draw (-.5,-1.5)+(60:.25)
-		[xscale=5.5,yscale=.6,->,rotate=-210] arc(-40:290:.25);
+		\draw (-.6,-1.5)+(60:.25)
+		[xscale=5.8,yscale=.6,->,rotate=-210] arc(-40:290:.25);
 		\node at (0,-2) {{\small$\Sn$}};
@@
 
-	Solving those differential equations would not be that tractable either. So instead we used operators, partial derivatives and polarization operators defined in the previous section. \\
+	Solving those differential equations would not be tractable either. So instead we used operators, partial derivatives and polarization operators defined in the previous section. \\
 
@@
 
-	The exact same strategy works to build the subspace generated by the Vandermonde $V_{\lambda}$ and its partial derivatives.
-
-	Once a basis of $\harmonics_n^{(r)}$ or $\mathcal{E}_\lambda^{(r)}$ is constructed, there still remains to recover its bicharacter.
+	Once a basis of $\harmonics_n^{(r)}$ is constructed, there still remains to recover its bicharacter.
 For $\GLr$ that's given by the multigrading.
@@
 
-	\begin{example} Compute $\mathcal{E}_{2,1}^{(2)}$ using the multidegree. 
+	\begin{example} Compute $\harmonics_{3}^{(2)}$ using the multidegree. 
 		\begin{sagesilent}
@@
 		\end{sagesilent}
-		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables. 
+		First, we compute $\harmonics_{3}^{(1)}$, for one row of variables. 
 		\begin{sagecommandline}
-			sage: v = vandermonde(Partition([2,1]))
+			sage: v = vandermonde(3)
 			sage: v
@@
 			sage: derivatives
-			sage: E_21 = Subspace({v.multidegree(): [v]}, derivatives)
-			sage: E_21.basis()
-			sage: E_21.dimension()
+			sage: H_3 = Subspace({v.multidegree(): [v]}, derivatives)
+			sage: H_3.basis()
+			sage: H_3.dimension()
 		\end{sagecommandline}
-		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. 
+		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\harmonics_3^{(2)}$, still with multidegree. 
 		\begin{sagecommandline}
@@
 			sage: polarizators
-			sage: E_21 = PolarizedSpace(E_21, polarizators)
-			sage: E_21.basis()
-			sage: E_21.dimension()
-			sage: E_21.dimensions()
+			sage: H_3 = PolarizedSpace(H_3, polarizators)
+			%sage: H_3.basis()
+			sage: H_3.dimension()
+			sage: H_3.dimensions()
 		\end{sagecommandline}
@@
 	We first define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
-	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the column preserving permutations of $\mu$.
+	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of all column preserving permutations of $\mu$.
+
 	To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say the tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top.
+Then a permutation is said row (resp.
+column) preserving if when applied to the canonical tableau of $\mu$, the entries of each row (resp.
+column) remains in the same row (resp.
+column) maybe in a different order (see example \ref{young_idempotent}).
 
@@
 
-	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
-		The canonical tableau associated is \tableau(12,3).\\
+	\begin{example}\label{young_idempotent} Let $\mu = (2,1)$.
+		The canonical tableau associated is \tableau(12,3).
+
 		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$.
 
-		For $\mu=2,1$, we have
+		For $\mu=(2,1)$, we have
 		$a_{2,1} = 1 + (12)$ and
@@
 	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
-	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on an adapted basis of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$.
+	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on an adapted basis of $\harmonics_{n}^{(r)}$ gives representatives of the isotypic components of $\Sn$.
 \pauline{Need more details here.}  \\
@@
 	The action of $\GLr$ commutes with the action of $\Sn$, then the polarization operators commute with the Young symmetrizer.
-Therefore, we can compute independently each $\Sn$ isotypic component of $\mathcal{E}_\lambda^{(r)}$ by starting from a basis of $\mathcal{E}_\lambda^{(1)}$ that itself is adapted to its decomposition into isotypic components:
-	$$\mathcal{E}_\lambda^{(1)}=:\bigoplus_\mu \mathcal{E}_{\lambda,\mu}^{(1)}.$$
+Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n}^{(r)}$ by starting from a basis of $\harmonics_{n}^{(1)}$ that itself is adapted to its decomposition into isotypic components:
+	$$\harmonics_{n}^{(1)}=:\bigoplus_{\mu \vdash n} \harmonics_{\mu}^{(1)},$$
 
-	Then we use the polarization operators to obtain all the isotypic components of $\mathcal{E}_\lambda^{(r)}$ ($r>1$) from those of $\mathcal{E}_\lambda^{(1)}$ .
+	where $\harmonics_{\mu}^{(1)}$ is the isotypic component of type $\mu$ of $\harmonics_{n}^{(1)}$.
+
+	Then we use the polarization operators to obtain all the isotypic components $\harmonics_{\mu}^{(r)}$ of $\harmonics_n^{(r)}$ ($r>1$) from those of $\harmonics_n^{(1)}$ .
 
 	\begin{example} \label{multigrading}
-		Compute $\harmonics_3^{(2)} = \mathcal{E}_3^{(2)}$ using the Vandermonde determinant associated to $\lambda=3$. We still use the multigrading. 
+		Compute $\harmonics_3^{(2)}$ using the Vandermonde determinant for $n=3$. We still use the multigrading. 
 		\begin{sagecommandline}
-			sage: v = vandermonde(Partition([3]))
-			sage: v
+			sage: v = vandermonde(3)
 			sage: derivatives = partial_derivatives(v.parent())
-			sage: E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+			sage: H_3 = Subspace({v.multidegree(): [v]}, derivatives)
 		\end{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: E_3 = IsotypicComponent(E_3, 3)
-			sage: E_3
+			sage: H_3 = IsotypicComponent(H_3, 3)
+			sage: H_3
 		\end{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: E_3[Partition([3])].basis()
-			sage: E_3[Partition([2,1])].basis()
-			sage: E_3[Partition([1,1,1])].basis()
+			sage: H_3[Partition([3])].basis()
+			sage: H_3[Partition([2,1])].basis()
+			sage: H_3[Partition([1,1,1])].basis()
 		\end{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2))
-			sage: E_3[Partition([2,1])].basis()
+			sage: H_3 = PolarizedSpace(H_3, polarization_operators(2))
+			sage: H_3[Partition([2,1])].basis()
 		\end{sagecommandline}
-	We print only the polarized isotypic component of type $2,1$ to avoid unreadable outputs in this example. 	
+	We print only the polarized isotypic component of type $(2,1)$ to avoid unreadable outputs in this example. 	
 	\end{example}
@@
 
-	Remark: For a fixed tableau $P$, denote by $\harmonics_P^{(r)}$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
+	For a fixed tableau $P$, denote by $\harmonics_P^{(r)}$ the space spanned by the higher Specht polynomials $(G_{P,Q})_Q$ under polarization.
 It's exactly the image of $\harmonics_n$ under the Young idempotent associated to $P$.
@@
 
+	However, for now we have not managed to fully implement this strategy but are still working on it.
+
 	\subsection{Exploiting column antisymmetries}
@@
 	One thing that can slow down the computation is that the polynomials we are working with tend to be big.
-For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, has $6!=720$ monomials.
+For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, is a homogeneous polynomial of degree $\sum_{i=1}^{5}i = 15$ with $6!=720$ monomials .
 This means that we need a lot of space to store them and it takes time when we want to apply operators.
 
-	However, since we use the Young symmetrizer to construct $\mathcal{E}_\lambda$, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
+	However, since we use the Young symmetrizer to construct $\harmonics_{n}^{(r)}$, for all $v \in \harmonics_{n}^{(r)}$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
 Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$.
@@
 
-	Thus keeping reduced form of the polynomials decreases space complexity, and also time complexity when applying operators.
+	Thus keeping reduced forms of the polynomials decreases space complexity, and also time complexity when applying operators.
 Note that each time a polarization operator is applied to an element, the normal reduced form of the new element obtained is computed again.
@@
 
-		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$ and has reduced form $x_1\theta_2$.
+		$V_{3} = -x_{1}^{2} x_{2} + x_{1} x_{2}^{2} + x_{1}^{2} x_{3} - x_{2}^{2} x_{3} - x_{1} x_{3}^{2} + x_{2} x_{3}^{2}$ is of type $(1,1,1)$ and has reduced form $x_1^2x_2$.
 
-		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$ and has reduced form $-\theta_1$.
+		$\partial_{x_2}V_{3} = -x_{1}^{2} + 2 x_{1} x_{2} - 2 x_{2} x_{3} + x_{3}^{2}$ is of type $(2,1)$ and has reduced form $x_1^2 - 2x_1x_2$.
 	\end{example}
 
-	In practice, the antisymmetries are exploited first when projecting $\mathcal{E}_\lambda^{(1)}$ onto isotypic components.
+	In practice, the antisymmetries are exploited first when projecting $\harmonics_n^{(1)}$ onto its isotypic components.
 When applying the Young idempotent, the reduced form of each element is computed.
@@
 	\begin{example}
-			Compute $\harmonics_3^{(2)} = \mathcal{E}_3^{(2)}$ exploiting antisymmetries. 
+			Compute $\harmonics_3^{(2)}$ exploiting antisymmetries. 
 		\begin{sagecommandline}
@@
 			sage: derivatives = partial_derivatives(v.parent())
-			sage: E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+			sage: H_3 = Subspace({v.multidegree(): [v]}, derivatives)
 		\end{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: E_3 = IsotypicComponent(E_3, 3, use_antisymmetry=True)
-			%sage: E_3[Partition([3])].basis()
-			sage: E_3[Partition([2,1])].basis()
-			sage: E_3[Partition([1,1,1])].basis()
+			sage: H_3 = IsotypicComponent(H_3, 3, use_antisymmetry=True)
+			%sage: H_3[Partition([3])].basis()
+			sage: H_3[Partition([2,1])].basis()
+			sage: H_3[Partition([1,1,1])].basis()
 		\end{sagecommandline}
@@
 		\begin{sagecommandline}
-			sage: p = E_3[Partition([2,1])].basis().values()[0][0]
+			sage: p = H_3[Partition([2,1])].basis().values()[0][0]
 			sage: p
@@
 		\begin{sagecommandline}
-			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2))
-			sage: E_3[Partition([2,1])].basis()
+			sage: H_3 = PolarizedSpace(H_3, polarization_operators(2))
+			sage: H_3[Partition([2,1])].basis()
 		\end{sagecommandline}
@@
 
-	The space $\mathcal{E}_\lambda$ is symmetric with respect to permutation of rows of $X$, and such permutations exchange multigraded components.
+	The space $\harmonics_{n}^{(r)}$ is symmetric with respect to permutation of rows of $X$, and such permutations exchange multigraded components.
 For example, for $r=3$, the homogeneous components of respective multidegree $(4,2,1)$ and $(2,1,4)$ coincide up to cycling of the rows.
-This means that there are polynomials in different homogeneous component that are the same up to a permutation of the sets of variables and that we have redundant information.
+This means that there are polynomials in different homogeneous components that are the same up to a permutation of the sets of variables and that we have redundant information.
 
@@
 Whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows.
-It can then easily be shown that those tweaked polarization operators properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$.
-\pauline{Tweaked polarizators don't generate the whole space only the decreasing multidegree components.}
+It can then easily be shown that those tweaked polarization operators properly generate the whole $\harmonics_{n}^{(r)}$ space from $\harmonics_n^ {(1)}$.
+\pauline{Tweaked polarizators don't generate the whole space only the decreasing multidegree components, right?}
 
@@
 
-		The polynomial $x_1^2 - 2x_1x_2 + 2x_2x_3 - x_3^2 \in \mathcal{H}_{3}$ has multidegree $(1,0)$ so the same polynomial with multidegree $(0,1)$ that is $y_1^2 - 2y_1y_2 + 2y_2y_3 - y_3^2$ also appears in $\mathcal{H}_{3}$ but it is not necessary to compute it explicitly.
+		The polynomial $x_1^2 - 2x_1x_2 + 2x_2x_3 - x_3^2 \in \mathcal{H}_{3}^{(2)}$ has multidegree $(1,0)$ so the same polynomial with multidegree $(0,1)$ that is $y_1^2 - 2y_1y_2 + 2y_2y_3 - y_3^2$ also appears in $\mathcal{H}_{3}^{(2)}$ but it is not necessary to compute it explicitly.
 		%$-2x_{1} y_{1} y_{2} + x_{1} y_{2}^{2} \in \mathcal{H}_{3}$ so $-2y_{1} x_{1} x_{2} + y_{1} x_{2}^{2} \in \mathcal{H}_{3}$
@@
 
-	In practice, when we polarize $\mathcal{E}_\lambda^{(1)}$, tweaked polarization operators are given in argument to \texttt{PolarizedSpace} instead of the classical ones.
+	In practice, when we polarize $\harmonics_{n}^{(1)}$, tweaked polarization operators are given in argument to \texttt{PolarizedSpace} instead of the classical ones.
 As said above, when specifying the row symmetries, only components of decreasing multidegree appear in the final result.
 
-	\begin{example} Exploiting both antisymmetries of columns and row symmetries, the homogeneous components for $\mathcal{E}_3^{(2)}$ become the following.
+	\begin{example} Exploiting both antisymmetries of columns and row symmetries, the homogeneous components for $\harmonics_3^{(2)}$ become the following.
 		\begin{sagesilent}
@@
 			derivatives = partial_derivatives(v.parent())
-			E_3 = Subspace({v.multidegree(): [v]}, derivatives)
+			H_3 = Subspace({v.multidegree(): [v]}, derivatives)
 		\end{sagesilent}
 		\begin{sagecommandline}
-			sage: E_3 = IsotypicComponent(E_3, 3, use_antisymmetry=True)
-			sage: E_3 = PolarizedSpace(E_3, polarization_operators(2, row_symmetry="permutation"))
-			sage: E_3[Partition([1,1,1])].basis()
-			sage: E_3[Partition([2,1])].basis()
-			sage: E_3[Partition([3])].basis()
+			sage: H_3 = IsotypicComponent(H_3, 3, use_antisymmetry=True)
+			sage: H_3 = PolarizedSpace(H_3, polarization_operators(2, row_symmetry="permutation"))
+			sage: H_3[Partition([1,1,1])].basis()
+			sage: H_3[Partition([2,1])].basis()
+			sage: H_3[Partition([3])].basis()
 		\end{sagecommandline}	
@@
 
-	As said before, the $\GLr$-character of $\mathcal{E}_\lambda$ is given by the multidegree of the homogeneous components.
-In other words, for a given isotypic component $\mathcal{E}_{\lambda,\mu}$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}} q^{d}$ where the sum is over all homogeneous component $\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}$ of type $\mu$ and multidegree $d$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
+	As said before, the $\GLr$-character of $\harmonics_n^{(r)}$ is given by the multidegree of the homogeneous components.
+In other words, for a given isotypic component $\harmonics_{\mu}^{(r)}$, $\mu \vdash n$, the $\GLr$-character associated to this component is given by $$\sum_{\harmonics_{\mu,d}^{(r)}} q^{d}$$ where the sum is over all homogeneous component $\harmonics_{\mu,d}^{(r)}$ of type $\mu$ and multidegree $d$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.
 
-	When exploiting the row symmetries, since we don't compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation.
+	When exploiting the row symmetries, since we compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation.
 However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions $m_d$ instead of summations to recover the character of $\GLr$ in each isotypic component.
@@
 It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.
+\\
+
+	Finding an efficient way to generate $\harmonics_{n}^{(r)}$ is the main part of the computation. Once we have the isotypic components separated by multidegree, we obtain immediatly the character.
+
+	\begin{example} We compute the character of $\harmonics_{3}^{(r)}$. Since we exploit row symmetry, we have to specify it in order to use monomials instead of sums as explain above. 
+		\begin{sagecommandline}
+			sage: character(H_3, row_symmetry="permutation")
+		\end{sagecommandline}
+	We finally obtain that the character of $\harmonics_{3}^{(r)}$ for $r \geq 2$ is $$\harmonics_{3}^{(r)} = 1 \otimes s_{3} +(s_{1} + s_{2}) \otimes s_{2,1} +(s_{1,1} + s_{3}) \otimes s_{1,1,1}.$$
+	\end{example}
 
@@
 
-	\pauline{I changed nothing in the two following subsections.}
+	\pauline{I changed nothing in the two following subsections. I leave it to you Nicolas.}
 	Building on the previous strategy, it would be tempting to only compute the subspace of $sl_r$ highest weight vectors within each $\harmonics_k^P$.
@@
 	\nicolas{2-3 paragraphs of announcement in the introduction}
-	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
+	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman introduce a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
 
@@
 
-	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}.
+	With a similar idea, François Bergeron introduce another generalization of the diagonal harmonics, with \emph{inert variables}.
 We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
@@
 
+	\begin{figure}[H]
+		\centering
+		\begin{tikzpicture}
+		\draw node{$\begin{pmatrix}
+			x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
+			x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
+			\vdots & \vdots & \ddots & \vdots \\
+			x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\ 
+			\theta_{1} & \theta_{2} & \cdots & \theta_{n}
+			\end{pmatrix}$ } (0,0);
+		\draw (-2.4,.6)+(60:.25)
+		[xscale=.5,yscale=3.5,->,rotate=80] arc(-40:290:.25);
+		\node at (-3,0.3) {{\small$\GLr$}};
+		\draw (-.6,-1.7)+(60:.25)
+		[xscale=5.8,yscale=.6,->,rotate=-210] arc(-40:290:.25);
+		\node at (0,-2.1) {{\small$\Sn$}};
+		\draw (-3,-.85) -- (-1.5,-.85);
+		\end{tikzpicture}
+		\caption{Simultaneous actions of $\GLr$ and $\Sn$ on $X$ with inert variables.}
+	\end{figure}
+
 	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
-Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} = \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
 
 	\begin{example}
-		The partition $2,1$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+		The partition $(2,1)$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
 	\end{example}
@@
 We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
-The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = n$.
+The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = (n)$.
 \\
@@
 
-	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute. \\
+	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute but hopefully most of the strategies we used to compute the character of $\harmonics_{n}^{(r)}$ work for $\mathcal{E}_\lambda^{(r)}$.
+
+	Therefore, we, once again, use polarization to compute $\mathcal{E}_\lambda^{(r)}$ from $\mathcal{E}_\lambda^{(1)}$, exploit the multigrading.
+We use the same isotypic projector to obtain the isotypic components, then we can still exploit the columns antisymmetries.
+%	\begin{example} ~
+%		
+%		$V_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is of type $(1,1,1)$ and has reduced form $x_1\theta_2$.
+%		
+%		$\partial_{x_2}V_{21} = -\theta_1 + \theta_3$ is of type $(2,1)$ and has reduced form $-\theta_1$.
+%	\end{example}
+	Finally, $\mathcal{E}_\lambda^{(r)}$ is still symmetric with respect to a permutation of the rows of $X$ containing classical variables so we exploit row symmetries in this case too.\\
+
+	\begin{example} In the following example, we use different strategies to compute $\mathcal{E}_{2,1}^{(2)}$.
+
+		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables exploiting multidegree. 
+		\begin{sagecommandline}
+			sage: v = vandermonde(Partition([2,1]))
+			sage: v
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: derivatives
+			sage: E_21 = Subspace({v.multidegree(): [v]}, derivatives)
+			sage: E_21.basis()
+			sage: E_21.dimension()
+		\end{sagecommandline}
+		And we project on isotypic component, using antisymmetries. 
+		\begin{sagecommandline}
+			sage: E_21 = IsotypicComponent(E_21, 3,use_antisymmetry=True)
+			sage: E_21
+		\end{sagecommandline}
+		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. We also exploit row symmetries. 
+		\begin{sagecommandline}
+			sage: polarizators = polarization_operators(2, row_symmetry="permutation")
+			sage: E_21 = PolarizedSpace(E_21, polarizators)
+			sage: E_21[Partition([1,1,1])].basis()
+			sage: E_21[Partition([2,1])].basis()
+		\end{sagecommandline}
+		And we easily obtain the character for $\mathcal{E}_{2,1}$. 
+	 	\begin{sagecommandline}
+		 	sage: character(E_21, row_symmetry="permutation")
+		\end{sagecommandline}
+
+	So the character of $\mathcal{E}_{2,1}^{(r)}$ for $r \geq 2$ is $$\mathcal{E}_{2,1}^{(r)} = 1 \otimes s_{2,1} + s_{1} \otimes s_{1,1,1} .$$
+	\end{example}
 
@@
 
-	\pauline{Change title}
+	Talk about non partition diagram : compositions and diagram with hole(s) (quotient).
 
-	Ask Francois.\\
-	Talk about non partition diagram, with or without hole (compositions).
-
-	\begin{definition} \pauline{Steenrod operators? }
+	\begin{definition}
 		The \emph{Steenrod operator} $St_{x_a}^k$ for $k>1$ is given by

### 2019-07-24 compute_character.py
Force number of cpus to be able to do parallel computation

@@ -587,7 +587,7 @@ def character(S, left_basis=s, right_basis=s, row_symmetry=None):
                 charac += tensor([charac_nu, right_basis(s(nu))])
         return charac
         
-@parallel
+@parallel(4)
 def parallel_character(S, operators, row_symmetry="permutation", add_degrees=add_degrees_isotypic):
     """
     Return a dictionnary corresponding to the character of the polarized version of the 
@@ -781,7 +781,6 @@ def E_mu(mu, use_antisymmetry=True, row_symmetry="permutation", parallel=False):
         s[] # s[1, 1, 1]
 
     """
-
     n = Integer(mu.size())
     # Determinant computation
     v = vandermonde(mu)

### 2019-07-24 article/article.tex
Complete section on diagonal hamonics with inert variables.

@@
 \newcommand{\Sym}[1]{\mathbb{S}_{#1}}
+\newcommand{\Elambda}[1]{\mathcal{E}_{#1}}
+\newcommand{\Elambdar}[2]{\mathcal{E}_{#1}^{(#2)}}
 
@@
 \nicolas{Ajouter des exemples au fur et à mesure}
+\pauline{J'ai déjà mis pas mal d'exemples. Il en faut plus?}
 
@@
 
-	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.
+	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.\\
 
 	In the next section, we expose strategies used to go further in the computation of those characters.
-In the last section, we present some applications/generalizations we are able to make using the same computation strategies.
-\pauline{annonce du contenu à réécrire}
+Those strategies are not limited to the diagonal harmonic polynomials.
+They can be used in other generalizations.
+We introduced some of these generalizations in the last section and discuss some applications of these computations.
 
@@
 
-	In fact we can do better. \pauline{Does it work only for $\harmonics_n^{(r)}$ or also for $\mathcal{E}_\lambda$?}
+	In fact we can do better. \pauline{Does it work only for $\harmonics_n^{(r)}$ or also for $\Elambda{\lambda}$?}
 	Fix a partition $\mu$. Recall that a basis of the Specht module $S_\mu$  is given by the family of Garnir/Specht polynomials $(G_{P})_P$ indexed by standard tableaux $P$ of shape $\mu$.
@@
 
-	\section{Applications}
+	\section{Applications / Generalizations}
 
@@
 The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
+
+	Note that inert variables, like constants, do not contribute to the degree of the polynomials in which they intervene. They can be considered as "degree 0 variables".
 
@@
 		\node at (0,-2.1) {{\small$\Sn$}};
-		\draw (-3,-.85) -- (-1.5,-.85);
+		\draw (-1.8,-.85) -- (1.8,-.85);
 		\end{tikzpicture}
-		\caption{Simultaneous actions of $\GLr$ and $\Sn$ on $X$ with inert variables.}
+		\caption{Simultaneous actions of $\GLr$ and $\Sn$ on classical and inert variables.}
 	\end{figure}
@@
 	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in these operators.
-We denote this space by $\mathcal{E}_{\lambda}^{(r)}$.
-The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\mathcal{E}_{\lambda}^{(r)}$ for $\lambda = (n)$.
+We denote this space by $\Elambdar{\lambda}{r}$.
+The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\Elambdar{\lambda}{r}$ for $\lambda = (n)$.
 \\
 
-	The character of $\mathcal{E}_{\lambda}^{(r)}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
-Therefore, when the precision is not necessary, we will drop the exponent and simply write $\mathcal{E}_{\lambda}$ for $\mathcal{E}_{\lambda}^{(r)}$ with $r \geq n$.
-\\
+	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
+Therefore, when the precision is not necessary, we will drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
 
-	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\mathcal{E}_\lambda^{(r)}$ is not easy to compute but hopefully most of the strategies we used to compute the character of $\harmonics_{n}^{(r)}$ work for $\mathcal{E}_\lambda^{(r)}$.
+	This property also gives use an upper bound for the number of sets of variables needed in the computation. \\
 
-	Therefore, we, once again, use polarization to compute $\mathcal{E}_\lambda^{(r)}$ from $\mathcal{E}_\lambda^{(1)}$, exploit the multigrading.
+	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we used to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.
+
+	Therefore, we, once again, use polarization to compute $\Elambdar{\lambda}{r}$ from $\Elambda{\lambda}{1}$ and exploit the multigrading.
 We use the same isotypic projector to obtain the isotypic components, then we can still exploit the columns antisymmetries.
@@
 %	\end{example}
-	Finally, $\mathcal{E}_\lambda^{(r)}$ is still symmetric with respect to a permutation of the rows of $X$ containing classical variables so we exploit row symmetries in this case too.\\
+	Finally, $\Elambdar{\lambda}{r}$ is still symmetric with respect to a permutation of the rows of $X$ containing classical variables so we exploit row symmetries in this case too.\\
 
-	\begin{example} In the following example, we use different strategies to compute $\mathcal{E}_{2,1}^{(2)}$.
+	\begin{example} In the following example, we use different strategies to compute $\Elambdar{2,1}{2}$.
 
-		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables exploiting multidegree. 
+		First, we compute $\Elambdar{2,1}{1}$, for one row of variables exploiting multidegree. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. We also exploit row symmetries. 
+		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\Elambdar{2,1}{2}$, still with multidegree. We also exploit row symmetries. 
 		\begin{sagecommandline}
@@
 		\end{sagecommandline}
-		And we easily obtain the character for $\mathcal{E}_{2,1}$. 
+		And we obtain the character for $\Elambda{2,1}$. 
 	 	\begin{sagecommandline}
@@
 
-	So the character of $\mathcal{E}_{2,1}^{(r)}$ for $r \geq 2$ is $$\mathcal{E}_{2,1}^{(r)} = 1 \otimes s_{2,1} + s_{1} \otimes s_{1,1,1} .$$
+	So the character of $\Elambdar{2,1}{r}$ for $r \geq 2$ is $$\Elambdar{2,1}{r} = 1 \otimes s_{2,1} + s_{1} \otimes s_{1,1,1} .$$
 	\end{example}
 
-	\subsection{Further work}
+	~
+
+	We presented in the previous examples all the steps of the computation using or not different strategies to optimize the computations.
+Thus, the code can be easily adapted to other generators and other operators (see section \ref{section_futher_work} for examples) at each step.
+
+	Therefore, to simply compute the character of $\Elambda{\mu}$ only setting the optimizations used, one can use the function \texttt{E\_mu} that takes in argument a partition or a diagram and returns the complete character $\Elambda{\mu}$.
+By default, this function uses antisymmetries of column and symmetries of rows, but this can be disabled.
+
+	Furthermore, parallel computation can be activate in this function.
+Indeed, once $\Elambda{\lambda}{1}$ is projected on its isotypic component, the computation is independent on each isotypic component and the character is simply the sum of the characters of all isotypic components.
+
+	\begin{example} \pauline{Ajouter d'autres exemples pertinents.}
+		We compute $\Elambda{1,1,1}$
+
+		\begin{sagecommandline}
+			sage: E_mu(Partition([1,1,1]))
+		\end{sagecommandline}	
+	\end{example}
+
+	\subsection{Further work}\label{section_futher_work}
 

### 2019-07-24 article/article.tex
Check verbs to use present everywhere.

@@
 	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
-It was then extended to compute other characters of polynomial spaces.
+It is then extended to compute other characters of polynomial spaces.
 
-	The main achievement is a calculation of the character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
+	The main achievement is a calculation of the character of the diagonal harmonic polynomials for $n=6$ and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.
 
 	This is a potentially huge calculation ($\harmonics_6^{(5)}$ is of dimension $5.8 \cdot10^5$), involving polynomials of degree up to $15$ in $30$ variables with thousands of terms.
-So we had to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
-As much as possible, the code was written to be modular and reusable.
+So we have to combine several strategies that each reduced the time and/or memory complexity by one or two orders of magnitude.
+As much as possible, the code is written to be modular and reusable.
 
@@
 The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
-It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.
-\pauline{Add details about grading.}
+It inherits from R a structure of graded $\GLr \times \Sn$ bi-module.
+The degree of a polynomial in $R_{\Sn}$ is defined to be the sum of the degrees in each set of variables.
 
@@
 
-    In order to study those spaces, we will use representation theory and characters.
-Intuitively, through representation theory, the purpose is to cut modules into irreducible submodules according to the group action.
-Those submodules are then represented by irreducible characters that encodes the group action on each submodule.
+    In order to study those spaces, we use representation theory and characters.
+Intuitively, we want to decompose modules into irreducible submodules according to the group action.
+Those submodules are then represented by irreducible characters that encode the group action on each submodule.
 For $\GLr$ and $\Sn$, irreducible characters can be indexed by partitions and encoded by Schur functions.
-Knowing the irreducible characters gives informations of the studied module such as the dimension.
+Knowing the irreducible characters gives information on the studied module such as the dimension.
 
-    We will not enter into details on representation theory here but for more on this topic see \cite{FultonHarris1991}.
-Also, \cite{Sagan} is a classical reference for representation theory of the symmetric group and see \cite{Green2007} for more on the polynomial representations of the general linear group.
+    We don't enter into details on representation theory here but for more on this topic see \cite{FultonHarris1991}.
+Also, \cite{Sagan} is a classical reference for representation theory of the symmetric group and \cite{Green2007} is about polynomial representations of the general linear group.
 \\
 
-   	The characters of the harmonic and diagonal harmonic polynomials spaces have been studied a lot until now.
+   	The characters of the harmonic and diagonal harmonic polynomial spaces have been studied a lot until now.
 For example, it is known that, when r=1, the action of $GL_1$ is trivial and $R_{\Sn}$ carries the usual graded representation of $\Sn$.
@@
 
-	Throughout this article, we will write the spaces and their the character the same way, except if there might be a confusion, then the variables will be added to the character and we will write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.\\
+	Throughout this article, we write the spaces and their the character the same way, except if there might be a confusion, then the variables are added to the character and we write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.\\
 
@@
 
-	So we took the classical route of realizing the coinvariant ring as the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials.
+	So we take the classical route of realizing the coinvariant ring as the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials.
 	This is the space of those polynomials that satisfy the equations given by the multisymmetric functions seen as differential operators.
 
-	Solving those differential equations would not be tractable either. So instead we used operators, partial derivatives and polarization operators defined in the previous section. \\
+	Solving those differential equations would not be tractable either. So instead we use partial derivatives and polarization operators defined in the previous section. \\
 
@@
 Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$.
-	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
+	It is therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
 We chose to keep the smallest representative monomial in lexicographic order and call the result the \emph{normal reduced form} of $v$.

### 2019-07-24 article/article.tex
Correct other tense mistakes.

@@
 	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
-Therefore, when the precision is not necessary, we will drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
+Therefore, when the precision is not necessary, we drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
 
@@
 
-	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we used to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.
+	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we use to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.
 
@@
 
-	We presented in the previous examples all the steps of the computation using or not different strategies to optimize the computations.
+	We presente in the previous examples all the steps of the computation using or not different strategies to optimize the computations.
 Thus, the code can be easily adapted to other generators and other operators (see section \ref{section_futher_work} for examples) at each step.

### 2019-07-25 article/article.tex
Add some ideas in further work section.

@@
 
-	\subsection{Inert variables}
+	\subsection{Inert variables} \label{section_inert_variables}
 	\nicolas{2-3 paragraphs of announcement in the introduction}
@@
 
-	Talk about non partition diagram : compositions and diagram with hole(s) (quotient).
+	The generalization of the Vandermonde determinant given in subsection \ref{section_inert_variables} is also well defined for other diagrams that are not Ferrer's diagrams of partitions.
+
+	For example, we could consider a diagram corresponding to a composition $\alpha = (\alpha_1, \alpha_2, \dots, \alpha_\ell)$.
+Like for a partition, the diagram of $\alpha$ is bottom left justified and the $i$-th row contains $\alpha_i$ boxes, for all $1 \leq i \leq \ell$.
+Then the exact same definition applied for $V_\alpha$ and we can defined the subspace associated to $\alpha$ and compute its character.
+
+	Thanks to our computations, we are able to show the following proposition.
+
+	\begin{prop}
+		Let $\alpha$ be a composition of $n$ and denote $\lambda(\alpha)$ the partition obtained by reordering the parts of $\alpha$.
+And denote by $\Elambdar{\alpha}{r}$ the character of the smallest $\GLr \times \Sn$-submodule containing $V_\alpha$ and closed by partial derivation and polarization.
+Then we have
+		$$\Elambdar{\alpha}{r} = \Elambdar{\lambda(\alpha)}{r}.$$
+	\end{prop}
+
+	\begin{example}
+		Add example. 
+	\end{example}
+
+	~
+
+	Following the same idea, let $\gamma$ by any set of cells of $\NN^2$ given by the cartesian coordinates of their bottom left corner.
+The determinant associated to $\gamma$ still have the same definition.
+$$V_{\gamma} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+
+	We define $\mathcal{M}_{\gamma}^{(r)}$ to be the smallest $\GLr \times \Sn$-submodule containing $V_\gamma$ and closed by partial derivation and polarization and we use the same notation for the character.
+\pauline{motivate introduction of the quotient ans Steenrod operators.}
+
+	Let $f \in \QQ[X]$, we define $f(\partial X)$ to be the function $f$ in which we replaced $x_{i,j}^k$ by $\partial_{x_{i,j}}^k$.
+If $f$ is invariant under the diagonal action of $\Sn$ on $X$, $f(\partial X)$ is called a symmetric derivative.
+
+	We denote by $\mathcal{N}_{\gamma}^{(r)}$ the union of all the images of $\mathcal{M}_{\gamma}^{(r)}$ by a symmetric derivative.
+Finally, we have $$\Elambdar{\gamma}{r} := \mathcal{M}_{\gamma}^{(r)} / \mathcal{N}_{\gamma}^{(r)}.
+$$
+	Note that when $\gamma$ is a composition or a partition,$ \mathcal{N}_{\gamma}^{(r)} = \emptyset$ and we still have the same definition for $\Elambdar{\gamma}{r} = \mathcal{M}_{\gamma}^{(r)}$.
 

### 2019-07-25 article/article.tex
Add details about young idempotent.

@@
 	\begin{theorem}
-		The Young symmetrizer $c_{\lambda}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $A_{\lambda}$ of $\Sn$.
+		The Young symmetrizer $c_{\mu}$ is idempotent up to a scalar and the image of $c_{\lambda}$ by right multiplication on $\CC \Sn$ is an irreducible representation $A_{\mu}$ of $\Sn$.
 		Thus any irreducible representation can be obtain this way for a unique partition. 
@@
 	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
-	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on an adapted basis of $\harmonics_{n}^{(r)}$ gives representatives of the isotypic components of $\Sn$.
-\pauline{Need more details here.}  \\
+	This theorem guarantees that $c_{\mu}$ is an isotypic projector.
+Thus applying $c_\mu$ on $\harmonics_{n}^{(r)}$ gives the $\Sn$-isotypic component of type $\mu$ of $\harmonics_{n}^{(r)}$.
+Moreover, using an adapted basis \pauline{On a vraiment besoin d'une base particulière?} of $\harmonics_{n}^{(r)}$ guarantees that we obtain enough elements to be able to construct a basis of the isotypic component and thus we obtain the multiplicity of the irreducible representation of $\Sn$ corresponding to $\mu$.
+\\
 
 	The action of $\GLr$ commutes with the action of $\Sn$, then the polarization operators commute with the Young symmetrizer.
-Therefore, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n}^{(r)}$ by starting from a basis of $\harmonics_{n}^{(1)}$ that itself is adapted to its decomposition into isotypic components:
+Therefore, in practice, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n}^{(r)}$ by starting from a basis of $\harmonics_{n}^{(1)}$ and decomposing it into isotypic components:
 	$$\harmonics_{n}^{(1)}=:\bigoplus_{\mu \vdash n} \harmonics_{\mu}^{(1)},$$

### 2019-07-25 add_degree.py
Move functions in proper file.

@@ -30,3 +30,52 @@ def add_degree(d1,d2):
     if not all(i>=0 for i in d):
         raise ValueError("invalid degree")
     return d
+    
+    
+def add_degrees_isotypic(gen_deg, op_deg):
+    """
+    Compute the sum componentwise of the lists of integrers contained in d1 and d2 
+    and return a grading set and the partition contained in d2 as result.
+    
+    INPUT:
+        - ``d1`` -- list containing a list of integers and a partition
+        - ``d2`` -- list of integers
+
+    EXAMPLES::
+        sage: d1 = ([3,0],[2,1])
+        sage: d2 = [-1,0]
+        sage: add_degrees_isotypic(d1, d2)
+        ((2, 0), [2, 1])
+        sage: add_degrees_isotypic(([2,0,1],[3,2]), [-1,0,0])
+        ((1, 0, 1), [3, 2])
+        sage: add_degrees_isotypic(([2,0,1],[3,2]), [-1,-1,0])
+        Traceback (most recent call last):
+        ...
+        ValueError: invalid degree
+    """
+    D = cartesian_product([ZZ for i in range(len(gen_deg[0]))])
+    d = D(gen_deg[0])+D(op_deg)
+    if not all(i>=0 for i in d):
+        raise ValueError("invalid degree")
+    return d, gen_deg[1]
+    
+def add_degrees_symmetric(gen_deg, op_deg):
+    """
+    Compute the sum componentwise of the lists of integrers contained in d1 and d2 
+    and return an ordered grading set and the partition contained in d2 as result.
+    
+    INPUT:
+        - ``d1`` -- list containing a list of integers and a partition
+        - ``d2`` -- list of integers
+
+    EXAMPLES::
+        sage: d1 = ([0,3],[2,1])
+        sage: d2 = [0,-1]
+        sage: add_degrees_symmetric(d1, d2)
+        ((2, 0), [2, 1])
+        sage: add_degrees_symmetric(([2,0,1],[3,2]), [-1,0,0])
+        ((1, 1, 0), [3, 2])
+    """
+    D = cartesian_product([ZZ for i in range(len(gen_deg[0]))])
+    d1, d2 = add_degrees_isotypic(gen_deg, op_deg)
+    return D(sorted(d1, reverse=True)), d2

### 2019-07-25 compute_character.py

@@ -340,46 +340,6 @@ def IsotypicComponent(S, arg, use_antisymmetry=False):
         return result[key]
     else:
         return result
-
-
-def add_degrees_isotypic(gen_deg, op_deg):
-    """
-    Compute the sum componentwise of the lists of integrers contained in d1 and d2 
-    and return a grading set and the partition contained in d2 as result.
-    
-    INPUT:
-        - ``d1`` -- list containing a list of integers and a partition
-        - ``d2`` -- list of integers
-
-    EXAMPLES::
-        sage: d1 = ([3,0],[2,1])
-        sage: d2 = [-1,0]
-        sage: add_degrees_isotypic(d1,d2)
-        ((2, 0), [2, 1])
-
-    """
-    D = cartesian_product([ZZ for i in range(len(gen_deg[0]))])
-    return D(gen_deg[0])+D(op_deg), gen_deg[1]
-    
-def add_degrees_symmetric(gen_deg,op_deg):
-    """
-    Compute the sum componentwise of the lists of integrers contained in d1 and d2 
-    and return an ordered grading set and the partition contained in d2 as result.
-    
-    INPUT:
-        - ``d1`` -- list containing a list of integers and a partition
-        - ``d2`` -- list of integers
-
-    EXAMPLES::
-        sage: d1 = ([0, 3],[2,1])
-        sage: d2 = [0, -1]
-        sage: add_degrees_symmetric(d1,d2)
-        ((2, 0), [2, 1])
-
-    """
-    D = cartesian_product([ZZ for i in range(len(gen_deg[0]))])
-    d = D(gen_deg[0])+D(op_deg)
-    return D(sorted(d, reverse=True)), gen_deg[1]
     
 ##############################################################################
 # Polarization Space

### 2019-07-25 antisymmetric_utilities.pyx
Remove useless imports and correct documentations

@@ -2,15 +2,11 @@ from sage.structure.parent cimport Parent
 from sage.structure.element cimport Element
 from sage.rings.polynomial.polydict cimport ETuple
 
-from sage.combinat.partition import Partition, Partitions
+from sage.combinat.partition import Partition
 from sage.groups.perm_gps.permgroup_element import PermutationGroupElement
-import sage.combinat.tableau
-from sage.combinat.tableau import StandardTableau, StandardTableaux
+from sage.combinat.tableau import StandardTableau
 
 import utilities
-#from utilities cimport diagonal_cmp
-#from utilities cimport diagonal_swap
-#from utilities cimport items_of_vector
 
 cpdef diagonal_antisort(exponents, int n, int r, tuple positions_list):
     """
@@ -99,8 +95,7 @@ cpdef is_diagonal_antisorted(exponents, int n, int r, tuple positions_list):
         False
         sage: is_diagonal_antisorted([1,2,3,4,5,6], 6, 1, ((0,2,4),(1,3,5)))
         False
-
-
+        
     """
     cdef int i, j
     cdef tuple positions
@@ -168,8 +163,6 @@ def antisymmetric_normal(p, int n, int r, tuple positions):
         sage: p1 = -2*x10*x11*x20 - 2*x10^2*x21 + 2*x10*x11*x21
         sage: antisymmetric_normal(p1, 3, 3, ((0,1,2),))
         -4*x10*x11*x20 - 2*x10^2*x21
-
-
     """
     cdef Parent R = p.parent()
     cdef dict d = {}
@@ -186,6 +179,8 @@ def antisymmetric_normal(p, int n, int r, tuple positions):
 def reduce_antisymmetric_normal(p, int n, int r, tuple positions):
     """
     Return the terms of `p` which are diagonally antisorted.
+    
+    See :func:`antisymmetric_normal` for details.
 
     INPUT:
 
@@ -193,7 +188,7 @@ def reduce_antisymmetric_normal(p, int n, int r, tuple positions):
     - ``r``, ``n`` -- nonnegative integers
     - ``positions`` -- a tuple of tuple of positions
 
-    This coincides with reduce_antisymmetric_normal (and is faster) if
+    This coincides with antisymmetric_normal (and is faster) if
     `p` is antisymmetric.
 
     EXAMPLES::

### 2019-07-25 young_idempotent.py
Add import

@@ -1,9 +1,10 @@
 #!/usr/bin/env python
 # -*- coding: utf-8 -*-
 
+from sage.misc.cachefunc import cached_function
+
 from sage.combinat.partition import Partition, Partitions
 from sage.combinat.permutation import Permutation
-
 from sage.calculus.functional import derivative
 
 from antisymmetric_utilities import *

### 2019-07-25 diagonal_polynomial_ring.py
Complete documentation

@@ -3,12 +3,10 @@
 
 import functools
 
-from sage.misc.cachefunc import cached_method, cached_function
-from sage.structure.sage_object import load
-
+from sage.misc.cachefunc import cached_method
 from sage.parallel.decorate import parallel
-from sage.misc.misc_c import prod
 
+from sage.misc.misc_c import prod
 from sage.rings.polynomial.polynomial_ring_constructor import PolynomialRing
 from sage.rings.integer_ring import ZZ
 from sage.rings.rational_field import QQ
@@ -17,11 +15,11 @@ from sage.categories.cartesian_product import cartesian_product
 from sage.combinat.words.word import Word
 from sage.matrix.constructor import matrix
 
+from utilities import *
+from antisymmetric_utilities import *
 from isomorphic_object import *
 from polynomial_derivative import *
 
-from utilities import *
-from antisymmetric_utilities import *
 
 ##############################################################################
 # Polynomial ring with diagonal action
@@ -38,7 +36,6 @@ class DiagonalPolynomialRing(IsomorphicObject):
         sage: P
         Diagonal Polynomial Ring with 3 rows of 4 variables over Rational Field
 
-
         sage: P = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
         sage: P
         Diagonal Polynomial Ring with 3 rows of 4 variables and inert variables over Rational Field
@@ -52,7 +49,6 @@ class DiagonalPolynomialRing(IsomorphicObject):
         self._inert = inert
         self._P = P
         self._R = R
-        self._Q = PolynomialRing(QQ,'q',r)
         self._grading_set = cartesian_product([ZZ for i in range(r)])
         self._hilbert_parent = PolynomialRing(ZZ, r, 'q')
         
@@ -69,45 +65,76 @@ class DiagonalPolynomialRing(IsomorphicObject):
             return "Diagonal Polynomial Ring with %s rows of %s variables over %s"%(self._r, self._n, self.base_ring())
         else:
             return "Diagonal Polynomial Ring with %s rows of %s variables and inert variables over %s"%(self._r, self._n, self.base_ring())
-        
-    def Q_gens(self):
+            
+    def variable_names(self):
         """
-        sage: D = DiagonalPolynomialRing(QQ, 4, 3, inert=1)
-        sage: D.Q_gens()
-        (q0, q1, q2)
+        Return the variable names. This is use when calling function
+        inject_variables() on self. 
         """
-        return self._Q.gens()
-        
[…]

### 2019-07-26 diagram.py
Correct error in function name in the tests.

@@ -92,45 +92,45 @@ class Diagram():
         Print the diagram. 
         
         EXAMPLES ::
-            sage: Diagram([(0,0),(1,1),(2,2)]).print()
+            sage: Diagram([(0,0),(1,1),(2,2)]).draw()
                  _
                _|_|
              _|_| 
             |_|   
-            sage: Diagram([(0,0), (1,0), (2,0), (0,1), (2,1)]).print_diagram()
+            sage: Diagram([(0,0), (1,0), (2,0), (0,1), (2,1)]).draw()
              _   _
             |_|_|_|
             |_|_|_|
-            sage: Diagram([(0,2),(1,1),(2,0)]).print_diagram()
+            sage: Diagram([(0,2),(1,1),(2,0)]).draw()
              _
             |_|_   
               |_|_ 
                 |_|
-            sage: Diagram([(0,0),(1,1)]).print_diagram() 
+            sage: Diagram([(0,0),(1,1)]).draw() 
                _
              _|_|
             |_| 
-            sage: Diagram([(0,1),(1,0),(1,1)]).print_diagram()  
+            sage: Diagram([(0,1),(1,0),(1,1)]).draw()  
              _ _
             |_|_|
               |_|
-            sage: Diagram([(0,1),(2,2)]).print_diagram()
+            sage: Diagram([(0,1),(2,2)]).draw()
                  _
              _  |_|
             |_|   
                   
-            sage: Diagram([(0,1),(2,3)]).print_diagram()
+            sage: Diagram([(0,1),(2,3)]).draw()
                  _
                 |_|
              _    
             |_|         
-            sage: Diagram([(0,1),(3,2),(3,3)]).print_diagram()
+            sage: Diagram([(0,1),(3,2),(3,3)]).draw()
                    _
                   |_|
              _    |_|
             |_|     
                     
-            sage: Diagram([(0,1),(3,2),(2,3)]).print_diagram()
+            sage: Diagram([(0,1),(3,2),(2,3)]).draw()
                  _  
                 |_|_ 
              _    |_|

### 2019-07-26 diagonal_polynomial_ring.py
Complete documentation byb adding tests where needed and explainations.

@@ -202,7 +202,7 @@ class DiagonalPolynomialRing(IsomorphicObject):
             print "No inert variables"
             return None
 
-    def derivative_variables(self):
+    def multivar_pol_ring_variables(self):
         """
         Return only the classic variables as variables of a multivariate polynomial ring.
         
@@ -216,11 +216,11 @@ class DiagonalPolynomialRing(IsomorphicObject):
             sage: DP.variables()[0,0].parent()
             Diagonal Polynomial Ring with 3 rows of 3 variables and inert variables over Rational Field
 
-            sage: DP.derivative_variables()
+            sage: DP.multivar_pol_ring_variables()
             [x00 x01 x02]
             [x10 x11 x12]
             [x20 x21 x22]
-            sage: DP.derivative_variables()[0,0].parent()
+            sage: DP.multivar_pol_ring_variables()[0,0].parent()
             Multivariate Polynomial Ring in x00, x01, x02, x10, x11, x12, x20, x21, x22, theta00, theta01, theta02 over Rational Field
 
         """
@@ -330,7 +330,7 @@ class DiagonalPolynomialRing(IsomorphicObject):
         # TODO NICOLAS add documentation
         """
         r = self._r
-        X = self.derivative_variables()
+        X = self.multivar_pol_ring_variables()
         res = []
         for i in range(r):
             res.extend([X[i,j],D[i]])
@@ -345,18 +345,22 @@ class DiagonalPolynomialRing(IsomorphicObject):
 
                 sage: P = DiagonalPolynomialRing(QQ, 3, 2)
                 sage: X = P.algebra_generators()
-                sage: p = X[0,0]*X[0,1]^2 * X[1,0]^2*X[1,1]^3
+                sage: p = X[0,0]*X[1,1]^2 + X[1,0]^2*X[0,1]
                 sage: p.multidegree()
-                (3, 5)
+                (1, 2)
                 sage: P.zero().multidegree()
                 -1
-                sage: P = DiagonalPolynomialRing(QQ, 3, 2, inert=1)
-                sage: X = P.algebra_generators()
-                sage: p = X[0,0]*X[0,1] * X[1,1]^3 * X[2,0]*X[2,1]^2 
-                sage: p.multidegree()
-                (2, 3)
                 
-            TODO : Add examples with inert variables
+                sage: P = DiagonalPolynomialRing(QQ, 3, 2, inert=1)
+                sage: X = P.variables()
+                sage: T = P.inert_variables()
[…]

### 2019-07-26 matrix_of_vectors.py
Add 'TODO' where documentation is needed

@@ -99,6 +99,9 @@ class MatrixOfVectors:
         return vector(self._base_ring, len(self._rank.cache), d, sparse=False)
 
     def vector(self, v):
+        """
+        TODO :: Add Documentation Nicolas
+        """
         R = self.ambient()
         unrank = self._unrank
         # TODO: this only works for polynomials!

### 2019-07-26 matrix_of_vectors.py
Add 'TODO' where documentation needed

@@ -108,9 +108,15 @@ class MatrixOfVectors:
         return R.sum(v[i]* R.monomial(*unrank(i)) for i in range(len(v)))
 
     def vectors(self):
+        """
+        TODO :: Add Documentation Nicolas
+        """
         return tuple(self.vector(v) for v in self._matrix)
 
     def _add_vector_to_matrix(self, m, v): # append?
+        """
+        TODO :: Add Documentation Nicolas
+        """
         r = self.plain_vector(v)
         if len(r) > m.ncols():
             m = m.augment(matrix(self._base_ring, m.nrows(), len(r)-m.ncols()))
@@ -149,6 +155,9 @@ class EchelonMatrixOfVectors(MatrixOfVectors):
         return "A %sx%s echelon matrix of vectors in %s"%(m.nrows(), m.ncols(), self.ambient())
 
     def extend(self, v, word=None):
+        """
+        TODO :: Add Documentation Nicolas
+        """
         self._stats["extend"] += 1
         if not v:
             self._stats["zero"] += 1

### 2019-07-26 diagram.py
REmove useless import

@@ -1,7 +1,6 @@
 #!/usr/bin/env python
 # -*- coding: utf-8 -*-
 
-from sage.combinat.composition import Composition
 from sage.rings.integer import Integer
 
 

### 2019-07-26 subspace.py

@@ -13,8 +13,6 @@ from sage.combinat.free_module import CombinatorialFreeModule
 
 from matrix_of_vectors import *
 
-
-
 class Subspace(object):
     """
     Construct a subspace from generators and linear operators

### 2019-07-26 matrix_of_vectors.py
Clean imports

@@ -2,13 +2,11 @@
 # -*- coding: utf-8 -*-
 
 import operator
-
-from utilities import items_of_vector
-
 from sage.structure.parent import Parent
 from sage.matrix.constructor import matrix
 from sage.modules.free_module_element import vector
 
+from utilities import items_of_vector
 from ranker import *
 
 

### 2019-07-26 polynomial_derivative.py
Clean imports

@@ -4,8 +4,8 @@
 from sage.misc.misc_c import prod
 from sage.functions.other import factorial
 from sage.functions.other import binomial
-
 from sage.structure.element import have_same_parent
+
 from matrix_of_vectors import items_of_vector
 
 ##############################################################################

### 2019-07-26 subspace.py
Clean imports

@@ -4,9 +4,8 @@
 import functools
 
 from sage.misc.constant_function import ConstantFunction
-from sage.misc.cachefunc import cached_method, cached_function
-from sage.structure.parent import Parent
-from sage.combinat.partition import Partition, Partitions
+from sage.misc.cachefunc import cached_method
+from sage.combinat.partition import Partition
 from sage.rings.semirings.non_negative_integer_semiring import NN
 from sage.rings.rational_field import QQ
 from sage.combinat.free_module import CombinatorialFreeModule

### 2019-07-26 utilities.pyx
Clean imports

@@ -1,11 +1,9 @@
-from sage.structure.parent cimport Parent
 from sage.structure.element cimport Element
 from sage.rings.polynomial.polydict cimport ETuple
 from sage.groups.perm_gps.permgroup_element cimport PermutationGroupElement
 
 import sage.combinat.tableau
 from sage.combinat.words.word import Word
-
 from sage.combinat.free_module import CombinatorialFreeModule
 
 cpdef items_of_vector(Element v):

### 2019-07-26 young_idempotent.py
Correct failed doctest and delete useless imports

@@ -126,7 +126,7 @@ def make_deriv_comp_young(x, mu):
         
     EXAMPLES::
         sage: P = DiagonalPolynomialRing(QQ,3,3)
-        sage: X = P.derivative_variables()
+        sage: X = P.multivar_pol_ring_variables()
         sage: [make_deriv_comp_young(x,mu) for x in X[0] for mu in Partitions(3)] 
         [<function f at ...>,
          <function f at ...>,

### 2019-07-26 setup.py
Clean setup file

@@ -15,7 +15,7 @@ def readfile(filename):
 # For the tests
 class SageTest(TestCommand):
     def run_tests(self):
-        errno = os.system("sage -t funcpersist.py matrix_of_vectors.py subspace.py diagram.py diagonal_polynomial_ring.py harmonic.py polarization_space.py add_degree.py derivative_space.py polynomial_derivative.py quotient.py young_idempotent.py isomorphic_object.py ranker.py")
+        errno = os.system("sage -t matrix_of_vectors.py subspace.py diagram.py diagonal_polynomial_ring.py add_degree.py polynomial_derivative.py young_idempotent.py isomorphic_object.py ranker.py")
         if errno != 0:
             sys.exit(1)
 
@@ -41,12 +41,10 @@ setup(
       'Programming Language :: Python :: 2.7',
     ], # classifiers list: https://pypi.python.org/pypi?%3Aaction=list_classifiers
     keywords = "",
-    py_modules=['funcpersist',
-                'matrix_of_vectors', 'subspace',
-                'diagram',
-                'diagonal_polynomial_ring', 'harmonic', 'polarization_space',
-                'add_degree', 'derivative_space', 'polynomial_derivative',
-                'quotient', 'young_idempotent', 'isomorphic_object',
+    py_modules=['matrix_of_vectors', 'subspace',
+                'diagram', 'diagonal_polynomial_ring',
+                'add_degree', 'polynomial_derivative',
+                'young_idempotent', 'isomorphic_object',
                 'ranker'
                ],
     cmdclass = {'test': SageTest}, # adding a special setup command for tests

### 2019-07-26 compute_character.py
Correct failed doctests

@@ -96,7 +96,7 @@ def partial_derivatives(P):
     n = P.ncols()
     r = P.nrows()
     D = P.grading_set()
-    X = P.derivative_variables()
+    X = P.multivar_pol_ring_variables()
     op = {}
     for i in range(r):
         op[D((-1 if j==i else 0 for j in range(r)))] = [attrcall("derivative", X[i,k]) for k in range(n)]
@@ -367,16 +367,18 @@ def PolarizedSpace(S, operators, add_degrees=add_degrees_isotypic):
         ....:     print(value.basis())
         {((2, 1), (1, 1, 1)): (-x00*x01*x10 + 1/2*x01^2*x10 + x00*x02*x10 - 1/2*x02^2*x10 - 1/2*x00^2*x11 + x00*x01*x11 - x01*x02*x11 + 1/2*x02^2*x11 + 1/2*x00^2*x12 - 1/2*x01^2*x12 - x00*x02*x12 + x01*x02*x12,), ((1, 1), (1, 1, 1)): (-x01*x10 + x02*x10 + x00*x11 - x02*x11 - x00*x12 + x01*x12,), ((3, 0), (1, 1, 1)): (x00^2*x01 - x00*x01^2 - x00^2*x02 + x01^2*x02 + x00*x02^2 - x01*x02^2,), ((1, 2), (1, 1, 1)): (-1/2*x01*x10^2 + 1/2*x02*x10^2 - x00*x10*x11 + x01*x10*x11 + 1/2*x00*x11^2 - 1/2*x02*x11^2 + x00*x10*x12 - x02*x10*x12 - x01*x11*x12 + x02*x11*x12 - 1/2*x00*x12^2 + 1/2*x01*x12^2,), ((0, 3), (1, 1, 1)): (x10^2*x11 - x10*x11^2 - x10^2*x12 + x11^2*x12 + x10*x12^2 - x11*x12^2,)}
         {((0, 0), (3,)): (1,)}
-        {((0, 2), (2, 1)): (1/2*x10^2 - x10*x11 + x11*x12 - 1/2*x12^2,), ((0, 1), (2, 1)): (x10 - x12,), ((1, 0), (2, 1)): (x00 - x02,), ((2, 0), (2, 1)): (-1/2*x00^2 + x00*x01 - x01*x02 + 1/2*x02^2,), ((1, 1), (2, 1)): (x00*x10 - x01*x10 - x00*x11 + x02*x11 + x01*x12 - x02*x12,)}
[…]

### 2019-09-03 article/article.tex
Comment futher work section
Add some comments.
Nouveaux essais pour Francois

@@
 		\begin{sagesilent}
-			load("../compute_character.py")
+			load("../character.py")
 		\end{sagesilent}
@@
 Therefore, in practice, we can compute independently each $\Sn$ isotypic component of $\harmonics_{n}^{(r)}$ by starting from a basis of $\harmonics_{n}^{(1)}$ and decomposing it into isotypic components:
-	$$\harmonics_{n}^{(1)}=:\bigoplus_{\mu \vdash n} \harmonics_{\mu}^{(1)},$$
+	$$\harmonics_{n}^{(1)}:=\bigoplus_{\mu \vdash n} \harmonics_{\mu}^{(1)},$$
 
@@
 
+	\pauline{Pour le moment cette section est juste une compilation de vagues idées... }
+
 	The generalization of the Vandermonde determinant given in subsection \ref{section_inert_variables} is also well defined for other diagrams that are not Ferrer's diagrams of partitions.
@@
 	We define $\mathcal{M}_{\gamma}^{(r)}$ to be the smallest $\GLr \times \Sn$-submodule containing $V_\gamma$ and closed by partial derivation and polarization and we use the same notation for the character.
-\pauline{motivate introduction of the quotient ans Steenrod operators.}
+\pauline{motivate introduction of the quotient and Steenrod operators.}
 

### 2019-09-03 character.py

@@ -4,6 +4,8 @@
 from pypersist import persist
 from sage.misc.misc import attrcall
 from sage.categories.tensor import tensor
+from sage.misc.latex import latex
+
 
 from diagonal_polynomial_ring import*
 from subspace import*

### 2019-09-03 one_line_one_cell.py
Delete useless file

@@ -1,14 +1,0 @@
-from character.py import *
-
-def frob_add_one_cell(i,n) :
-    diagram = Diagram([(k,0) for k in range(0,n-1)]+[(i,1)])
-    diagram.draw()
-    return E_mu(diagram, parallel=True, r=n-2)
-
-n = 6
-res = []
-for i in range(0,n-1):
-    res += frob_add_one_cell(i,n)
-    print(res[i])
-    print
-    print latex_output_character(res[i])

### 2020-06-08 article/article.tex
improvement of context part + little change of structure

@@
 
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks=true,
+	linkcolor=magenta,
+	filecolor=magenta,      
+	urlcolor=cyan,
+	citecolor=cyan
+}
+
 %Notes
 \usepackage[colorinlistoftodos,prependcaption,textsize=small,textwidth=2.5cm]{todonotes}
-\newcommand{\pauline}[1]{\todo[linecolor=blue,backgroundcolor=cyan!25,bordercolor=blue]{#1}}
-\newcommand{\nicolas}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green]{#1}}
+\newcommand{\pauline}[1]{\todo[linecolor=magenta,backgroundcolor=magenta!20,bordercolor=magenta]{#1}}
+\newcommand{\nicolas}[1]{\todo[linecolor=cyan,backgroundcolor=cyan!25,bordercolor=cyan]{#1}}
 
@@
 \DeclareMathOperator{\GLr}{GL_r}
+\DeclareMathOperator{\Gl}{GL}
 \DeclareMathOperator{\harmonics}{\mathcal{H}}
@@
 As much as possible, the code is written to be modular and reusable.
+\\
 
-	\section{Context : harmonic and diagonal harmonic polynomials}
+	\pauline{paragraphes suivants à revoir, peut servir pour un rapide historique dans l'intro, sinon à supprimer}
+
+	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman introduce a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
+
+	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$.
+We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
+Then, let define
+	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
+	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\
+
+	With a similar idea, François Bergeron introduce another generalization of the diagonal harmonics, with \emph{inert variables}.
+We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
+The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
+
+	\section{Context}
+
+	\subsection{Action of $\GLr \times \Sn$ on multivariate polynomials}
 
 \nicolas{Ajouter des exemples au fur et à mesure}
-\pauline{J'ai déjà mis pas mal d'exemples. Il en faut plus?}
 
@@
 	$$X := \begin{pmatrix}
-	x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
-	x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
+	x_{11} & x_{12} & \cdots & x_{1n} \\
+	x_{21} & x_{22} & \cdots & x_{2n} \\
 	\vdots & \vdots & \ddots & \vdots \\
-	x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\
+	x_{r1} & x_{r2} & \cdots & x_{rn} \\
 	\end{pmatrix}$$
-	and we denote by $\bm{x}_i = (x_{i,1}, x_{i,2}, \dots, x_{i,n})$ the i-th set of variables.
+	and we denote by $\bm{x}_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables.
 We use the convention that bold letters stand for sets of variables and light letters stand for the variables themselves.
@@
 	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns of $X$ and of the general linear group $\GLr$ by diagonal action on the rows of $X$.
+More precisely, let consider $\sigma  \in \Sn$ as a permutation matrix, then, the action of $\Sn$ on $f \in R$, is given by $f(X) \mapsto f(X.\sigma)$.
+In the same way, the action of $\GLr$ on $f \in R$, is given by $f(\bm{x}) \mapsto f(T.X)$ where $T \in \GLr$.
 	\begin{figure}[H]
@@
 The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term.
-It inherits from R a structure of graded $\GLr \times \Sn$ bi-module.
-The degree of a polynomial in $R_{\Sn}$ is defined to be the sum of the degrees in each set of variables.
+We recall that $R$ is graduated by the degree and since $\mathcal{I}_n$ is a homogeneous ideal of $R$, $R_{\Sn}$ inherits from R a structure of graded $\GLr \times \Sn$ bi-module.
+The degree of a polynomial $f$ in $R_{\Sn}$ is defined to be the maximum degree of a monome of $f$.
+\pauline{Définir le degré plus en détail ?}
 
@@
 
-	We denote the partial derivatives by $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
+	We recall that the irrducible characters of both $\GLr$ and $\Sn$ can be express in terms of Schur functions.
+Thus, the character associated to the simultaneous action of $\GLr$ and $\Sn$ on $R$ is given by a pair of Schur functions $(s_\mu(\bm{q}), s_\lambda(\bm{w})$ with $\bm{q} = (q_1, q_2, \dots, q_r)$ encoding the action of $\GLr$ and $\bm{w} = (w_1, w_2, \dots, w_n)$ encoding the action of $\Sn$.
+We rewrite this pair of Schur function as a formal tensor product and we obtain the following expression for the $(\GLr \times \Sn)$-character
+	\begin{equation}
+	\sum_{\lambda \vdash n} \sum_{\mu} c_{\lambda\mu} s_\mu \otimes s_\lambda,
+	\end{equation}
+
+	where the coefficients $c_\lambda\mu \in \NN$ correspond to the multiplicities of the irreducible representations and are to be determined.
+Note that, in order to simply the expression, we dropped the variables $\bm{q}$ and $\bm{w}$, since the tensor product already indicate which Schur function is associated to $\GLr$ and which one is associated to $\Sn$.
+\\
+
+	We can extend all those considerations to the polynomial ring $R' = \QQ[X']$ of multivariate polynomials on $r$ sets of $n$ variables plus one set of inert variables.
+
+	$$X' := \begin{pmatrix}
+	x_{11} & x_{12} & \cdots & x_{1n} \\
+	x_{21} & x_{22} & \cdots & x_{2n} \\
+	\vdots & \vdots & \ddots & \vdots \\
+	x_{r1} & x_{r2} & \cdots & x_{rn} \\
+	\theta_1 & \theta_2 & \cdots & \theta_n
+	\end{pmatrix}$$
+
+	In this case, $\GLr$ still acts by left multiplication on the $r$ first sets of variables but does not act on $\bm{\theta}$.
+Thus, $\GLr$ can be seen as a subgroup of $\Gl_{r+1}$ not acting on the last row of $X'$.
+However, $\Sn$ still acts by right multiplication, permuting the columns of $X'$, including the inert variables.
+
+	\begin{figure}[h]
+	\centering
+	\begin{tikzpicture}
+	\draw node{$\begin{pmatrix}
+		x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
+		x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
+		\vdots & \vdots & \ddots & \vdots \\
+		x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\ 
+		\theta_{1} & \theta_{2} & \cdots & \theta_{n}
+		\end{pmatrix}$ } (0,0);
+	\draw (-2.4,.6)+(60:.25)
+	[xscale=.5,yscale=3.5,->,rotate=80] arc(-40:290:.25);
+	\node at (-3,0.3) {{\small$\GLr$}};
+	\draw (-.6,-1.7)+(60:.25)
+	[xscale=5.8,yscale=.6,->,rotate=-210] arc(-40:290:.25);
+	\node at (0,-2.1) {{\small$\Sn$}};
+	\draw (-1.8,-.85) -- (1.8,-.85);
+	\end{tikzpicture}
+	\caption{Simultaneous actions of $\GLr$ and $\Sn$ on classical and inert variables.}
+	\end{figure}
+
+	The $\theta_i$ are said to be inert because there are considered to be of degree 0 which means that they are considered as constants for the derivation ans they don't intervene in the computation of the degree of a polynomial.
+Thus, the ring $R'$ has a structure of $(\GLr \times \Sn)$-module graded by the degree.
+\\
+
+	We won't enter more into details on representation theory here but for more on this topic see \cite{FultonHarris1991}.
+Also, \cite{Sagan} is a classical reference for representation theory of the symmetric group and \cite{Green2007} is about polynomial representations of the general linear group.
+
+	\subsection{Multivariate harmonic polynomials}
+
+	We denote the partial derivatives by $\partial x^k := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
 	When $X$ contains only one set of variables, $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.
@@
 		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$,
-		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0.$$
+		$$\partial x_1^k f + \partial x_2^k f + \dots + \partial x_n^k f = 0.$$
 	\end{definition}
@@
 	\begin{example}
-		The Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.
-
-		The space of harmonic polynomials in two variables is $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$. 
+	Let consider the case of $2$ variables $x_1$ and $x_2$. 
+	In this case, polynomials with only a constant term are harmonic.
+Moreover, $x_1-x_2$ is harmonic but $x_1^2-x_2^2$.
+In fact, linear combinations of constants and $x_1-x_2$ are the only harmonic polynomials in 2 variables so $\harmonics_2 = \QQ \{ 1, x_1-x_2 \}$.
 	\end{example}
 
-	It is easy to see that if $f$ is harmonic then $\partial_{x_i} f$ is also harmonic for all $x_i \in X$.
+	\begin{example}
+		The Vandermonde determinant $V_n:= \prod_{i<j}(x_i-x_j) = \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} $ is harmonic.
+Indeed, it is well-known that the Vandermonde determinant is the antisymmetric polynomial in $n$ variables with the smallest degree.
+Therefore, since $\sum_{i=1}^{n} \partial x_i^k V_n$ is still antisymmetric, it has to be 0.
+	\end{example}
+
+	Since derivatives on polynomials commute, if $f$ is harmonic then $\partial x_i f$ is also harmonic for all $x_i \in X$.
 Using that, one can define $\harmonics_{n}$ directly with  partial derivatives instead of seeing them as solutions of a system of partial differential equations as stated in the following theorem.
@@
 	\begin{theorem}
-		The space of harmonic polynomials $\harmonics_{n}$ is the smallest subspace containing the Vandermonde determinant $V_n$ and closed by partial derivatives.
+		The space of harmonic polynomials $\harmonics_{n}$ is the smallest subspace containing the Vandermonde determinant $V_n$ and closed by partial derivatives : $\harmonics_{n} = \mathcal{D}(\QQ\{V_n\})$, where $\mathcal{D}$ denote the closure by partial derivatives.
 	\end{theorem}
@@
 
-	As for harmonic polynomials, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.
+	As for harmonic polynomials, we would like an alternative and more direct way to obtain $\harmonics_n^{(r)}$ directly using operators.
 
 	\begin{definition}
-		The \emph{polarisation operator} $P_{x,y}^k$ is given by
-		$$P_{x,y}^k = \sum_{i=1}^{n} y_i \partial_{x_i}^k$$
+		The \emph{polarisation operator} $P_{\bm{x},\bm{y}}^k$ is given by
+		$$P_{\bm{x},\bm{y}}^k = \sum_{i=1}^{n} y_i \partial x_i^k$$
 		where $\bm{x}$ and $\bm{y}$ are two sets of variables of $X$. 
@@
 
-	For $k=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$.
+	For $k=1$, those operators implement the action of $\mathfrak{sl}_r$ induced by $\mathfrak{gl}_r$. \pauline{Can you add more details on that Nicolas ?}
 
@@
 	\begin{conjecture} \label{DiagHarm}
-		Diagonal harmonic polynomials $\harmonics_n^{(r)}$ are obtained by polarization of harmonic polynomials $\harmonics_n^{(1)}$ in the first set of variables.
+		Diagonal harmonic polynomials $\harmonics_n^{(r)}$ is the smallest subspace containing the Vandermonde determinant and closed by partial derivatives and polarisation operators : $\harmonics_n^{(r)} = \mathcal{P}_{\mathcal{D}}(\QQ\{V_n\})$, where $\mathcal{P}_{\mathcal{D}}$ denote the closure by partial derivatives and polarisation.
 	\end{conjecture}
 
-	Conjecture \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}).
-It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true.
-\pauline{talk to Mike for more informations} \\
+	Conjecture \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}). It is not proven yet for more than two sets of variables. \\
 
-    Since diagonal harmonics polynomials spaces are of huge dimension, they are not easy to study.
-Indeed, when $r=1$, $R_{\Sn}$ is of dimension $n!$, and when $r=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$).
+	Let now construct a similar subspace of $R'$ using inert variables.
+Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
+Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+
+	\begin{example}
+		The partition $(2,1)$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
+	\end{example}
+
+	\begin{definition}
+			Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization. We denote this space by $\Elambdar{\lambda}{r}$.
+	\end{definition}
+
+	The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\Elambdar{\lambda}{r}$ for $\lambda = (n)$.
+
+	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
+Therefore, when the precision is not necessary, we drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
+	This property also gives use an upper bound for the number of sets of variables needed in the computation. \\
+
+	The characters of the harmonic and diagonal harmonic polynomial spaces have been studied a lot until now.
+For example, it is known that, when r=1, the action of $GL_1$ is trivial and $R_{\Sn}$ carries the usual graded representation of $\Sn$.
+Its character is given by a Hall-Littlewood polynomial.
+	The case r=2 has been studied by Garsia and Haiman (see \cite{GarsiaHaiman1993}) and the bigraded character, as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), is a Macdonald polynomial.
+	Finally, some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
+Therefore, the computation of the characters of $\harmonics_{n}^{(r)}$ should lead to a better understanding of those spaces.
+
+    Therefore, since polynomials spaces and $\Elambdar{\lambda}{r}$ are of huge dimension, they are not easy to study.
+Indeed, when $r=1$, $\harmonics_n = \Elambdar{n}{1}$ is of dimension $n!$, and when $r=2$, $\Elambdar{n}{2}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$).
+Moreover, $\Elambdar{n}{r}$ contain high degree polynomials with a lot of terms.
+For example, when $n=6$, we work with 36 variables, with polynomial of degree up to 15 and containing up to $6!
+= 720$ monomes.
+A quick estimation of the time it would take to compute the character using brute force, gives us about 1600 years of computation.
 
@@
 Knowing the irreducible characters gives information on the studied module such as the dimension.
-
-    We don't enter into details on representation theory here but for more on this topic see \cite{FultonHarris1991}.
-Also, \cite{Sagan} is a classical reference for representation theory of the symmetric group and \cite{Green2007} is about polynomial representations of the general linear group.
-\\
-
-   	The characters of the harmonic and diagonal harmonic polynomial spaces have been studied a lot until now.
-For example, it is known that, when r=1, the action of $GL_1$ is trivial and $R_{\Sn}$ carries the usual graded representation of $\Sn$.
-Its character is given by a Hall-Littlewood polynomial.
-
-    The case r=2 has been studied by Garsia and Haiman (see \cite{GarsiaHaiman1993}) and the bigraded character, as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), is a Macdonald polynomial.
-
-	Finally, some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown.
-Therefore, the computation of the characters of $\harmonics_{n}^{(r)}$ should lead to a better understanding of those spaces.
-\\
-
-	Throughout this article, we write the spaces and their the character the same way, except if there might be a confusion, then the variables are added to the character and we write $\mathcal{H}_n^{(r)}(\bm{q};\bm{w})$ for the character of $\mathcal{H}_n^{(r)}$,  with $\bm{q}$ the variables used to express the $\GLr$ part of the character and $\bm{w}$ for the $\Sn$ part.\\
 
@@
 
-	\begin{example} \label{H_3} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$. \pauline{I haven't find yet a way to have latex output with automatic breaklines.}
+	\begin{example} \label{H_3} Compute $\harmonics_3$ with one row of variables $\bm{x} = (x_1, x_2, x_3)$. \pauline{I haven't find out a way to have latex output with automatic breaklines.}
 		\begin{sagesilent}
@@
 	At this stage, we have an algorithm, but are still doing linear algebra in a huge space. The cost is $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space.
+
+	\subsection{Quasi-commutativity of derivatives and polarisation operators}
 
@@
 
-	\subsection{Exploiting column antisymmetries}
-
-	One thing that can slow down the computation is that the polynomials we are working with tend to be big.
-For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, is a homogeneous polynomial of degree $\sum_{i=1}^{5}i = 15$ with $6!=720$ monomials .
-This means that we need a lot of space to store them and it takes time when we want to apply operators.
-
-	However, since we use the Young symmetrizer to construct $\harmonics_{n}^{(r)}$, for all $v \in \harmonics_{n}^{(r)}$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
-Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$.
-	It is therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
-We chose to keep the smallest representative monomial in lexicographic order and call the result the \emph{normal reduced form} of $v$.
-\\
-
-	Thus keeping reduced forms of the polynomials decreases space complexity, and also time complexity when applying operators.
-Note that each time a polarization operator is applied to an element, the normal reduced form of the new element obtained is computed again.
-
-	\begin{example} ~
-
-		$V_{3} = -x_{1}^{2} x_{2} + x_{1} x_{2}^{2} + x_{1}^{2} x_{3} - x_{2}^{2} x_{3} - x_{1} x_{3}^{2} + x_{2} x_{3}^{2}$ is of type $(1,1,1)$ and has reduced form $x_1^2x_2$.
-
-		$\partial_{x_2}V_{3} = -x_{1}^{2} + 2 x_{1} x_{2} - 2 x_{2} x_{3} + x_{3}^{2}$ is of type $(2,1)$ and has reduced form $x_1^2 - 2x_1x_2$.
-	\end{example}
-
-	In practice, the antisymmetries are exploited first when projecting $\harmonics_n^{(1)}$ onto its isotypic components.
-When applying the Young idempotent, the reduced form of each element is computed.
-From this step, the polynomials lie in a diagonal polynomial ring with antisymmetries, thus each polynomial carries the information of its antisymmetries.
-	Then, we maintain the elements of the bases of the isotypic components in their reduced form during polarization.
-
-	\begin{example}
-			Compute $\harmonics_3^{(2)}$ exploiting antisymmetries. 
-		\begin{sagecommandline}
-			sage: v = vandermonde(Partition([3]))
-			sage: derivatives = partial_derivatives(v.parent())
-			sage: H_3 = Subspace({v.multidegree(): [v]}, derivatives)
-		\end{sagecommandline}
-		At this stage, we project onto the isotypic components of $\Sym{3}$ exploiting antisymmetries. One can check the difference between this computation and the one in example \ref{multigrading}. 
-		\begin{sagecommandline}
-			sage: H_3 = IsotypicComponent(H_3, 3, use_antisymmetry=True)
-			%sage: H_3[Partition([3])].basis()
-			sage: H_3[Partition([2,1])].basis()
-			sage: H_3[Partition([1,1,1])].basis()
-		\end{sagecommandline}
-		We see that the parent of the polynomials carries the information about the antisymmetries to keep polynomials in normal reduced form.
-		\begin{sagecommandline}
-			sage: p = H_3[Partition([2,1])].basis().values()[0][0]
-			sage: p
-			sage: p.parent()
-		\end{sagecommandline}
-		Now we polarize each isotypic component still exploiting antisymmetries.  
-		\begin{sagecommandline}
-			sage: H_3 = PolarizedSpace(H_3, polarization_operators(2))
-			sage: H_3[Partition([2,1])].basis()
-		\end{sagecommandline}
-	\end{example}
-
-	This trick was already used by François Bergeron for the polarizations of the Vandermonde (the diagram space).
-Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
-
-	We gain in theory up to $n!$. In practice, between one and two orders of magnitude due to the overhead of straightening monomials.
-
 	\subsection{Exploiting row symmetries}
@@
 
+	\subsection{Exploiting column antisymmetries}
+
+	One thing that can slow down the computation is that the polynomials we are working with tend to be big.
+For example, for $\lambda \vdash 6$, the Vandermonde determinant $V_\lambda$, is a homogeneous polynomial of degree $\sum_{i=1}^{5}i = 15$ with $6!=720$ monomials .
+This means that we need a lot of space to store them and it takes time when we want to apply operators.
+
+	However, since we use the Young symmetrizer to construct $\harmonics_{n}^{(r)}$, for all $v \in \harmonics_{n}^{(r)}$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$.
+Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$.
+	It is therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created).
+We chose to keep the smallest representative monomial in lexicographic order and call the result the \emph{normal reduced form} of $v$.
+\\
+
+	Thus keeping reduced forms of the polynomials decreases space complexity, and also time complexity when applying operators.
+Note that each time a polarization operator is applied to an element, the normal reduced form of the new element obtained is computed again.
+
+	\begin{example} ~
+
+		$V_{3} = -x_{1}^{2} x_{2} + x_{1} x_{2}^{2} + x_{1}^{2} x_{3} - x_{2}^{2} x_{3} - x_{1} x_{3}^{2} + x_{2} x_{3}^{2}$ is of type $(1,1,1)$ and has reduced form $x_1^2x_2$.
+
+		$\partial_{x_2}V_{3} = -x_{1}^{2} + 2 x_{1} x_{2} - 2 x_{2} x_{3} + x_{3}^{2}$ is of type $(2,1)$ and has reduced form $x_1^2 - 2x_1x_2$.
+	\end{example}
+
+	In practice, the antisymmetries are exploited first when projecting $\harmonics_n^{(1)}$ onto its isotypic components.
+When applying the Young idempotent, the reduced form of each element is computed.
+From this step, the polynomials lie in a diagonal polynomial ring with antisymmetries, thus each polynomial carries the information of its antisymmetries.
+	Then, we maintain the elements of the bases of the isotypic components in their reduced form during polarization.
+
+	\begin{example}
+		Compute $\harmonics_3^{(2)}$ exploiting antisymmetries. 
+		\begin{sagecommandline}
+			sage: v = vandermonde(Partition([3]))
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: H_3 = Subspace({v.multidegree(): [v]}, derivatives)
+		\end{sagecommandline}
+		At this stage, we project onto the isotypic components of $\Sym{3}$ exploiting antisymmetries. One can check the difference between this computation and the one in example \ref{multigrading}. 
+		\begin{sagecommandline}
+			sage: H_3 = IsotypicComponent(H_3, 3, use_antisymmetry=True)
+			%sage: H_3[Partition([3])].basis()
+			sage: H_3[Partition([2,1])].basis()
+			sage: H_3[Partition([1,1,1])].basis()
+		\end{sagecommandline}
+		We see that the parent of the polynomials carries the information about the antisymmetries to keep polynomials in normal reduced form.
+		\begin{sagecommandline}
+			sage: p = H_3[Partition([2,1])].basis().values()[0][0]
+			sage: p
+			sage: p.parent()
+		\end{sagecommandline}
+		Now we polarize each isotypic component still exploiting antisymmetries.  
+		\begin{sagecommandline}
+			sage: H_3 = PolarizedSpace(H_3, polarization_operators(2))
+			sage: H_3[Partition([2,1])].basis()
+		\end{sagecommandline}
+	\end{example}
+
+	This trick was already used by François Bergeron for the polarizations of the Vandermonde (the diagram space).
+Using higher Specht polynomials further allowed  to generalize that optimization to each shape.
+
+	We gain in theory up to $n!$. In practice, between one and two orders of magnitude due to the overhead of straightening monomials.
+
 	\subsection{Exploiting representations of $sl_k$}
@@
 
-	\section{Applications / Generalizations}
-
-	\subsection{Inert variables} \label{section_inert_variables}
-	\nicolas{2-3 paragraphs of announcement in the introduction}
-	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman introduce a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
-
-	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$.
-We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner.
-Then, let define
-	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
-	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\
-
-	With a similar idea, François Bergeron introduce another generalization of the diagonal harmonics, with \emph{inert variables}.
-We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert.
-The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.
-
-	Note that inert variables, like constants, do not contribute to the degree of the polynomials in which they intervene. They can be considered as "degree 0 variables".
-
-	\begin{figure}[H]
-		\centering
-		\begin{tikzpicture}
-		\draw node{$\begin{pmatrix}
-			x_{1,1} & x_{1,2} & \cdots & x_{1,n} \\
-			x_{2,1} & x_{2,2} & \cdots & x_{2,n} \\
-			\vdots & \vdots & \ddots & \vdots \\
-			x_{r,1} & x_{r,2} & \cdots & x_{r,n} \\ 
-			\theta_{1} & \theta_{2} & \cdots & \theta_{n}
-			\end{pmatrix}$ } (0,0);
-		\draw (-2.4,.6)+(60:.25)
-		[xscale=.5,yscale=3.5,->,rotate=80] arc(-40:290:.25);
-		\node at (-3,0.3) {{\small$\GLr$}};
-		\draw (-.6,-1.7)+(60:.25)
-		[xscale=5.8,yscale=.6,->,rotate=-210] arc(-40:290:.25);
-		\node at (0,-2.1) {{\small$\Sn$}};
-		\draw (-1.8,-.85) -- (1.8,-.85);
-		\end{tikzpicture}
-		\caption{Simultaneous actions of $\GLr$ and $\Sn$ on classical and inert variables.}
-	\end{figure}
-
-	Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
-Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
-
-	\begin{example}
-		The partition $(2,1)$ contains the cells $(0,0)$ and $(1,0)$ in the first row, and the cell $(0,1)$ in the second row, and $V_{2,1} = -x_2\theta_1 + x_3\theta_1 + x_1\theta_2 - x_3\theta_2 - x_1\theta_3 + x_2\theta_3$.
-	\end{example}
-
-	Like before, we consider the smallest subspace containing $V_{\lambda}$ and closed by partial derivation and polarization, except that this time the inert variables do not intervene in these operators.
-We denote this space by $\Elambdar{\lambda}{r}$.
-The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\Elambdar{\lambda}{r}$ for $\lambda = (n)$.
-\\
-
-	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
-Therefore, when the precision is not necessary, we drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
-
-	This property also gives use an upper bound for the number of sets of variables needed in the computation. \\
-
-	Like for $\harmonics_n^{(r)}$, the $\GLr \times \Sn$-character of $\Elambdar{\lambda}{r}$ is not easy to compute due to the dimension but hopefully most of the strategies we use to compute the character of $\harmonics_{n}^{(r)}$ work for $\Elambdar{\lambda}{r}$.
-
-	Therefore, we, once again, use polarization to compute $\Elambdar{\lambda}{r}$ from $\Elambda{\lambda}{1}$ and exploit the multigrading.
-We use the same isotypic projector to obtain the isotypic components, then we can still exploit the columns antisymmetries.
-%	\begin{example} ~
-%		
-%		$V_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is of type $(1,1,1)$ and has reduced form $x_1\theta_2$.
-%		
-%		$\partial_{x_2}V_{21} = -\theta_1 + \theta_3$ is of type $(2,1)$ and has reduced form $-\theta_1$.
-%	\end{example}
-	Finally, $\Elambdar{\lambda}{r}$ is still symmetric with respect to a permutation of the rows of $X$ containing classical variables so we exploit row symmetries in this case too.\\
+	\section{Results}
 
@@
 
-	\subsection{Further work}\label{section_futher_work}
+	\section{Further work}\label{section_futher_work}
 

### 2020-06-08 diagram.py
correct print python 3

@@ -183,5 +183,5 @@ class Diagram():
                             string += '|_|' 
                         else:
                             string += ' '
-            print string
+            print(string)
 

### 2020-06-08 subspace.py
correct bugs due to python 3

@@ -193,7 +193,7 @@ class Subspace(object):
         self._base_ring = ambient.base_ring()
 
         if hilbert_parent is None:
-            if generators.keys()[0] in NN:
+            if list(generators.keys())[0] in NN:
                 hilbert_parent = QQ['q']
         self._hilbert_parent = hilbert_parent
 
@@ -205,7 +205,7 @@ class Subspace(object):
         self._todo = []
         self._add_degrees = add_degrees
         self._extend_word = extend_word
-        for d, gens in generators.iteritems():
+        for d, gens in generators.items():
             basis = EchelonMatrixOfVectors(ambient=self._ambient, stats=self._stats)
             for g in gens:
                 if basis.extend(g):
@@ -218,7 +218,7 @@ class Subspace(object):
     
     def todo(self, vector, d1, word):
         todo = self._todo
-        for d2, ops in self._operators.iteritems():
+        for d2, ops in self._operators.items():
             try:
                 d3 = self._add_degrees(d1, d2)
             except ValueError:

### 2020-06-08 subspace.py
correct bugs due to python 3

@@ -238,7 +238,7 @@ class Subspace(object):
     def basis(self):
         self.finalize()
         basis = {}
-        for i, val in self._bases.iteritems() : 
+        for i, val in self._bases.items() : 
             if val.vectors() != () :
                 basis[i] = val.vectors()
         #return sum((basis.vectors() for basis in self._bases.values()), ())
@@ -249,7 +249,7 @@ class Subspace(object):
 
     def dimensions(self):
         self.finalize()
-        return {d: basis.cardinality() for d, basis in self._bases.iteritems()}
+        return {d: basis.cardinality() for d, basis in self._bases.items()}
 
     def matrix(self):
         self.finalize()

### 2020-06-08 article/article.tex
add section commutativity operators

@@
+% !TeX spellcheck = en_US
 \documentclass[letter,12pt]{article}
@@
 \newcommand{\CC}{\mathbb{C}}
+\newcommand{\x}{\bm{x}}
+\newcommand{\y}{\bm{y}}
 \newcommand{\Sym}[1]{\mathbb{S}_{#1}}
@@
 	In this article, we present a new SageMath package to compute bicharacter of some multivariate polynomials spaces. 
-	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module.
+	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$(\GLr \times \Sn$)-module.
 It is then extended to compute other characters of polynomial spaces.
@@
 The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$-character.
-It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
+It is thus equivalent to consider the $(\GLr \times \Sn$)-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.
 \\
 
-	We recall that the irrducible characters of both $\GLr$ and $\Sn$ can be express in terms of Schur functions.
-Thus, the character associated to the simultaneous action of $\GLr$ and $\Sn$ on $R$ is given by a pair of Schur functions $(s_\mu(\bm{q}), s_\lambda(\bm{w})$ with $\bm{q} = (q_1, q_2, \dots, q_r)$ encoding the action of $\GLr$ and $\bm{w} = (w_1, w_2, \dots, w_n)$ encoding the action of $\Sn$.
+	We recall that the irreducible characters of both $\GLr$ and $\Sn$ can be express in terms of Schur functions.
+Thus, the character associated to the simultaneous action of $\GLr$ and $\Sn$ on $R$ is given by a pair of Schur functions $(s_\mu(\bm{q}), s_\lambda(\bm{w}))$ with $\bm{q} = (q_1, q_2, \dots, q_r)$ encoding the action of $\GLr$ and $\bm{w} = (w_1, w_2, \dots, w_n)$ encoding the action of $\Sn$.
 We rewrite this pair of Schur function as a formal tensor product and we obtain the following expression for the $(\GLr \times \Sn)$-character
@@
 
-	where the coefficients $c_\lambda\mu \in \NN$ correspond to the multiplicities of the irreducible representations and are to be determined.
+	where the coefficients $c_{\lambda\mu}$ are positive integers corresponding to the multiplicities of the irreducible representations and are to be determined.
 Note that, in order to simply the expression, we dropped the variables $\bm{q}$ and $\bm{w}$, since the tensor product already indicate which Schur function is associated to $\GLr$ and which one is associated to $\Sn$.
@@
 
-	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$, is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$.
+	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$, is the joint kernel of the differential operators $D_k := \partial x_1^k + \cdots + \partial x_n^k$.
 It is also a realization of the coinvariants of the symmetric group: $R\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.
@@
 	\begin{example}
-	Let consider the case of $2$ variables $x_1$ and $x_2$. 
+	Let consider the case of two variables $x_1$ and $x_2$. 
 	In this case, polynomials with only a constant term are harmonic.
-Moreover, $x_1-x_2$ is harmonic but $x_1^2-x_2^2$.
-In fact, linear combinations of constants and $x_1-x_2$ are the only harmonic polynomials in 2 variables so $\harmonics_2 = \QQ \{ 1, x_1-x_2 \}$.
+Moreover, $x_1-x_2$ is harmonic but $x_1^2-x_2^2$ is not.
+In fact, linear combinations of constants and $x_1-x_2$ are the only harmonic polynomials in two variables so $\harmonics_2 = \QQ \{ 1, x_1-x_2 \}$.
 	\end{example}
@@
 Indeed, it is well-known that the Vandermonde determinant is the antisymmetric polynomial in $n$ variables with the smallest degree.
-Therefore, since $\sum_{i=1}^{n} \partial x_i^k V_n$ is still antisymmetric, it has to be 0.
+Therefore, since $\sum_{i=1}^{n} \partial x_i^k V_n$ is still antisymmetric but of a lower degree, it has to be 0.
 	\end{example}
@@
 Using that, one can define $\harmonics_{n}$ directly with  partial derivatives instead of seeing them as solutions of a system of partial differential equations as stated in the following theorem.
-See \cite{Haiman2002} and \cite{Bergeron2009} for more details.
+See \cite{Haiman2002} or \cite{Bergeron2009} for more details.
 
@@
 	Going back to an arbitrary number $r$ of sets of variables, we define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
-	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{1,1}}^{\alpha_1}\dots\partial_{x_{r,1}}^{\alpha_r} + \dots + \partial_{x_{1,n}}^{\alpha_1}\dots\partial_{x_{r,n}}^{\alpha_r}$$
+	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial x_{1,1}^{\alpha_1}\dots\partial x_{r,1}^{\alpha_r} + \dots + \partial x_{1,n}^{\alpha_1}\dots\partial x_{r,n}^{\alpha_r}$$
 
@@
 	\begin{definition}
-		The space of \emph{diagonal harmonic polynomials} $\harmonics_n^{(r)}$ is the joint kernel of the differential operators $(D_\alpha)_\alpha$.
-Note that $\harmonics_n^{(r)}$ contains $\harmonics_{n}^{(1)} = \harmonics_{n}$.
+		The space of \emph{diagonal harmonic polynomials} is the joint kernel of the differential operators $(D_\alpha)_\alpha$. 
 	\end{definition}
 
-	As for harmonic polynomials, we would like an alternative and more direct way to obtain $\harmonics_n^{(r)}$ directly using operators.
+	Note that the space of diagonal harmonic polynomials contains $\harmonics_{n}^{(1)} = \harmonics_{n}$.
+	As for harmonic polynomials, we would like an alternative and more direct way to obtain this space directly using operators.
 
@@
 	\begin{conjecture} \label{DiagHarm}
-		Diagonal harmonic polynomials $\harmonics_n^{(r)}$ is the smallest subspace containing the Vandermonde determinant and closed by partial derivatives and polarisation operators : $\harmonics_n^{(r)} = \mathcal{P}_{\mathcal{D}}(\QQ\{V_n\})$, where $\mathcal{P}_{\mathcal{D}}$ denote the closure by partial derivatives and polarisation.
+		Denote $\harmonics_n^{(r)}$ the smallest subspace containing the Vandermonde determinant and closed by partial derivatives and polarisation operators : $\mathcal{P}_{\mathcal{D}}(\QQ\{V_n\})$, where $\mathcal{P}_{\mathcal{D}}$ denote the closure by partial derivatives and polarisation.
+Then, the space of diagonal harmonic polynomials and $\harmonics_n^{(r)}$ are the same space.
 	\end{conjecture}
 
-	Conjecture \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}). It is not proven yet for more than two sets of variables. \\
+	Conjecture \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}), but it has not been proven yet for more than two sets of variables.
+From now, we work only with $\harmonics_{n}^{(r)}$ as defined in this conjecture.
+\\
 
 	Let now construct a similar subspace of $R'$ using inert variables.
-Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of its cells.
-Then the determinant $V_{\lambda}$ associated to $\lambda$ is given by $$V_{\lambda} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
+Let $\lambda$ be a partition of $n$ and note $(a,b)$ the Cartesian coordinates of the South West corner of its cells.
+Then we define the determinant $V_{\lambda}$ associated to $\lambda$ by $$V_{\lambda} := \det (x_i^a \theta_i^b)_{1 \leq i \leq n \atop (a,b) \in \lambda} .$$
 
@@
 
-	The space of diagonal harmonics $\harmonics_n^{(r)}$ is thus a special case of $\Elambdar{\lambda}{r}$ for $\lambda = (n)$.
+	The space $\harmonics_n^{(r)}$ is thus a special case of $\Elambdar{\lambda}{r}$ for $\lambda = (n)$.
 
-	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2013} or \cite{Bergeron2009}).
+	The character of $\Elambdar{\lambda}{r}$ stabilizes for $r \geq n$ (see \cite{Bergeron2009} or \cite{Bergeron2013}).
+This means that $r=n-1$ sets of variables are necessary to obtain all the terms of the character and adding another set or more of variables won't change the result.
 Therefore, when the precision is not necessary, we drop the exponent and simply write $\Elambda{\lambda}$ for $\Elambdar{\lambda}{r}$ with $r \geq n$.
-	This property also gives use an upper bound for the number of sets of variables needed in the computation. \\
+	This property also gives us an upper bound for the number of sets of variables needed in the computation. \\
 
@@
 Moreover, $\Elambdar{n}{r}$ contain high degree polynomials with a lot of terms.
-For example, when $n=6$, we work with 36 variables, with polynomial of degree up to 15 and containing up to $6!
+For example, when $n=6$, we have to work with 36 variables, with polynomials of degree up to 15 and containing up to $6!
 = 720$ monomes.
@@
 
-	\subsection{Computing in the space of harmonic polynomials using polarization}
+	\subsection{Computing in $\Elambdar{n}{r}$ using polarization}
 
@@
 
-	Solving those differential equations would not be tractable either. So instead we use partial derivatives and polarization operators defined in the previous section. \\
+	Solving those differential equations would not be tractable either.
+So instead, based on conjecture \ref{DiagHarm}, we use partial derivatives and polarization operators defined in the previous section.
+\pauline{Reformulation nécessaire, pas la preuve que ce sont les mêmes espaces alors raccourcis pas très rigoureux présenté ainsi.}\\
 
@@
 			sage: derivatives = [attrcall('derivative', x) for x in R.gens()]
-			sage: H_3 = Subspace([M.determinant()], derivatives)
-			sage: H_3.basis()
-			sage: H_3.dimension()
+			sage: H3 = Subspace([M.determinant()], derivatives)
+			sage: H3.basis()
+			sage: H3.dimension()
 		\end{sagecommandline}
+
+	With two rows of variables. 
+		\begin{sagesilent}
+			load("../character.py")
+		\end{sagesilent}
+		\begin{sagecommandline}
+			sage: v = vandermonde(3,2)
+			sage: derivatives = [attrcall("derivative", x) for i in range(2) for x in v.parent().multivar_pol_ring_variables()[i] ]
+			sage: polarizators = [attrcall("polarization", i1=i1, i2=i2, d=d) for d in range(1,4) for i1 in range(0, 2) for i2 in range(0, 2) if (i1!=i2)]
+			sage: H3 = Subspace([v], derivatives+polarizators)
+			sage: H3.dimension() 	
+		\end{sagecommandline}
+	\pauline{Problème dimension, j'ai trouvé l'élément intru mais je sais pas pourquoi il apparaît}
 	\end{example}
@@
 	\subsection{Quasi-commutativity of derivatives and polarisation operators}
+
+	At this stage, we are interested in reducing the number of operations computed by our \texttt{Subspace} utility.
+One way to do that would be to need less operators to obtain the same basis.
+This can be done by considering the quasi-commutativity of the partial derivatives and the polarisation operators.
+
+	\begin{prop}\label{prop_commutativite}
+		For all subspace $\mathcal{W}$ of $R'$,
+		$$\mathcal{P}_\mathcal{D}(\mathcal{W}) = \mathcal{D} \circ \mathcal{P}(\mathcal{W}) = \mathcal{P} \circ \mathcal{D}(\mathcal{W}),$$
+		where $\mathcal{P}$ is the closure by polarisation operators.
+	\end{prop}
+
+	\begin{proof}
+		If we apply a partial derivative and a polarisation operator with no variable in common on an element of $R'$, applying them on any order does not change the result.
+But let now look at what happen if those operators do have variables on common.
+
+		\begin{equation}\label{polpartial}
+		\partial y_i^l P^k_{\x,\y}f - P^k_{\x,\y} \partial y_i ^l f 
+		= \partial y_i ^l \sum_{j=1}^{n} y_j \partial x_j ^kf - \sum_{j=1}^{n} y_j \partial x_j ^k \partial y_i ^l f
+		\end{equation}
+
+		For $i=j$, we temporarily removed indices and we obtain, 
+		$\partial y^ly \partial x^k f - y \partial x^k \partial y^l = l\partial y^{l-1} \partial x^kf + y\partial y^{l} \partial x^kf - y\partial x^k \partial y^{l} f = l\partial y^{l-1} \partial x^kf$.
+		Using this result in equation \ref{polpartial}, we have 
+		\begin{equation}\label{polpartiali}
+		\partial y_i^l P^k_{\x,\y}f - P^k_{\x,\y} \partial y_i^l f  =  l\sum_{i=1}^{n} \partial y_i^{l-1} \partial x_i^k f.
+		\end{equation}
+
+		Thus we obtain a sum of composed partial derivatives.
+Since the spaces we study are closed by derivation, the commutation of partial derivatives and polarisation operators gives operators we are already using to build the subspace.
+Therefore, we don't obtain new linear independent elements by commuting those operators.
+	\end{proof}
+
+	This phenomena is due to the commutativity of the action of $\GLr$ represented by the polarisation operators and the action of $\Sn$ of $V_\gamma$  and its partial derivatives.
+
+	In our case, $\mathcal{W} = \QQ\{V_\lambda\}$ and we want to compute $\Elambdar{\lambda}{r} = \mathcal{P}_{\mathcal{D}}(\QQ\{V_\lambda\})$.
+Proposition \ref{prop_commutativite} implies that we can first compute a basis $\mathbb{B}_\lambda^{(1)}$ of the space $\Elambdar{\lambda}{1} = \mathcal{D}(\QQ\{V_\lambda\})$.
+Then, we can obtain a basis of $\Elambdar{\lambda}{r}$ from $\mathcal{P}(\mathcal{B}_\gamma^{(1)})$.
+
+	This way, we use only the partial derivatives on the first set of variables of $X'$ and we reduce the amount of compositions of operators to compute.
+
+	\begin{example}
+		\begin{sagesilent}
+			load("../character.py")
+		\end{sagesilent}
+		\begin{sagecommandline}
+			sage: v = vandermonde(3)
+			sage: v
+			sage: derivatives = partial_derivatives(v.parent())
+			sage: derivatives
+			sage: E3 = Subspace({v.multidegree() : [v]}, derivatives)
+			sage: E3.basis()
+			sage: E3.dimension()
+			sage: polarizators = polarization_operators(2)
+			sage: polarizators
+			sage: E3 = PolarizedSpace(E3, polarizators)
+			sage: E3.dimension()
+			sage: E3.dimensions()
+		\end{sagecommandline}
+	\end{example}
 
@@
 		\begin{sagecommandline}
-			sage: p = H_3[Partition([2,1])].basis().values()[0][0]
+			sage: p = list(H_3[Partition([2,1])].basis().values())[0][0]
 			sage: p
@@
 		Let $\alpha$ be a composition of $n$ and denote $\lambda(\alpha)$ the partition obtained by reordering the parts of $\alpha$.
-And denote by $\Elambdar{\alpha}{r}$ the character of the smallest $\GLr \times \Sn$-submodule containing $V_\alpha$ and closed by partial derivation and polarization.
+And denote by $\Elambdar{\alpha}{r}$ the character of the smallest $(\GLr \times \Sn$)-submodule containing $V_\alpha$ and closed by partial derivation and polarization.
 Then we have
@@
 
-	We define $\mathcal{M}_{\gamma}^{(r)}$ to be the smallest $\GLr \times \Sn$-submodule containing $V_\gamma$ and closed by partial derivation and polarization and we use the same notation for the character.
+	We define $\mathcal{M}_{\gamma}^{(r)}$ to be the smallest $(\GLr \times \Sn$)-submodule containing $V_\gamma$ and closed by partial derivation and polarization and we use the same notation for the character.
 \pauline{motivate introduction of the quotient and Steenrod operators.}

### 2020-06-08 character.py
correct bugs due to python 3

@@ -254,7 +254,7 @@ def merge(dict1, dict2):
 
     """
     result = dict1
-    for key, value in dict2.iteritems():
+    for key, value in dict2.items():
         if key in result:
             result[key] += value
         else:
@@ -314,14 +314,14 @@ def IsotypicComponent(S, arg, use_antisymmetry=False):
     
     basis = S.basis()
     result = {}
-    P1 = basis.values().pop()[0].parent()
+    P1 = list(basis.values()).pop()[0].parent()
     for nu in list_partitions:
         result_nu = {}
         if use_antisymmetry == True:
             antisymmetries = antisymmetries_of_tableau(nu.initial_tableau())
             P2 = DiagonalAntisymmetricPolynomialRing(P1._R, P1.ncols(), P1.nrows(), 
                                                  P1.ninert(), antisymmetries)
-        for deg, value in basis.iteritems():
+        for deg, value in basis.items():
             if use_antisymmetry:
                 gen = []
                 for p in value:
@@ -340,7 +340,7 @@ def IsotypicComponent(S, arg, use_antisymmetry=False):
             result[nu] = Subspace(result_nu, operators={})
                 
     if len(result.keys()) == 1:
-        key = result.keys()[0]
+        key = list(result.keys())[0]
         return result[key]
     else:
         return result
@@ -405,14 +405,14 @@ def PolarizedSpace(S, operators, add_degrees=add_degrees_isotypic):
     """
     if isinstance(S, dict):
         return {key : PolarizedSpace(value, operators, add_degrees=add_degrees)
-                for key, value in S.iteritems()}
+                for key, value in S.items()}
     else:
         basis = S.basis()
-        basis_element = basis.values().pop()[0]
+        basis_element = list(basis.values()).pop()[0]
         P1 = basis_element.parent()
         if operators != {}:
-            r = len(operators.keys().pop())
-            row_symmetry = operators.values().pop()[0].kwds['row_symmetry']
+            r = len(list(operators.keys()).pop())
+            row_symmetry = list(operators.values()).pop()[0].kwds['row_symmetry']
         else:
             r=1
             row_symmetry = None
@@ -423,7 +423,7 @@ def PolarizedSpace(S, operators, add_degrees=add_degrees_isotypic):
 
         if isinstance(P1, DiagonalAntisymmetricPolynomialRing):
             P2 = DiagonalAntisymmetricPolynomialRing(P1._R, P1.ncols(), r , P1.ninert(), P1.antisymmetries())
-            for key, value in basis.iteritems():
[…]
